### 2020-11-06 examples/point_defects/article/article.tex
new-runs

\documentclass[a4paper]{article}
\usepackage[margin=25mm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\pagenumbering{gobble}
\usepackage{verbatim}

% Keywords command
\providecommand{\keywords}[1]
{
  \small
  \textbf{\textit{Keywords---}} #1
}

\title{Numerical Solution of Point Defect Equations by MOOSE}
\author{Abdurrahman Ozturk$^{1}$, Karim Ahmed$^{1}$  \\
        \small $^{1}$Texas A\&M University \\
        % \small $^{2}$University B \\
}
% \date{} % Comment this line to show today's date

\begin{document}
\maketitle

\begin{abstract}

We present a detailed investigation of the effect of size on the segregation of point defects to interfaces and the resultant nucleation of voids. We utilize the spatially-resolved rate-theory (SRRT) modeling technique valid for modeling surfaces as discrete sinks. The effects of defect production rate, bias, and profile are thoroughly studied. The model predictions are generally different from the textbook ones obtained by the classical homogenized rate theory approach. The simulations show a strong dependence of the steady state defect profiles on the grain size, temperature, and production rate, bias, and profile. Moreover, the sink strength of each boundary is also affected by these factors. Furthermore, it is predicted that whenever there is a production bias, no neutral sinks can exist, i.e., there is always a preference for surfaces/interfaces to absorb one type of defects over another. The model predictions demonstrate the shortcomings of the classical homogenous rate-theory approach and shed light on the limitations of using ion irradiation to mimic neutron irradiation.

% Irradiation of a material creates point defects, vacancies and interstitials, as a result of
% atomic collisions. Those point defects are mobile and able to diffuse through material, recombine with each other,
% and disappear when they react with sinks. The concentration of both vacancy and interstitial can be described mathematically by chemical rate balance equations, named point defect equations (rate theory equations). Production, recombination, diffusion and reaction of point defects are given by separate terms in those equations, which makes it easy to solve and analyze each of them individually. In this work, spatially resolved non-dimensional point defect equations are solved in 1D by using MOOSE Framework. The effect of irradiation dose rate, sink density, temperature, uniform defect production, non-uniform defect production and biased defect production on steady state defect concentration profile and on grain boundary sink strength are studied. The calculations are also repeated for different domain sizes changing from 5\emph{nm} to 5$\mu$\emph{m} to investigate the effect of grain size on defect concentration and grain boundary sink strength. According to results, the domain size and defect production profile/bias have a significant effect on concentration profiles. They could create a flipped concentration profile through domain, which ends up with a defect segregation near grain boundary.

\end{abstract} \hspace{10pt}

%TC:ignore
\keywords{point defect equations, rate theory, radiation damage, MOOSE}
% \begin{thebibliography}{00}
% \bibitem{b2} Garry Was.
% \end{thebibliography}
%TC:endignore

% Word count
% \verbatiminput{\jobname.wordcount.tex}

\section{Introduction} \hspace{10pt}

\section{Methodology} \hspace{10pt}

\section{Results} \hspace{10pt}

The production bias is a factor that is used to create a difference between interstitial
and vacancy generation in domain. As the production bias increases, vacancy production
increases and the gap between steady state vacancy and interstitial concentrations gets wider.
Most of the plots in this part are generated by using the simulation results for Cs=1e18 m -3 ,
T=773K, K 0 =1e-3 dpa/s.
In nano-scale case, since the domain size is not big enough, the boundaries become
closer to each other. This causes point defects to reach sinks before they react with each other
and recombination plateau to disappear as it can be seen in Fig. 2. The nanoscale case acts like
a high-sink and high-temp condition case despite its low-sink and low-temperature. Therefore,
change in production bias does not have a significant effect on average concentration behavior
in nanoscale

On the other hand, in micro-scale case, the domain has reasonable size, and thus
boundaries are far from each other. This provides defects more time to accumulate inside the
domain and recombine with each other after they reach a specific concentration. Figure 3
clearly shows the effect of production bias on average concentration.

Effect of production bias on spatial profile of defect concentrations for nanoscale is
shown in Figure 4. The results seem not affected too much because of the same reasons
mentioned previously for average concentration.

The micro-scale results (Fig. 5) are quite interesting and worth to think over. The
concentration profiles of interstitials for 0.1%, 5% and 10% cases are flipped over. A closer look
at evolution of 5% case over time in Fig. 6, after the end of quasi-steady-state region (t=10 -4 s in
Fig 3.), the average interstitial concentration starts to decrease as they segregate through sinks.
At steady state, the average interstitial concentration becomes minimum at the center and
maximum near boundaries because of segregation.

The defect production rate (K 0 ) is the source term in point defect equations and has a
significant effect on concentrations.
In nano-scale case, the average concentration behavior is like high-sink density behavior
because of narrow domain. But, when the defect production rate increases, the average
concentration is shifted upward, and interstitial and vacancy average concentrations get closer
to each other because the production compensates more absorption at sinks than previous.
Based on this, if the production rate increased sufficiently, the recombination zone would
appear again in nano-scale domain.

\end{document}

### 2020-11-06 examples/point_defects/monocrystal/Nickel/Nickel_1D/coordinate_systems/500nm/Nickel_1D_uniform+boundary_sink_1e18_773K/Nickel_1D_uniform+boundary_sink_1e18_773K_1e-6/Nickel_1D_uniform+boundary_sink_1e18_773K_1e-6_0%/spherical-zero_recomb/analytical.py

@@ -1,0 +1,21 @@
+import numpy as np
+import math
+Cs=1e18
+Di=1.1066108307323346e-09
+Dv=2.0050685348844685e-13
+k0=1e-6
+kis=4.8949408023459335e-17
+kvs=8.869144879425032e-21
+a=500
+ki=(kis*Cs/Di)**0.5
+kv=(kvs*Cs/Dv)**0.5
+x=[]
+ci=[]
+cv=[]
+for i in range(0,500):
+    print(i)
+    x.append(i)
+    ci.append((k0/(Di*ki*ki))*(1-a*math.sinh(ki*x[i])/(x[i]*math.sinh(ki*a))))
+    cv.append((k0/(Dv*kv*kv))*(1-a*math.sinh(kv*x[i])/(x[i]*math.sinh(kv*a))))
+
+print(ci,cv)

### 2020-11-06 examples/point_defects/monocrystal/Nickel/plots/exponential.m

@@ -1,0 +1,25 @@
+format long;
+clear all;
+hold on;
+mu = 250;
+sigma = 50;
+K0 = 9.037e-13;
+A = 0;
+A_th=K0*(500-1)*exp(-((500-mu)^2)/(2*sigma^2))/(sigma*(2*pi)^0.5)
+for i=1:501
+    x(i)=i-1;
+y(i) = K0 * exp(-((x(i) - mu) ^ 2) / (2 * sigma ^ 2)) / ((0.4 / sigma) * sigma * (2 * pi) ^ 0.5);
+if
+  i > 1 A = A + 0.5 * (y(i) + y(i - 1)) * (x(i) - x(i - 1));
+end end yyaxis left plot(x, y) text(mu, K0, '\leftarrow A=' + string(A)) mu = 2500;
+sigma = 500;
+K0 = 9.037e-15;
+A = 0;
+A_th=K0*(5000-1)*exp(-((5000-mu)^2)/(2*sigma^2))/(sigma*(2*pi)^0.5)
+for i=1:5001
+    x(i)=(i-1);
+y(i) = K0 * exp(-((x(i) - mu) ^ 2) / (2 * sigma ^ 2)) / ((0.4 / sigma) * sigma * (2 * pi) ^ 0.5);
+if
+  i > 1 A = A + 0.5 * (y(i) + y(i - 1)) * (x(i) - x(i - 1));
+end end yyaxis right plot(x, y) text(mu, K0, '\leftarrow A=' + string(A)) xlabel('x')
+    ylabel('K0') grid on;

### 2020-11-06 examples/point_defects/monocrystal/Nickel/plots/modified_normal_dist.m

@@ -1,0 +1,27 @@
+format long;
+clear all;
+hold on;
+mu = 2500;
+sigma = 500;
+K0 = 9.037e-13;
+A = 0;
+A_th = K0 * (500 - 1) * exp(-((500 - mu) ^ 2) / (2 * sigma ^ 2)) / (sigma * (2 * pi) ^ 0.5);
+for
+  i = 1 : 5001 x(i) = i - 1;
+y(i) = K0 * exp(-((x(i) - mu + sigma) ^ 2) / (2 * sigma ^ 2)) /
+       ((0.4 / sigma) * sigma * (2 * pi) ^ 0.5);
+if
+  i > mu y2(i) = 0;
+else
+  y2(i) = 0.25 * K0 * (1 - (x(i) / mu) ^ 2);
+end y3(i) = y(i) + y2(i);
+% if i < mu % xx = 1.2 * mu - x(i);
+% y(i) = y(i) + K0 * exp(-((xx - mu) ^ 2) / (2 * sigma ^ 2)) /
+                    ((0.4 / sigma) * sigma * (2 * pi) ^ 0.5);
+% end if i > 1 A = A + 0.5 * (y(i) + y(i - 1)) * (x(i) - x(i - 1));
+end
+
+        end %
+    yyaxis left % plot(x, y) %
+    plot(x, y2) plot(x, y3) text(mu, K0, '\leftarrow A=' + string(A)) xlabel('x')
+        ylabel('K0') grid on;

### 2020-11-06 examples/point_defects/monocrystal/Nickel/plots/spherical_analytical.m

@@ -1,0 +1,20 @@
+format long;
+clear all;
+hold on;
+Cs = 1e18;
+Di = 1.1066108307323346e-09;
+Dv = 2.0050685348844685e-13;
+k0 = 1e-6;
+kis = 4.8949408023459335e-17;
+kvs = 8.869144879425032e-21;
+a = 500;
+ki=(kis*Cs/Di)^0.5
+kv=(kvs*Cs/Dv)^0.5
+
+for i=1:501
+    x(i)=i-1;
+ci(i) = (k0 / (Di * ki * ki)) * (1 - a * sinh(ki * x(i)) / (x(i) * sinh(ki * a)));
+cv(i) = (k0 / (Dv * kv * kv)) * (1 - a * sinh(kv * x(i)) / (x(i) * sinh(kv * a)));
+end
+
+    % yyaxis left plot(x, ci) plot(x, cv) xlabel('x') ylabel('Defect Concentration') grid on;

### 2020-11-08 examples/point_defects/article/article_plot.py
plotting_script update

@@ -1,0 +1,207 @@
+import re
+import sys
+import csv
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+
+                # ------------------------------------------------------- #
+                # ======================================================= #
+                # Pyhton script to plot data from MOOSE csv output files. #
+                # ======================================================= #
+                # ----------------------------------------------eigenturk #
+
+
+def getHelp():
+    print('\033[96m'+"\n# ------------------------------------------------------- #\n"
+          "# ======================================================= #\n"
+          "# Pyhton script to plot data from MOOSE csv output files. #\n"
+          "# ======================================================= #\n"
+          "# ----------------------------------------------eigenturk #\n"+'\033[0m')
+    print("This script is a tool for plotting csv files based on specified column numbers.\n\n"
+          "Usage: plot [filename] [column_number1] [column_number2] ... [-h] [-s]\n\n"
+          "Arguments:\n\n"
+          "\tfilename\t\tName of the data file with extension\n"
+          "\tcolumn_number\t\tThe column number of the data in csv file\n\n"
+          "Optional arguments:\n\n"
+          "  -h, Show this help message and exit.\n"
+          "  -s, Save only mode, plot wont be shown.\n\n"
+          "  -f, Multiple file mode."+'\033[91m'+" << ! Depricated, will be deleted. !\n\n"+'\033[0m'
+          '\033[4m'+'\033[1m'+"Manual for commands :\n\n"+'\033[0m'
+          "Note  : To make using this script easy, create 'plot' command by adding following line to bash profile.\n"
+          '\033[92m'+"\tCheck script file path(e.g. projects/scripts/plot.py)\n"+'\033[0m'
+          '\033[92m'+"\talias plot=\"python projects/scripts/plot.py\"\n"+'\033[0m'
+          "\n-Plotting data from a single file\n"
+          '\033[93m'+"\tplot filename column_number(x) column_number(y1) column_number(y2)....column_number(yn)\n"+'\033[0m'
+          "\n-Plotting data from multiple files\n"
[…]

### 2020-11-08 scripts/plot.py

@@ -1,8 +1,16 @@
+import re
 import sys
 import csv
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
+
+
+                # ------------------------------------------------------- #
+                # ======================================================= #
+                # Pyhton script to plot data from MOOSE csv output files. #
+                # ======================================================= #
+                # ----------------------------------------------eigenturk #
 
 
 def getHelp():
@@ -12,66 +20,81 @@ def getHelp():
           "# ======================================================= #\n"
           "# ----------------------------------------------eigenturk #\n"+'\033[0m')
     print("This script is a tool for plotting csv files based on specified column numbers.\n\n"
-          "Usage: plot [filename] [column_number1] [column_number2] ... [-f] [-s]\n\n"
+          "Usage: plot [filename] [column_number1] [column_number2] ... [-h] [-s]\n\n"
           "Arguments:\n\n"
           "\tfilename\t\tName of the data file with extension\n"
           "\tcolumn_number\t\tThe column number of the data in csv file\n\n"
           "Optional arguments:\n\n"
           "  -h, Show this help message and exit.\n"
-          "  -f, Multiple file mode, data from multiple files will be pllotted on the same figure.\n"
           "  -s, Save only mode, plot wont be shown.\n\n"
+          "  -f, Multiple file mode."+'\033[91m'+" << ! Depricated, will be deleted. !\n\n"+'\033[0m'
           '\033[4m'+'\033[1m'+"Manual for commands :\n\n"+'\033[0m'
           "Note  : To make using this script easy, create 'plot' command by adding following line to bash profile.\n"
-          '\033[91m'+"\tCheck script file path(e.g. projects/scripts/plot.py)\n"+'\033[0m'
-          '\033[91m'+"\talias plot=\"python projects/scripts/plot.py\"\n"+'\033[0m'
-          "\n1. Plotting multiple y values from same csv file\n"
+          '\033[92m'+"\tCheck script file path(e.g. projects/scripts/plot.py)\n"+'\033[0m'
+          '\033[92m'+"\talias plot=\"python projects/scripts/plot.py\"\n"+'\033[0m'
[…]

### 2020-11-08 scripts/plot.py
plotting_script update

@@ -89,10 +89,10 @@ if fmode == False:
     markers = ["",""]
     palette = plt.get_cmap('gray')  # Black and White Scale
 else:
-    # markers = ["","s", "o", "v","X"]
     markers = ["",""]
-    # palette = plt.get_cmap('gray')  # Black and White Scale
     palette = plt.get_cmap('Set1')  # Color Scale, {Set1,Set2,Set3,Dark2,tab10},tab20,Pastel1}
+    # markers = ["","s", "o", "v","X"]
+    # palette = plt.get_cmap('gray')  # Black and White Scale
 
 #=============================================================================
 

### 2020-11-08 scripts/plot.py
plotting_script update

@@ -89,8 +89,10 @@ if fmode == False:
     markers = ["",""]
     palette = plt.get_cmap('gray')  # Black and White Scale
 else:
+    #option 1 : use different colors
     markers = ["",""]
     palette = plt.get_cmap('Set1')  # Color Scale, {Set1,Set2,Set3,Dark2,tab10},tab20,Pastel1}
+    #option 2 : use different markers
     # markers = ["","s", "o", "v","X"]
     # palette = plt.get_cmap('gray')  # Black and White Scale
 

### 2020-11-08 examples/point_defects/article/article_plot.py
plotting_script update

@@ -191,7 +191,10 @@ ax.spines['top'].set_visible(True)
 
 # Labels
 plt.xlim(xmin,xmax)
-ax.tick_params(axis='both')
+ax.xaxis.set_tick_params(which='major', size=5, width=1, direction='in', top='on')
+ax.xaxis.set_tick_params(which='minor', size=3, width=1, direction='in', top='on')
+ax.yaxis.set_tick_params(which='major', size=5, width=1, direction='in', right='on')
+ax.yaxis.set_tick_params(which='minor', size=3, width=1, direction='in', right='on')
 ax.set_xlabel(xlbl)
 ax.set_ylabel(ylbl)
 # plt.axis('equal')               # fix x and y axis

### 2020-11-08 scripts/plot.py

@@ -6,11 +6,11 @@ import pandas as pd
 import matplotlib.pyplot as plt
 
 
-                # ------------------------------------------------------- #
-                # ======================================================= #
-                # Pyhton script to plot data from MOOSE csv output files. #
-                # ======================================================= #
-                # ----------------------------------------------eigenturk #
+# -------------------------------------------------------------------------------------------------------------- #
+# ============================================================================================================== #
+#                           Pyhton script to plot data from MOOSE csv output files.                              #
+# ============================================================================================================== #
+# -----------------------------------------------------------------------------------------------------eigenturk #
 
 
 def getHelp():
@@ -26,19 +26,21 @@ def getHelp():
           "\tcolumn_number\t\tThe column number of the data in csv file\n\n"
           "Optional arguments:\n\n"
           "  -h, Show this help message and exit.\n"
-          "  -s, Save only mode, plot wont be shown.\n\n"
+          "  -s, Save only mode, plot wont be shown.\n"
+          "  -g, Gray scale mode, plot will be in black and white scale.\n\n"
           "  -f, Multiple file mode."+'\033[91m'+" << ! Depricated, will be deleted. !\n\n"+'\033[0m'
           '\033[4m'+'\033[1m'+"Manual for commands :\n\n"+'\033[0m'
-          "Note  : To make using this script easy, create 'plot' command by adding following line to bash profile.\n"
-          '\033[92m'+"\tCheck script file path(e.g. projects/scripts/plot.py)\n"+'\033[0m'
+          "Note  : To make it easy, create 'plot' command by adding following line to your shell profile.\n"
           '\033[92m'+"\talias plot=\"python projects/scripts/plot.py\"\n"+'\033[0m'
           "\n-Plotting data from a single file\n"
-          '\033[93m'+"\tplot filename column_number(x) column_number(y1) column_number(y2)....column_number(yn)\n"+'\033[0m'
[…]

### 2020-11-09 examples/point_defects/article/article_plot.py
injected_interstitials

@@ -6,11 +6,11 @@ import pandas as pd
 import matplotlib.pyplot as plt
 
 
-                # ------------------------------------------------------- #
-                # ======================================================= #
-                # Pyhton script to plot data from MOOSE csv output files. #
-                # ======================================================= #
-                # ----------------------------------------------eigenturk #
+# -------------------------------------------------------------------------------------------------------------- #
+# ============================================================================================================== #
+#                           Pyhton script to plot data from MOOSE csv output files.                              #
+# ============================================================================================================== #
+# -----------------------------------------------------------------------------------------------------eigenturk #
 
 
 def getHelp():
@@ -26,19 +26,21 @@ def getHelp():
           "\tcolumn_number\t\tThe column number of the data in csv file\n\n"
           "Optional arguments:\n\n"
           "  -h, Show this help message and exit.\n"
-          "  -s, Save only mode, plot wont be shown.\n\n"
+          "  -s, Save only mode, plot wont be shown.\n"
+          "  -g, Gray scale mode, plot will be in black and white scale.\n\n"
           "  -f, Multiple file mode."+'\033[91m'+" << ! Depricated, will be deleted. !\n\n"+'\033[0m'
           '\033[4m'+'\033[1m'+"Manual for commands :\n\n"+'\033[0m'
-          "Note  : To make using this script easy, create 'plot' command by adding following line to bash profile.\n"
-          '\033[92m'+"\tCheck script file path(e.g. projects/scripts/plot.py)\n"+'\033[0m'
+          "Note  : To make it easy, create 'plot' command by adding following line to your shell profile.\n"
           '\033[92m'+"\talias plot=\"python projects/scripts/plot.py\"\n"+'\033[0m'
           "\n-Plotting data from a single file\n"
-          '\033[93m'+"\tplot filename column_number(x) column_number(y1) column_number(y2)....column_number(yn)\n"+'\033[0m'
[…]

### 2020-11-09 examples/point_defects/monocrystal/Nickel/Nickel_1D/coordinate_systems/500nm/Nickel_1D_uniform+boundary_sink_1e18_773K/Nickel_1D_uniform+boundary_sink_1e18_773K_1e-6/Nickel_1D_uniform+boundary_sink_1e18_773K_1e-6_0%/spherical-zero_recomb/analytical.py

@@ -1,21 +1,24 @@
+import matplotlib.pyplot as plt
 import numpy as np
 import math
-Cs=1e18
-Di=1.1066108307323346e-09
-Dv=2.0050685348844685e-13
-k0=1e-6
-kis=4.8949408023459335e-17
-kvs=8.869144879425032e-21
-a=500
+Cs=1.206e-11
+Di=1
+Dv=0.00018119003349692062
+k0=9.036600512379032e-16
+kis=3667.79639822092
+kvs=0.6645681522535332
+a=5000
 ki=(kis*Cs/Di)**0.5
 kv=(kvs*Cs/Dv)**0.5
 x=[]
 ci=[]
 cv=[]
-for i in range(0,500):
+for i in range(1,5000):
     print(i)
     x.append(i)
     ci.append((k0/(Di*ki*ki))*(1-a*math.sinh(ki*x[i])/(x[i]*math.sinh(ki*a))))
     cv.append((k0/(Dv*kv*kv))*(1-a*math.sinh(kv*x[i])/(x[i]*math.sinh(kv*a))))
 
-print(ci,cv)
+fig = plt.figure(figsize=(5, 5))
+plt.plot(x,ci)
+plt.plot(x,cv)

### 2020-11-09 scripts/plot.py

@@ -64,7 +64,7 @@ if sys.argv[-2]=="-"+"g" or sys.argv[-1]=="-"+"g":
     n=n-1
 
 if re.search(".csv",file.readlines()[0]):
-    print('\033[92m'+"Multiple File Mode : Data from multiple files was plotted on the same figure."+'\033[0m')
+    print('\033[92m'+"Multiple File Mode : Data from multiple files was plotted on the same figure.\n"+'\033[0m')
     fmode = True
     # Read file names from file
     csvfile=[]
@@ -74,7 +74,7 @@ if re.search(".csv",file.readlines()[0]):
         csvfile.append(filenames[i][:-1])
 else:
     fmode = False
-    print('\033[92m'+"Single File Mode : Data from a single file was plotted."+'\033[0m')
+    print('\033[92m'+"Single File Mode : Data from a single file was plotted.\n"+'\033[0m')
     csvfile = [filename]
 
 smode = False
@@ -94,7 +94,7 @@ ax = fig.add_subplot(1, 1, 1)
 
 # Plotting Style,Color Palette,Markers and Line Styles
 linestyles = ["solid","dotted","dashdot","dashed"]
-markers = ["",""]
+markers = ["","","","",""]
 plt.style.use('seaborn-whitegrid')
 
 if gmode == True: # Use Gray Color Scale
@@ -108,7 +108,7 @@ else: # Colorful plotting
 #=============================================================================
 
 for fid in range(0,len(csvfile)):
-    print(csvfile[fid][-30:])
+    print('\033[92m'+"Reading file......"+'\033[0m'+csvfile[fid][-40:])
     with open(csvfile[fid], 'r') as f:
         reader = csv.reader(f, delimiter=',')
         headers = next(reader)
@@ -122,7 +122,7 @@ for fid in range(0,len(csvfile)):
     df=pd.DataFrame(data,columns=headers)
 
     # Read Command Line Arguments
-    log = [0]*n
+    log = [0]*n  #list to check if log-plot was requested for commandline argument
     for i in range(2,n):
         c=0
         if isinstance(sys.argv[i][0],str):
@@ -146,10 +146,10 @@ for fid in range(0,len(csvfile)):
     # ylbl = "y(x) [unit]"       # define y label manually
 
     #Axis Limits
-    xmin=np.min(data[:, int(sys.argv[2])])
-    xmax=np.max(data[:, int(sys.argv[2])])
[…]

### 2020-11-09 scripts/plot.py
injected_interstitials

@@ -23,7 +23,7 @@ def getHelp():
           "Usage: plot [filename] [column_number1] [column_number2] ... [-h] [-s]\n\n"
           "Arguments:\n\n"
           "\tfilename\t\tName of the data file with extension\n"
-          "\tcolumn_number\t\tThe column number of the data in csv file\n\n"
+          "\tcolumn(number or name)\t\tThe column number(name) of the data in csv file\n\n"
           "Optional arguments:\n\n"
           "  -h, Show this help message and exit.\n"
           "  -s, Save only mode, plot wont be shown.\n"
@@ -33,14 +33,14 @@ def getHelp():
           "Note  : To make it easy, create 'plot' command by adding following line to your shell profile.\n"
           '\033[92m'+"\talias plot=\"python projects/scripts/plot.py\"\n"+'\033[0m'
           "\n-Plotting data from a single file\n"
-          '\033[93m'+"\tplot filename column_number(x) column_number(y1).....column_number(yn)\n"+'\033[0m'
+          '\033[93m'+"\tplot filename column_x column_y1.....column_yn\n"+'\033[0m'
           "\n-Plotting data from multiple files\n"
           '\033[91m'+"\tFirst, append name of all csv files to a seperate file (e.g. \"csvfiles\"),then use name of that file in command line.\n"
-          '\033[93m'+"\tplot csvfiles column_number(x) column_number(y)\n"+'\033[0m'
+          '\033[93m'+"\tplot csvfiles column_x column_y\n"+'\033[0m'
           "\n-Save a plot without showing it by adding \"-s\" at end of the command\n"
-          '\033[93m'+"\tplot filename column_number(x) column_number(y1).....column_number(yn) -s\n"+'\033[0m'
+          '\033[93m'+"\tplot filename column_x column_y1.....column_yn -s\n"+'\033[0m'
           "\n-Use gray color scale for plotting by adding \"-g\" at end of the command\n"
-          '\033[93m'+"\tplot filename column_number(x) column_number(y1).....column_number(yn) -g\n"+'\033[0m')
+          '\033[93m'+"\tplot filename column_x column_y1.....column_yn -g\n"+'\033[0m')
     sys.exit()
 
 if sys.argv[-1]=="-"+"h":

### 2020-11-20 examples/point_defects/article/article.tex
article latex file

@@
 \usepackage{graphicx}
-\pagenumbering{gobble}
 \usepackage{verbatim}
+\pagenumbering{arabic}
+\graphicspath{ {./plots/} }
 
@@
 
+% \tableofcontents
+
 \title{Numerical Solution of Point Defect Equations by MOOSE}
@@
 % \date{} % Comment this line to show today's date
-
 \begin{document}
@@
 \keywords{point defect equations, rate theory, radiation damage, MOOSE}
-% \begin{thebibliography}{00}
-% \bibitem{b2} Garry Was.
-% \end{thebibliography}
 %TC:endignore
@@
 
+% \listoftables
+% \listoffigures
+
 \section{Introduction} \hspace{10pt}
@@
 \section{Methodology} \hspace{10pt}
+
+\begin{table}[h!]
+  \centering
+  \caption{Material Properties for Nickel\cite{walgraef1996}}
+  \label{table:1}
+  \begin{tabular}{ ||p{2cm}|p{2cm}||  }
+     % \hline
+     % \multicolumn{5}{|c|}{Material Properties} \\
+     \hline
+     Property & Value\\
+     \hline\hline
+     a  & 0.352 nm\\
+     V  & 0.01206 nm^3\\
+     E_{m,i}  & 0.30 eV\\
+     E_{m,v}  & 1.30 eV\\
+     E_{f,i}  & 4.27 eV\\
+     E_{f,v}  & 1.60 eV\\
+     D_{0,i}  & 1e-7 m^2/s\\
+     D_{0,v}  & 6e-5 m^2/s\\
+
+     \hline
+  \end{tabular}
+\end{table}
+
+\begin{table}[h!]
+  \centering
+  \caption{Simulation Parameters}
+  \label{table:2}
+  \begin{tabular}{ ||p{2cm}|p{2cm}|p{4cm}|p{2cm}|p{2cm}||  }
+     % \multicolumn{5}{|c|}{Simulation Parameters} \\
+     \hline
+     Type & Dose Rate & Defect Production Profile & Temperature & Sink Density\\
+     \hline
+     \hline
+     Neutron  & 1e-3  & Uniform     & 773K & 1e18\\
+              & 1e-6  & Uniform     & 773K & 1e18\\
+     \hline
+     Ion      & 1e-3  & Distributed & 773K & 1e18\\
+              & 1e-6  & Distributed & 773K & 1e18\\
+     \hline
+  \end{tabular}
+\end{table}
 
@@
 T=773K, K 0 =1e-3 dpa/s.
+
+  \subsection{Neutron Irradiation}
+    \subsubsection{Concentrations}
+      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-0}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-0}}
+        \caption{Concentration profiles for 1e-6 dpa/s and 0\% Production Bias}
+        \label{figure:1}
+      \end{figure}
+      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-0}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-0}}
+        \caption{Concentration profiles for 1e-3 dpa/s and 0\% Production Bias}
+        \label{figure:2}
+      \end{figure}
+      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-5}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-5}}
+        \caption{Concentration profiles for 1e-6 dpa/s and 5\% Production Bias}
+        \label{figure:3}
+      \end{figure}
+      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-5}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-5}}
+        \caption{Concentration profiles for 1e-3 dpa/s and 5\% Production Bias}
+        \label{figure:4}
+      \end{figure}
+      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-neutron-5}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-high_neutron-5}}
+        \caption{Vacancy Supersaturation profiles for 1e-6 dpa/s and 1e-3 dpa/s with 5\% Production Bias}
+        \label{figure:5}
+      \end{figure}
+    \subsubsection{Sink Strengths}
+      \begin{figure}[h!]
+        \centering
+        \includegraphics[scale=0.6]{concentration_proflies_MOOSE_Analytical_Neutron_0}
+        \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.\cite{heald1977}}
+        \label{figure:6}
+      \end{figure}
+
+  \subsection{Ion Irradiation}
+    \subsubsection{Concentrations}
+      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-0}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-0}}
+        \caption{Concentration profiles for 1e-6 dpa/s and 0\% Production Bias}
+        \label{figure:7}
+      \end{figure}
+      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-0}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-0}}
+        \caption{Concentration profiles for 1e-3 dpa/s and 0\% Production Bias}
+        \label{figure:8}
+      \end{figure}
+      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-5}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-5}}
+        \caption{Concentration profiles for 1e-6 dpa/s and 5\% Production Bias}
+        \label{figure:9}
+      \end{figure}
+      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-5}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-5}}
+        \caption{Concentration profiles for 1e-3 dpa/s and 5\% Production Bias}
+        \label{figure:10}
+      \end{figure}
+      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-ion-5}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-low_ion-5}}
+        \caption{Vacancy Supersaturation profiles for 1e-6 dpa/s and 1e-3 dpa/s with 5\% Production Bias}
+        \label{figure:11}
+      \end{figure}
+
+    \subsubsection{Sink Strengths}
+
 In nano-scale case, since the domain size is not big enough, the boundaries become
@@
 Based on this, if the production rate increased sufficiently, the recombination zone would
-appear again in nano-scale domain.
+appear again in nano-scale domain.\cite{was2016}
+
+\section{Conclusion} \hspace{10pt}
+
+% \begin{thebibliography}{00}
+% \bibitem{b2} Garry S. Was.
+% \end{thebibliography}
+\addcontentsline{toc}{section}{References}
+\bibliographystyle{unsrt}
+\bibliography{ref}
 

### 2020-11-20 scripts/plot_lengthscaled.py

@@ -1,3 +1,4 @@
+import re
 import os
 import sys
 import csv
@@ -5,8 +6,18 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 
-# scale = 9.036600512379032e-12 # for time scale
-scale = 1e-1 #for length scale
+
+# -------------------------------------------------------------------------------------------------------------- #
+# ============================================================================================================== #
+#                           Pyhton script to plot data from MOOSE csv output files.                              #
+# ============================================================================================================== #
+# -----------------------------------------------------------------------------------------------------eigenturk #
+
+scale = 1e-1 # scaling factor for imported DATA
+
+w = 9.036600512379032e-12 #time scale used in MOOSE
+l = 1e-10  #length scale used in MOOSE
+domain = "full"   #full or half
 
 def getHelp():
     print('\033[96m'+"\n# ------------------------------------------------------- #\n"
@@ -15,115 +26,153 @@ def getHelp():
           "# ======================================================= #\n"
           "# ----------------------------------------------eigenturk #\n"+'\033[0m')
     print("This script is a tool for plotting csv files based on specified column numbers.\n\n"
-          "Usage: plot [filename] [column_number1] [column_number2] ... [-f] [-s]\n\n"
+          "Usage: plot [filename] [column_number1] [column_number2] ... [-h] [-s]\n\n"
           "Arguments:\n\n"
           "\tfilename\t\tName of the data file with extension\n"
-          "\tcolumn_number\t\tThe column number of the data in csv file\n\n"
+          "\tcolumn(number or name)\t\tThe column number(name) of the data in csv file\n\n"
           "Optional arguments:\n\n"
           "  -h, Show this help message and exit.\n"
[…]

### 2020-12-02 examples/point_defects/article/article.tex
imperfect-article

@@
 %TC:ignore
-\keywords{point defect equations, rate theory, radiation damage, MOOSE}
+\keywords{point defect equations, rate theory, interstitial, vacancy, radiation damage, MOOSE}
 %TC:endignore
@@
   \caption{Material Properties for Nickel\cite{walgraef1996}}
-  \label{table:1}
+  \label{table:Ni_material_properties}
   \begin{tabular}{ ||p{2cm}|p{2cm}||  }
@@
   \caption{Simulation Parameters}
-  \label{table:2}
-  \begin{tabular}{ ||p{2cm}|p{2cm}|p{4cm}|p{2cm}|p{2cm}||  }
+  \label{table:simulation_parameters}
+  \begin{tabular}{ ||p{2cm}|p{2cm}|p{3cm}|p{2cm}|p{2cm}||  }
      % \multicolumn{5}{|c|}{Simulation Parameters} \\
      \hline
-     Type & Dose Rate & Defect Production Profile & Temperature & Sink Density\\
+     Type & Dose Rate & Defect Production & Temperature & Sink Density\\
      \hline
      \hline
-     Neutron  & 1e-3  & Uniform     & 773K & 1e18\\
-              & 1e-6  & Uniform     & 773K & 1e18\\
+     Neutron  & 1e-3 dpa/s  & Uniform     & 773 K & 1e18 1/m^{3}\\
+              & 1e-6 dpa/s  & Uniform     & 773 K & 1e18 1/m^{3}\\
      \hline
-     Ion      & 1e-3  & Distributed & 773K & 1e18\\
-              & 1e-6  & Distributed & 773K & 1e18\\
+     Ion      & 1e-3 dpa/s  & Distributed & 773 K & 1e18 1/m^{3}\\
+              & 1e-6 dpa/s  & Distributed & 773 K & 1e18 1/m^{3}\\
      \hline
@@
 
+!!!mention!!! The production bias is a factor that is used to create a difference between interstitial
+and vacancy generation in domain.}
+
 \section{Results} \hspace{10pt}
 
-The production bias is a factor that is used to create a difference between interstitial
-and vacancy generation in domain. As the production bias increases, vacancy production
-increases and the gap between steady state vacancy and interstitial concentrations gets wider.
-Most of the plots in this part are generated by using the simulation results for Cs=1e18 m -3 ,
-T=773K, K 0 =1e-3 dpa/s.
+The simulation results for different irradiation types are presented by defect concentration, vacancy supersaturation as well as sink strength plots.
+The calculated sink strengths are also tabulated for different domain size and bias rates.
 
   \subsection{Neutron Irradiation}
-    \subsubsection{Concentrations}
+    \subsubsection{Concentrations} \hspace{10pt}
       \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
@@
         \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-0}}
-        \caption{Concentration profiles for 1e-6 dpa/s and 0\% Production Bias}
-        \label{figure:1}
+        \caption{Concentration profiles for neutron irradation with 0\% Production Bias}
+        \label{figure:concentrations_neutron_0_1e-6}
       \end{figure}
@@
         \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-0}}
-        \caption{Concentration profiles for 1e-3 dpa/s and 0\% Production Bias}
-        \label{figure:2}
+        \caption{Concentration profiles for high dose neutron irradation with 0\% Production Bias}
+        \label{figure:concentrations_neutron_0_1e-3}
       \end{figure}
@@
         \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-5}}
-        \caption{Concentration profiles for 1e-6 dpa/s and 5\% Production Bias}
-        \label{figure:3}
+        \caption{Concentration profiles for neutron irradation with 5\% Production Bias}
+        \label{figure:concentrations_neutron_5_1e-6}
       \end{figure}
@@
         \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-5}}
-        \caption{Concentration profiles for 1e-3 dpa/s and 5\% Production Bias}
-        \label{figure:4}
+        \caption{Concentration profiles for high dose neutron irradation with 5\% Production Bias}
+        \label{figure:concentrations_neutron_5_1e-3}
       \end{figure}
-      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
+      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
         \centering
@@
         \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-high_neutron-5}}
-        \caption{Vacancy Supersaturation profiles for 1e-6 dpa/s and 1e-3 dpa/s with 5\% Production Bias}
-        \label{figure:5}
+        \caption{Vacancy Supersaturation profiles for normal and high dose neutron irradation with 5\% Production Bias}
+        \label{figure:vacancy_supersaturation_neutron_5}
       \end{figure}
     \subsubsection{Sink Strengths}
+    The grain boundary sink strengths are calculated by using the equation \ref{equation:sink_strength}.
+First of all the defect concentration profile found by MOOSE is validated by comparing to analytical result as shown in Fig.\ref{figure:concentrations_MOOSE_analytical}
       \begin{figure}[h!]
         \centering
-        \includegraphics[scale=0.6]{concentration_proflies_MOOSE_Analytical_Neutron_0}
+        \includegraphics[scale=0.6]{concentration_profiles_MOOSE_Analytical_Neutron_0}
         \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.\cite{heald1977}}
-        \label{figure:6}
+        \label{figure:concentrations_MOOSE_analytical}
+      \end{figure}
+      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_k}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_Z}}
+        \caption{Sink Strengths for neutron irradiation with 0\% Production Bias}
+        \label{figure:sink_strengths_neutron_0_1e-6}
+      \end{figure}
+      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_k}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_Z}}
+        \caption{Sink Strengths for neutron irradation with 5\% Production Bias}
+        \label{figure:sink_strengths_neutron_5_1e-6}
       \end{figure}
@@
     \subsubsection{Concentrations}
-      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
+      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
         \centering
@@
         \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-0}}
-        \caption{Concentration profiles for 1e-6 dpa/s and 0\% Production Bias}
-        \label{figure:7}
+        \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
+        \label{figure:concentrations_ion_0_1e-6}
       \end{figure}
-      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
+      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
         \centering
@@
         \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-0}}
-        \caption{Concentration profiles for 1e-3 dpa/s and 0\% Production Bias}
-        \label{figure:8}
+        \caption{Concentration profiles for ion irradiation with 0\% Production Bias}
+        \label{figure:concentrations_ion_0_1e-3}
       \end{figure}
-      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
+      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
         \centering
@@
         \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-5}}
-        \caption{Concentration profiles for 1e-6 dpa/s and 5\% Production Bias}
-        \label{figure:9}
+        \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
+        \label{figure:concentrations_ion_5_1e-6}
       \end{figure}
-      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
+      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
         \centering
@@
         \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-5}}
-        \caption{Concentration profiles for 1e-3 dpa/s and 5\% Production Bias}
-        \label{figure:10}
+        \caption{Concentration profiles for ion irradation with 5\% Production Bias}
+        \label{figure:concentrations_ion_5_1e-3}
       \end{figure}
-      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
+      \begin{figure}[h!]  %Ion - %5 Bias rate
         \centering
@@
         \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-low_ion-5}}
-        \caption{Vacancy Supersaturation profiles for 1e-6 dpa/s and 1e-3 dpa/s with 5\% Production Bias}
-        \label{figure:11}
+        \caption{Vacancy Supersaturation profiles for low dose and ion irradation with 5\% Production Bias}
+        \label{figure:vacancy_supersaturation_ion_5}
       \end{figure}
@@
     \subsubsection{Sink Strengths}
+      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_0_k}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_0_Z}}
+        \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
+        \label{figure:sink_strengths_ion_0_1e-6}
+      \end{figure}
+      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 5% Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_5_k}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_5_Z}}
+        \caption{Sink Strengths for ion irradiation with 5\% Production Bias}
+        \label{figure:sink_strengths_ion_5_1e-6}
+      \end{figure}
 
@@
 
+The most significant parameters are found as domain size and bias rate as shown in plots in this section.
+
 % \begin{thebibliography}{00}

### 2020-12-02 scripts/plot.py

@@ -181,7 +181,7 @@ for fid in range(0,len(csvfile)):
             ymin=np.min(data[:, int(sys.argv[column])])
             ax.set_ylim(ymin,ymax)
         if np.ceil(np.max(data[:, int(sys.argv[column])]))>ymax:
-            np.ceil(ymax=np.max(data[:, int(sys.argv[column])]))
+            ymax=np.ceil(np.max(data[:, int(sys.argv[column])]))
             ax.set_ylim(ymin,ymax)
         num+=1
 

### 2020-12-02 scripts/plot_lengthscaled.py

@@ -49,28 +49,32 @@ def getHelp():
           '\033[93m'+"\tplot filename column_x column_y1.....column_yn -g\n"+'\033[0m')
     sys.exit()
 
-def getSinkStrength(df_unscaled,l,scale,domain="full"):
+def getSinkStrength(df,l,scale,domain="full"):
     ss_file = open('sink_strength_moose.csv', 'a')
-    nrow = df_unscaled.shape[0] #number of columns in dataframe
-    size = df_unscaled.loc[nrow-1,'x']/scale
+    nrow = df.shape[0] #number of columns in dataframe
+    size = df.loc[nrow-1,'x']
+    flow_area=1
+    if df.loc[nrow-1,'y']==0 and df.loc[nrow-1,'z']==0:
+        flow_area=size*size
     if domain == "half":
         print('\033[91m'+"Domain is choosen as \""+domain+"\""+'\033[0m')
-        xi = df_unscaled.loc[0,'xi']
-        xv = df_unscaled.loc[0,'xv']
+        xi = df.loc[0,'xi']  # left boundary(r=0) for spherical coordinate system
+        xv = df.loc[0,'xv']  # left boundary(r=0) for spherical coordinate system
     else:
-        xi = df_unscaled.loc[(nrow+1)/2,'xi']
-        xv = df_unscaled.loc[(nrow+1)/2,'xv']
-    Ji = df_unscaled.loc[nrow-1,'jix']
-    Jv = df_unscaled.loc[nrow-1,'jvx']
-    Di = df_unscaled.loc[(nrow+1)/2,'Di']
-    Dv = df_unscaled.loc[(nrow+1)/2,'Dv']
+        xi = df.loc[(nrow+1)/2,'xi']
+        xv = df.loc[(nrow+1)/2,'xv']
+    Ji = flow_area*df.loc[nrow-1,'jix']
+    Jv = flow_area*df.loc[nrow-1,'jvx']
+    Di = df.loc[(nrow+1)/2,'Di']
+    Dv = df.loc[(nrow+1)/2,'Dv']
     Zi = Ji/(xi*Di)
     Zv = Jv/(xv*Dv)
     rho = 6/(np.pi*(size*2)**3)
     ki = rho*Zi
     kv = rho*Zv
[…]

### 2020-12-07 examples/point_defects/article/article.tex
article-plots

@@
 
-  \subsection{Neutron Irradiation}
+  \subsection{Neutron Irradiation} \hspace{10pt}
+  Neutrons have an energy spectrum that varies a couple of orders of magnitude.
+This makes defect generation possible at different energies.
+Also, the high penetration depth of neutrons allow them travel through material corresponding to their energy and end up with an uniform or flat-like defect profiles.
     \subsubsection{Concentrations} \hspace{10pt}
@@
 
-  \subsection{Ion Irradiation}
+  \subsection{Ion Irradiation} \hspace{10pt}
+  Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic.
+Furtmermore, they cannot penetrate through material a lot because of high energy loss in collisions.
+These characteristic causes a non-uniform defect profiles.
     \subsubsection{Concentrations}

### 2020-12-07 scripts/plot_lengthscaled.py
500nm-bias rate

@@ -58,17 +58,19 @@ def getSinkStrength(df,l,scale,domain="full"):
         flow_area=size*size
     if domain == "half":
         print('\033[91m'+"Domain is choosen as \""+domain+"\""+'\033[0m')
-        xi = df.loc[0,'xi']  # left boundary(r=0) for spherical coordinate system
-        xv = df.loc[0,'xv']  # left boundary(r=0) for spherical coordinate system
+        xi = df.loc[0,'xi']  # at center(r=0) for spherical coordinate system
+        xv = df.loc[0,'xv']  # at center(r=0) for spherical coordinate system
     else:
-        xi = df.loc[(nrow+1)/2,'xi']
-        xv = df.loc[(nrow+1)/2,'xv']
-    Ji = flow_area*df.loc[nrow-1,'jix']
-    Jv = flow_area*df.loc[nrow-1,'jvx']
+        xi = df.loc[(nrow+1)/2,'xi'] # at center for cartesian coordinate system
+        xv = df.loc[(nrow+1)/2,'xv'] # at center for cartesian coordinate system
+    Ji=df.loc[nrow-1,'jix']
+    Jv=df.loc[nrow-1,'jvx']
+    Fi = flow_area*Ji
+    Fv = flow_area*Jv
     Di = df.loc[(nrow+1)/2,'Di']
     Dv = df.loc[(nrow+1)/2,'Dv']
-    Zi = Ji/(xi*Di)
-    Zv = Jv/(xv*Dv)
+    Zi = Fi/(xi*Di)
+    Zv = Fv/(xv*Dv)
     rho = 6/(np.pi*(size*2)**3)
     ki = rho*Zi
     kv = rho*Zv
@@ -78,13 +80,13 @@ def getSinkStrength(df,l,scale,domain="full"):
     print("xv = "+str(xv)+", jvx = "+str(Jv)+", Dv = "+str(Dv))
     print('\033[93m'+"Zi: "+str(Zi)+" \nZv: "+str(Zv))
     print('\033[97m'+"ki^2: "+str(ki)+" \nkv^2: "+str(kv)+" "+'\033[0m')
[…]

### 2020-12-20 scripts/paramstudy.py
new results

@@ -55,20 +55,20 @@ def find_line(param,file,blockmode=False,filename=False):
                     if re.search(name,lines[i]):
                         linenum.append(i)
                         return linenum
-                sys.exit("Error! : "+name+" value is not defined input file.")
+                sys.exit("Error 58! : "+name+" value is not defined input file.")
             #Find the line including parameter
             if re.compile(name).search(line) and re.search("parametric study",line):
                 if re.search("_names",line):
                     subindex = 0
                     for subline in lines[index:]:
-                        if re.search("_values",subline):
+                        if re.search("_values",subline) or re.search("_expressions",subline):
                             linenum.append(index+subindex)
                         if re.compile(re.escape("[../]")).search(subline):
                             for back in range(index,0,-1):
-                                if re.search("_values",lines[back]):
+                                if re.search("_values",lines[back]) or re.search("_expressions",lines[back]):
                                     linenum.append(back)
                                 if re.compile(re.escape("[./")).search(lines[back]):
-                                    sys.exit("Error! : "+name+" value is not defined input file.")
+                                    sys.exit("Error 71! : "+name+" value is not defined input file.")
                         subindex += 1
                 linenum.append(index)
                 index += 1
@@ -85,13 +85,13 @@ def find_line(param,file,blockmode=False,filename=False):
                         if re.search("_names",subline):
                             _names_index = index+subindex
                             for _values_index in range(index,len(lines)):
-                                if re.search("_values",lines[_values_index]):
+                                if re.search("_values",lines[_values_index]) or re.search("_expressions",lines[_values_index]):
                                     linenum.append(_values_index)
                                     return linenum
                         linenum.append(index+subindex)
                         return linenum
                     if re.compile(re.escape("[../]")).search(subline):
-                        sys.exit("Error! : "+name+" is not defined in block "+block)
+                        sys.exit("Error 94! : "+name+" is not defined in block "+block)
                     subindex += 1
             else:
                 index += 1
@@ -101,7 +101,7 @@ def find_line(param,file,blockmode=False,filename=False):
 #Generate New Line
 def newline(values,runid,param,line,linenum,file):
     if param == "function" or param == "prop_values":
-        sys.exit("Error! : Specify variable name instead of "+param)
[…]

### 2020-12-20 examples/point_defects/article/article.tex
new-results

@@
 This makes defect generation possible at different energies.
-Also, the high penetration depth of neutrons allow them travel through material corresponding to their energy and end up with an uniform or flat-like defect profiles.
+Also, the high penetration depth of neutrons allow them travel through material corresponding to their energy and end up with an uniform or flat-like defect production profiles.
     \subsubsection{Concentrations} \hspace{10pt}
+    As a result of uniform defect production and sink at boundaries, the concentration profiles are symmetrical around domain center.
+For unbiased case, representing the equal amount of point defect production, the steady state value of concentrations are not changing significantly with increasing domain size as shown in Fig.
+\ref{figure:concentrations_neutron_0_1e-6}.
+The centerline concentration is sensitive to domain size and might change with increasing domain size.
+High neutron dose rate raises concentration levels and provides sharper and more stable profiles (see Fig.
+\ref{figure:concentrations_neutron_0_1e-3}) in the same domain.
+
       \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
@@
       \end{figure}
+      \hspace{10pt}
+      In reality, even though atomic collisions create vacancy-interstitial pairs, following events cause a gap between the amount of point defects.
+The amount of vacancies would be more than interstitials.
+Production bias is used to ensure this imbalance.
+Unlike unbiased case, the steady state concentration profiles change significantly.
+The centerline interstitial concentration decreases, and its profile turns down after a specific domain size (1000 nm).
+Moreover, the ratio between miniumum and maximum peaks gets bigger with increasing domain size, which could be explained as interstitial atom segregation near boundary.
+The vacancy concentration, on the other hand, increases proportional to domain size, and its profile having peak at higher concentrations as shown in Fig.
+\ref{figure:concentrations_neutron_5_1e-6}.
+Similar to unbiased case, average concentration levels increases with dose rate.
+But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller domain sizes than 500 nm (see Fig.
+\ref{figure:concentrations_neutron_5_1e-3}).
       \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
@@
   Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic.
-Furtmermore, they cannot penetrate through material a lot because of high energy loss in collisions.
+Furtmermore, they cannot penetrate through material too much because of their high energy loss in collisions.
 These characteristic causes a non-uniform defect profiles.
+The Fig.
+\ref{figure:defect_production_500-5000nm} shows the defect production profiles in different domain sizes for ion irradation.
+    \begin{figure}[h!]  %Ion irradation
+      \centering
+      \subfloat{\includegraphics[scale=0.6]{defect_production_500-5000nm}}
+      \qquad
+      \caption{Defect production profiles for ion irradation.}
+      \label{figure:defect_production_500-5000nm}
+    \end{figure}
     \subsubsection{Concentrations}
@@
 The most significant parameters are found as domain size and bias rate as shown in plots in this section.
-
+The shape of profile is defined by balance between parameters(bias,dose rate, domain size,..)
+An online tool could be created to play with different parameters.
 % \begin{thebibliography}{00}

### 2020-12-20 examples/point_defects/article/article.tex
article-edit

@@
 
-The simulation results for different irradiation types are presented by defect concentration, vacancy supersaturation as well as sink strength plots.
-The calculated sink strengths are also tabulated for different domain size and bias rates.
+In reactor environment, materials are exposed to different types of particle radiation such as electron, proton, neutron and ion.
+This study covers two most significant irradation types, neutrons and ions.
+The results obtained from MOOSE simulations are presented in this section by plots of defect concentration, vacancy supersaturation and sink strengths.
+%The calculated sink strengths are also tabulated for different domain size and bias rates.
 
@@
 This makes defect generation possible at different energies.
-Also, the high penetration depth of neutrons allow them travel through material corresponding to their energy and end up with an uniform or flat-like defect production profiles.
+Also, the high penetration depth of neutrons allow them travel through material corresponding to their energy and end up with a uniform or flat-like defect production profiles.
     \subsubsection{Concentrations} \hspace{10pt}
-    As a result of uniform defect production and sink at boundaries, the concentration profiles are symmetrical around domain center.
-For unbiased case, representing the equal amount of point defect production, the steady state value of concentrations are not changing significantly with increasing domain size as shown in Fig.
+    Even though atomic collisions create vacancy-interstitial pairs, following events creates gap between the amount of point defects in favor of vacancies.
+At steady state condition, there are more vacancies than interstitials in microstructure.
+Since producing equal amount of point defects is not physically correct, production bias is used to ensure this imbalance while modeling point defects.
+For unbiased case, as a result of uniform defect production and reaching equilibrium at boundaries, the concentration profiles are symmetrical around domain center.
+The steady state concentration at center is not changing significantly with increasing size as shown in Fig.
 \ref{figure:concentrations_neutron_0_1e-6}.
-The centerline concentration is sensitive to domain size and might change with increasing domain size.
-High neutron dose rate raises concentration levels and provides sharper and more stable profiles (see Fig.
-\ref{figure:concentrations_neutron_0_1e-3}) in the same domain.
+In case of high neutron dose rate, concentration levels increase, profiles become more stable (see Fig.
+\ref{figure:concentrations_neutron_0_1e-3}).
 
@@
       \hspace{10pt}
-      In reality, even though atomic collisions create vacancy-interstitial pairs, following events cause a gap between the amount of point defects.
-The amount of vacancies would be more than interstitials.
-Production bias is used to ensure this imbalance.
        Unlike unbiased case, the steady state concentration profiles change significantly.
-The centerline interstitial concentration decreases, and its profile turns down after a specific domain size (1000 nm).
-Moreover, the ratio between miniumum and maximum peaks gets bigger with increasing domain size, which could be explained as interstitial atom segregation near boundary.
+The interstitial concentration at center decreases, and its spatial profile turns down after a specific domain size (1000 nm in Fig.
+\ref{figure:concentrations_neutron_5_1e-6}).
+Moreover, the depth of profile gets larger with increasing domain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary.
 The vacancy concentration, on the other hand, increases proportional to domain size, and its profile having peak at higher concentrations as shown in Fig.

### 2020-12-23 examples/point_defects/article/article.tex
article-edit

@@
 \section{Introduction} \hspace{10pt}
+\newpage
+\section{Methodology} \hspace{10pt}
 
-\section{Methodology} \hspace{10pt}
+\subsection{Point Defect Equations} \hspace{10pt}
+The irradiation of a material causes the creation of vacancies and interstitial because of
+atomic collisions. The point defects can diffuse through material, recombine with each other,
+and react with sinks which are present in microstructure. The concentration of point defects is
+described mathematically by the chemical rate balance equations given in following sets of equations.\\
+
+\begin{equation}
+  \begin{aligned}
+    &\frac{dC_i}{dt} = K_0 - K_{iv}C_iC_v - K_{is}C_iC_s + \nabla\cdot D_i\nabla C_i\\
+    &\frac{dC_v}{dt} = K_0 - K_{iv}C_iC_v - K_{vs}C_vC_s + \nabla\cdot D_v\nabla C_v\\
+  \end{aligned}}
+  \label{equation:point_defect_equations}
+\end{equation}\\
+
+There are different terms with different rate coefficients as seen in Eq.
+\ref{equation:point_defect_equations}.
+The first term on the RHS is a source term, representing defect generation with rate of K\textsubscript{0}.
+The second term is a reaction term, referring the recombination process if the defect x reacts with defect y with a rate of K\textsubscript{xy}.
+The third term is also a reaction term, representing the reaction between the defect x and the sink s with a rate of K\textsubscript{xs}.
+In this study, the sink concentration is assumed constant and uniformly distributed over domain.
+The last term is diffusion term which is resolving the spatial behavior of defects.\\
+
+Another form of point defect equations can be written by using sink strength, \textit{k} definition for sink reaction term.\\
+
+\begin{equation}
+  \begin{aligned}
+    &k_i^2D_iC_i = K_{is}C_iC_s \\
+    &k_v^2D_vC_v = K_{vs}C_vC_s \\
+  \end{aligned}}
+  \label{equation:sink_reaction_term}
+\end{equation}\\
+\begin{equation}
+  \begin{aligned}
+    &\frac{dC_i}{dt} = K_0 - K_{iv}C_iC_v - k_i^2D_iC_i + \nabla\cdot D_i\nabla C_i\\
+    &\frac{dC_v}{dt} = K_0 - K_{iv}C_iC_v - k_v^2D_vC_v + \nabla\cdot D_v\nabla C_v\\
+  \end{aligned}}
+  \label{equation:point_defect_equations_sink_strength}
+\end{equation}\\
+
+!!!mention!!! The production bias is a factor that is used to create a difference between interstitial and vacancy generation in domain.}
+
+\subsection{Non-dimensionalization of Point Defect Equations} \hspace{10pt}
+The time space of defect interactions is enormously large, which could differ from nanoseconds to hours.
+In addition, rate coefficients also have different orders.
+To make it easier to solve point defect equations numerically, their non-dimensionalized forms are implemented in MOOSE.
+The non-dimensionalization scheme and final form of equations are given in this section.
+
+\subsection{Model Settings and Parameters} \hspace{10pt}
+Nickel is selected as a base material, and its properties are used in calculations.
 
@@
 
-!!!mention!!! The production bias is a factor that is used to create a difference between interstitial
-and vacancy generation in domain.}
-
+\newpage
 \section{Results} \hspace{10pt}
@@
 This makes defect generation possible at different energies.
-Also, the high penetration depth of neutrons allow them travel through material corresponding to their energy and end up with a uniform or flat-like defect production profiles.
+Also, the high penetration depth of neutrons allow them to travel through material corresponding to their energies.
+Thus, they end up with a uniform or flat-like defect production profiles.
+
+  Numerical models are frequently used to solve scientific problems.
+Users of these models are making decisions based on results obtained from simulations, so the numerical approach should be reliable.
+Before presenting MOOSE results of this study, a simple 1D spherical grain approach is tested in MOOSE and the results are compared to analytical results for validation.
+
+  In this approach the recombination term in Eq.
+\ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\
+
+  \begin{equation}
+    \begin{aligned}
+      &0 = \frac{K_0}{D_i} - k_i^2C_i + \frac{d^2C_i}{dr^2}+\frac{2}{r}\frac{dC_i}{dr}\\
+      &0 = \frac{K_0}{D_v} - k_v^2C_v + \frac{d^2C_v}{dr^2}+\frac{2}{r}\frac{dC_v}{dr}\\
+    \end{aligned}}
+    \label{equation:spherical_norecomb_point_defect_equations}
+  \end{equation}\\
+  \begin{equation}
+    \begin{aligned}
+      &C_i(r)=\frac{K_0}{D_ik_i^2}\bigg(1-\frac{a\sinh{k_ir}}{r\sinh{k_ia}}\bigg)\\
+      &C_v(r)=\frac{K_0}{D_vk_v^2}\bigg(1-\frac{a\sinh{k_vr}}{r\sinh{k_va}}\bigg)\\
+    \end{aligned}}
+    \label{equation:spherical_grain_analytical_solution}
+  \end{equation}\\
+
+  As seen in Fig. \ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=0.55]{concentration_profiles_MOOSE_Analytical_Neutron_0}
+    \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.}
+    \label{figure:concentrations_MOOSE_analytical}
+  \end{figure}
     \subsubsection{Concentrations} \hspace{10pt}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-0}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-0}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
         \caption{Concentration profiles for neutron irradation with 0\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-0}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-0}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
         \caption{Concentration profiles for high dose neutron irradation with 0\% Production Bias}
@@
       \end{figure}
-      \hspace{10pt}
+
        Unlike unbiased case, the steady state concentration profiles change significantly.
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-5}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-5}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
         \caption{Concentration profiles for neutron irradation with 5\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-5}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-5}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
         \caption{Concentration profiles for high dose neutron irradation with 5\% Production Bias}
@@
       \end{figure}
+
+    \newpage
+    \subsubsection{Supersaturation} \hspace{10pt}
       \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
         \centering
-        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-neutron-5}}
+        \subfloat{\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-high_neutron-5}}
+        \subfloat{\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
         \caption{Vacancy Supersaturation profiles for normal and high dose neutron irradation with 5\% Production Bias}
@@
       \end{figure}
-    \subsubsection{Sink Strengths}
+
+    \newpage
+    \subsubsection{Sink Strengths} \hspace{10pt}
     The grain boundary sink strengths are calculated by using the equation \ref{equation:sink_strength}.
-First of all the defect concentration profile found by MOOSE is validated by comparing to analytical result as shown in Fig.\ref{figure:concentrations_MOOSE_analytical}
-      \begin{figure}[h!]
-        \centering
-        \includegraphics[scale=0.6]{concentration_profiles_MOOSE_Analytical_Neutron_0}
-        \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.\cite{heald1977}}
-        \label{figure:concentrations_MOOSE_analytical}
-      \end{figure}
       \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_k}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_k}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_Z}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_Z}}
         \caption{Sink Strengths for neutron irradiation with 0\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_k}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_Z}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z}}
         \caption{Sink Strengths for neutron irradation with 5\% Production Bias}
@@
   Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic.
-Furtmermore, they cannot penetrate through material too much because of their high energy loss in collisions.
+Furthermore, they cannot penetrate through material too much because of their high energy loss in collisions.
 These characteristic causes a non-uniform defect profiles.
@@
       \centering
-      \subfloat{\includegraphics[scale=0.6]{defect_production_500-5000nm}}
+      \subfloat{\includegraphics[scale=0.55]{defect_production_500-5000nm}}
       \qquad
@@
     \end{figure}
+    \newpage
     \subsubsection{Concentrations}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-0}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-0}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
         \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-0}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-0}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
         \caption{Concentration profiles for ion irradiation with 0\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-5}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-5}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
         \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-5}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-5}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
         \caption{Concentration profiles for ion irradation with 5\% Production Bias}
@@
       \end{figure}
+
+    \newpage
+    \subsubsection{Supersaturation}
       \begin{figure}[h!]  %Ion - %5 Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-ion-5}}
+        \subfloat{\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-low_ion-5}}
+        \subfloat{\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
         \caption{Vacancy Supersaturation profiles for low dose and ion irradation with 5\% Production Bias}
@@
 
+    \newpage
     \subsubsection{Sink Strengths}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_0_k}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_0_Z}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
         \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_5_k}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k}}
         \qquad
-        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_5_Z}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z}}
         \caption{Sink Strengths for ion irradiation with 5\% Production Bias}

### 2020-12-23 scripts/dataprep.py

@@ -1,0 +1,26 @@
+import numpy as np
+import math
+import subprocess
+import os
+import sys
+import csv
+
+# ------------------------------------------------------- #
+# ======================================================= #
+#     Pyhton script to create data file from CSV files    #
+# ======================================================= #
+# ----------------------------------------------eigenturk #
+
+n=len(sys.argv)
+csvfile=[]
+file = open(sys.argv[1])
+filenames = file.readlines()
+for i in range(0,len(filenames)):
+    csvfile.append(filenames[i][:-1])
+
+# open the file including csv file names`
+# store csv files into an array
+# input desired column numbers
+# loop over all csv files
+# loop over given columns and copy data to the new file
+# make sure data has headers and can be used for 3D plotting

### 2020-12-28 examples/point_defects/article/article.tex
article-edit

@@
 \title{Numerical Solution of Point Defect Equations by MOOSE}
-\author{Abdurrahman Ozturk$^{1}$, Karim Ahmed$^{1}$  \\
+\author{Abdurrahman Ozturk$^{1}$, Author2$^{1}$, Author3$^{1}$, Karim Ahmed$^{1}$  \\
         \small $^{1}$Texas A\&M University \\
@@
     &\frac{dC_i}{dt} = K_0 - K_{iv}C_iC_v - K_{is}C_iC_s + \nabla\cdot D_i\nabla C_i\\
-    &\frac{dC_v}{dt} = K_0 - K_{iv}C_iC_v - K_{vs}C_vC_s + \nabla\cdot D_v\nabla C_v\\
+    &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - K_{vs}C_vC_s + \nabla\cdot D_v\nabla C_v\\
   \end{aligned}}
@@
 \ref{equation:point_defect_equations}.
-The first term on the RHS is a source term, representing defect generation with rate of K\textsubscript{0}.
-The second term is a reaction term, referring the recombination process if the defect x reacts with defect y with a rate of K\textsubscript{xy}.
-The third term is also a reaction term, representing the reaction between the defect x and the sink s with a rate of K\textsubscript{xs}.
+The first term on the RHS is a source term, representing defect generation with rate of \textit{K\textsubscript{0}}.
+In vacancy equation, \textit{b} is used as percent production bias to create a difference between interstitial and vacancy generation in domain.
+The second term is a reaction term, referring the recombination process if the defect \textit{x} reacts with defect \textit{y} with a rate of \textit{K\textsubscript{xy}}.
+The third term is also a reaction term, representing the reaction between the defect \textit{x} and the sink \text{s} with a rate of \textit{K\textsubscript{xs}}.
 In this study, the sink concentration is assumed constant and uniformly distributed over domain.
@@
     &\frac{dC_i}{dt} = K_0 - K_{iv}C_iC_v - k_i^2D_iC_i + \nabla\cdot D_i\nabla C_i\\
-    &\frac{dC_v}{dt} = K_0 - K_{iv}C_iC_v - k_v^2D_vC_v + \nabla\cdot D_v\nabla C_v\\
+    &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - k_v^2D_vC_v + \nabla\cdot D_v\nabla C_v\\
   \end{aligned}}
@@
 \end{equation}\\
-
-!!!mention!!! The production bias is a factor that is used to create a difference between interstitial and vacancy generation in domain.}
 
@@
   \label{table:simulation_parameters}
-  \begin{tabular}{ ||p{2cm}|p{2cm}|p{3cm}|p{2cm}|p{2cm}||  }
+  \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}||  }
      % \multicolumn{5}{|c|}{Simulation Parameters} \\
      \hline
-     Type & Dose Rate & Defect Production & Temperature & Sink Density\\
+     Type & Dose Rate (dpa/s) & Defect Production & Temperature (K) & Sink Density (m^{-3})\\
      \hline
      \hline
-     Neutron  & 1e-3 dpa/s  & Uniform     & 773 K & 1e18 1/m^{3}\\
-              & 1e-6 dpa/s  & Uniform     & 773 K & 1e18 1/m^{3}\\
+     Neutron  & 1e-3  & Uniform     & 773 & 1e18\\
+              & 1e-6  & Uniform     & 773 & 1e18\\
      \hline
-     Ion      & 1e-3 dpa/s  & Distributed & 773 K & 1e18 1/m^{3}\\
-              & 1e-6 dpa/s  & Distributed & 773 K & 1e18 1/m^{3}\\
+     Ion      & 1e-3  & Distributed & 773 & 1e18\\
+              & 1e-6  & Distributed & 773 & 1e18\\
      \hline
@@
 Also, the high penetration depth of neutrons allow them to travel through material corresponding to their energies.
-Thus, they end up with a uniform or flat-like defect production profiles.
+Thus, they cause a uniform or flat-like defect production profile in material.\cite{was2016}
 
-  Numerical models are frequently used to solve scientific problems.
-Users of these models are making decisions based on results obtained from simulations, so the numerical approach should be reliable.
-Before presenting MOOSE results of this study, a simple 1D spherical grain approach is tested in MOOSE and the results are compared to analytical results for validation.
+  Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable.
+Before presenting results from this study, a simple 1D spherical grain problem for neutron irradation is solved by MOOSE, and its results are compared to analytical results for validation.
 
@@
 At steady state condition, there are more vacancies than interstitials in microstructure.
-Since producing equal amount of point defects is not physically correct, production bias is used to ensure this imbalance while modeling point defects.
-For unbiased case, as a result of uniform defect production and reaching equilibrium at boundaries, the concentration profiles are symmetrical around domain center.
+Since producing equal amount of point defects is not physically correct, production bias is used to ensure this imbalance in modeling point defects.
+For unbiased case, as a result of uniform defect production and equilibrium condition at boundaries, the concentration profiles are symmetrical around domain center.
 The steady state concentration at center is not changing significantly with increasing size as shown in Fig.
@@
 In case of high neutron dose rate, concentration levels increase, profiles become more stable (see Fig.
-\ref{figure:concentrations_neutron_0_1e-3}).
+\ref{figure:concentrations_neutron_0_1e-3}).\\
 
@@
         \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
-        \caption{Concentration profiles for neutron irradation with 0\% Production Bias}
+        \caption{Concentration profiles for low dose rate neutron irradation with 0\% Production Bias}
         \label{figure:concentrations_neutron_0_1e-6}
@@
       \end{figure}
-
-       Unlike unbiased case, the steady state concentration profiles change significantly.
-The interstitial concentration at center decreases, and its spatial profile turns down after a specific domain size (1000 nm in Fig.
+      \newpage
+       If production bias is applied, the steady state concentration profiles change significantly.
+The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical domain size} (${\sim}$1000 nm in Fig.
 \ref{figure:concentrations_neutron_5_1e-6}).
@@
 The vacancy concentration, on the other hand, increases proportional to domain size, and its profile having peak at higher concentrations as shown in Fig.
-\ref{figure:concentrations_neutron_5_1e-6}.
-Similar to unbiased case, average concentration levels increases with dose rate.
-But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller domain sizes than 500 nm (see Fig.
-\ref{figure:concentrations_neutron_5_1e-3}).
+\ref{figure:concentrations_neutron_5_1e-6}.\\
       \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
@@
         \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
-        \caption{Concentration profiles for neutron irradation with 5\% Production Bias}
+        \caption{Concentration profiles for low dose rate neutron irradation with 5\% Production Bias}
         \label{figure:concentrations_neutron_5_1e-6}
-      \end{figure}
-      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
+      \end{figure}\\
+
+      Similar to unbiased case, average concentration levels increases with dose rate.
+But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller domain sizes than 500 nm (see Fig.
+\ref{figure:concentrations_neutron_5_1e-3}).\\
+      \begin{figure}[htb!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
         \centering
@@
         \subfloat{\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
-        \caption{Vacancy Supersaturation profiles for normal and high dose neutron irradation with 5\% Production Bias}
+        \caption{Vacancy Supersaturation profiles for low and high dose neutron irradation with 5\% Production Bias}
         \label{figure:vacancy_supersaturation_neutron_5}
@@
         \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_Z}}
-        \caption{Sink Strengths for neutron irradiation with 0\% Production Bias}
+        \caption{Sink Strengths for low dose rate neutron irradiation with 0\% Production Bias}
         \label{figure:sink_strengths_neutron_0_1e-6}
@@
         \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z}}
-        \caption{Sink Strengths for neutron irradation with 5\% Production Bias}
+        \caption{Sink Strengths for low dose rate neutron irradation with 5\% Production Bias}
         \label{figure:sink_strengths_neutron_5_1e-6}
@@
 Furthermore, they cannot penetrate through material too much because of their high energy loss in collisions.
-These characteristic causes a non-uniform defect profiles.
-The Fig.
-\ref{figure:defect_production_500-5000nm} shows the defect production profiles in different domain sizes for ion irradation.
+These characteristic causes a non-uniform defect production profile.
+The defect production profile used for ion irradation simulations are shown in Fig.
+\ref{figure:defect_production}.
+The dose rate, K\textsubscript{0} and domain size (1000 nm) would be scaled for different cases, but the profile is going to stay unchanged.
     \begin{figure}[h!]  %Ion irradation
       \centering
-      \subfloat{\includegraphics[scale=0.55]{defect_production_500-5000nm}}
+      \subfloat{\includegraphics[scale=0.3]{defect_production}}
       \qquad
-      \caption{Defect production profiles for ion irradation.}
-      \label{figure:defect_production_500-5000nm}
+      \caption{Defect production profile for ion irradation.}
+      \label{figure:defect_production}
     \end{figure}
     \newpage
-    \subsubsection{Concentrations}
+    \subsubsection{Concentrations} \hspace{10pt}
+    The effect of defect production distribution is the first thing that can be observed easily on concentration profiles.
+Since, all defect production profiles having peak at around half of the domain, the concentration profiles are also showing the same behavior and reaching maximum at the center of domain, then waning through boundaries.
+
+    If production bias is zero, maximum concentration that point defects can reach is equal for all different domain sizes shown in Fig.
+\ref{figure:concentrations_ion_0_1e-6}.
+High ion dose rate is scaling up the concentration levels without making a significant change in profiles (see Fig.
+\ref{figure:concentrations_ion_0_1e-3}).
       \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
         \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
-        \caption{Concentration profiles for ion irradiation with 0\% Production Bias}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
+        \caption{Concentration profiles for high dose rate ion irradiation with 0\% Production Bias}
         \label{figure:concentrations_ion_0_1e-3}
       \end{figure}
+      \newpage
+      In case of applying production bias, profiles become completely different.
+Although the flipping behavior observed in neutron irradation case is also visible in ion irradation case, the non-uniform defect production causes asymmetrical interstitial concentration profile in Fig.
+\ref{figure:concentrations_ion_5_1e-6}.
+The vacancy concentration profiles also become asymmetrical and shift up with increasing domain size.
+Increasing ion dose rate from 1e-6 dpa/s to 1e-3 dpa/s reduces the effect of defect production profile as well as critical domain size to flip (see Fig.
+\ref{figure:concentrations_ion_5_1e-3}).
       \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
         \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
-        \caption{Concentration profiles for ion irradation with 5\% Production Bias}
+        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
+        \caption{Concentration profiles for high dose rate ion irradation with 5\% Production Bias}
         \label{figure:concentrations_ion_5_1e-3}
@@
         \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z}}
-        \caption{Sink Strengths for ion irradiation with 5\% Production Bias}
+        \caption{Sink Strengths for high dose rate ion irradiation with 5\% Production Bias}
         \label{figure:sink_strengths_ion_5_1e-6}
@@
 
-In nano-scale case, since the domain size is not big enough, the boundaries become
-closer to each other. This causes point defects to reach sinks before they react with each other
-and recombination plateau to disappear as it can be seen in Fig. 2. The nanoscale case acts like
-a high-sink and high-temp condition case despite its low-sink and low-temperature. Therefore,
-change in production bias does not have a significant effect on average concentration behavior
-in nanoscale
-
-On the other hand, in micro-scale case, the domain has reasonable size, and thus
-boundaries are far from each other. This provides defects more time to accumulate inside the
-domain and recombine with each other after they reach a specific concentration. Figure 3
-clearly shows the effect of production bias on average concentration.
-
-Effect of production bias on spatial profile of defect concentrations for nanoscale is
-shown in Figure 4. The results seem not affected too much because of the same reasons
-mentioned previously for average concentration.
-
-The micro-scale results (Fig. 5) are quite interesting and worth to think over. The
-concentration profiles of interstitials for 0.1%, 5% and 10% cases are flipped over. A closer look
-at evolution of 5% case over time in Fig. 6, after the end of quasi-steady-state region (t=10 -4 s in
-Fig 3.), the average interstitial concentration starts to decrease as they segregate through sinks.
-At steady state, the average interstitial concentration becomes minimum at the center and
-maximum near boundaries because of segregation.
-
-The defect production rate (K 0 ) is the source term in point defect equations and has a
-significant effect on concentrations.
-In nano-scale case, the average concentration behavior is like high-sink density behavior
-because of narrow domain. But, when the defect production rate increases, the average
-concentration is shifted upward, and interstitial and vacancy average concentrations get closer
-to each other because the production compensates more absorption at sinks than previous.
-Based on this, if the production rate increased sufficiently, the recombination zone would
-appear again in nano-scale domain.\cite{was2016}
+% In nano-scale case, since the domain size is not big enough, the boundaries become
+% closer to each other. This causes point defects to reach sinks before they react with each other
+% and recombination plateau to disappear as it can be seen in Fig. 2. The nanoscale case acts like
+% a high-sink and high-temp condition case despite its low-sink and low-temperature. Therefore,
+% change in production bias does not have a significant effect on average concentration behavior
+% in nanoscale
+%
+% On the other hand, in micro-scale case, the domain has reasonable size, and thus
+% boundaries are far from each other. This provides defects more time to accumulate inside the
+% domain and recombine with each other after they reach a specific concentration. Figure 3
+% clearly shows the effect of production bias on average concentration.
+%
+% Effect of production bias on spatial profile of defect concentrations for nanoscale is
+% shown in Figure 4. The results seem not affected too much because of the same reasons
+% mentioned previously for average concentration.
+%
+% The micro-scale results (Fig. 5) are quite interesting and worth to think over. The
+% concentration profiles of interstitials for 0.1%, 5% and 10% cases are flipped over. A closer look
+% at evolution of 5% case over time in Fig. 6, after the end of quasi-steady-state region (t=10 -4 s in
+% Fig 3.), the average interstitial concentration starts to decrease as they segregate through sinks.
+% At steady state, the average interstitial concentration becomes minimum at the center and
+% maximum near boundaries because of segregation.
+%
+% The defect production rate (K 0 ) is the source term in point defect equations and has a
+% significant effect on concentrations.
+% In nano-scale case, the average concentration behavior is like high-sink density behavior
+% because of narrow domain. But, when the defect production rate increases, the average
+% concentration is shifted upward, and interstitial and vacancy average concentrations get closer
+% to each other because the production compensates more absorption at sinks than previous.
+% Based on this, if the production rate increased sufficiently, the recombination zone would
+% appear again in nano-scale domain.
 
@@
 
-The most significant parameters are found as domain size and bias rate as shown in plots in this section.
-The shape of profile is defined by balance between parameters(bias,dose rate, domain size,..)
-An online tool could be created to play with different parameters.
+The rate theory equations resolve the temporal and spatial concentration profiles of point defects.
+The behavior of concentration distributions are controlled by parameters given in equation, representing their reactions and diffusion in domain.
+According to the results obtained in this study, the combination of production bias, production dose rate, production profile and domain size determine whether the steady state point defect concentration profile is symmetrical, flipped or both.
+There is always a critical value for parameters that could change the defect concentration profile entirely.
+
+% An online tool could be created to play with different parameters.
 % \begin{thebibliography}{00}

### 2020-12-28 examples/point_defects/article/article.tex
article-edit

@@
     &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - K_{vs}C_vC_s + \nabla\cdot D_v\nabla C_v\\
-  \end{aligned}}
+  \end{aligned}
   \label{equation:point_defect_equations}
@@
     &k_v^2D_vC_v = K_{vs}C_vC_s \\
-  \end{aligned}}
+  \end{aligned}
   \label{equation:sink_reaction_term}
@@
     &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - k_v^2D_vC_v + \nabla\cdot D_v\nabla C_v\\
-  \end{aligned}}
+  \end{aligned}
   \label{equation:point_defect_equations_sink_strength}
@@
   Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable.
-Before presenting results from this study, a simple 1D spherical grain problem for neutron irradation is solved by MOOSE, and its results are compared to analytical results for validation.
+Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE, and its results are compared to analytical results for validation.
 
-  In this approach the recombination term in Eq.
+  In this approach the mutual recombination term in Eq.
 \ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\
@@
       &0 = \frac{K_0}{D_v} - k_v^2C_v + \frac{d^2C_v}{dr^2}+\frac{2}{r}\frac{dC_v}{dr}\\
-    \end{aligned}}
+    \end{aligned}
     \label{equation:spherical_norecomb_point_defect_equations}
@@
       &C_v(r)=\frac{K_0}{D_vk_v^2}\bigg(1-\frac{a\sinh{k_vr}}{r\sinh{k_va}}\bigg)\\
-    \end{aligned}}
+    \end{aligned}
     \label{equation:spherical_grain_analytical_solution}
@@
     \includegraphics[scale=0.55]{concentration_profiles_MOOSE_Analytical_Neutron_0}
-    \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.}
+    \caption{Comparison of MOOSE results with analytical solution for spherical grain.}
     \label{figure:concentrations_MOOSE_analytical}
@@
     \subsubsection{Supersaturation} \hspace{10pt}
+    Supersaturation is a condition that the actual concentration of point defect is larger than its equilibrium concentration.
+The opposite condition is called undersaturation which is being smaller than equilibrium concentration.
+In both cases, the system is not at the minimum free energy.
+Both vacancies and interstitials could be supersaturated, then aggiomerate into voids or discs of interstitial atoms.
+These can produce stacking faults in crystal microstructure.
+
+    The effective vacancy supersaturation, ${S_v}$ is calculated by using following equation,\cite{was2016}\\
+
+    \begin{equation}
+      \begin{aligned}
+        &S_v=\frac{D_vC_v-D_iC_i}{D_vC_v^e}\\
+      \end{aligned}
+    \end{equation}\\
+
+    The vacancy supersaturation curves for biased neutron irradation is given in Fig.
+\ref{figure:vacancy_supersaturation_neutron_5}.
+Since the defect concentrations are symmetrical for neutron irradation, supersaturation curves are also symmetrical around domain center.
+The plot shows a non-linear increase in supersaturation values as domain gets larger.
       \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
@@
 
-    \newpage
     \subsubsection{Sink Strengths} \hspace{10pt}
-    The grain boundary sink strengths are calculated by using the equation \ref{equation:sink_strength}.
-      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
+    The sink reaction term in Eq.
+\ref{equation:point_defect_equations_sink_strength} represents the total loss of point defects to sinks that are voids and dislocations within the domain.
+It can be written in expanded form as below,
+
+    \begin{equation}
+      \begin{aligned}
+        &k^2DC=(Z\rho_d+4\pi r_h\rho_h)DC\\
+      \end{aligned}
+    \end{equation}\\
+    Similarly, grain boundary sink strength can be calculated by considering total flow of point defect to grain boundary.
+
+    \begin{equation}
+      \begin{aligned}
+        &F=Z_{gb}DC_0\\
+      \end{aligned}
+    \end{equation}
+
+    where ${F}$ is total flow at grain boundary, ${Z_{gb}}$ is grain boundary sink strength, ${D}$ is diffusion coefficient and ${C_0}$ is defect concentration at the domain center.\\\\
+    So that the grain boundary sink strength is
+
+    \begin{equation}
+      \begin{aligned}
+        &Z_{gb}=\frac{F}{DC_0}\\
+      \end{aligned}
+    \end{equation}\\
+    The total flow, ${F}$ is equal to current multiplied by surface area at grain boundary.
+${F}$ and ${C_0}$ can be taken from directly MOOSE simulation results.
+The total grain boundary sink strength, ${k^2_{gb}}$ is calculated by multiplying ${Z_{gb}}$ by the grain density, ${\rho_{gb}}$.\cite{heald1977}
+
+    \begin{equation}
+      \begin{aligned}
+        &\rho_{gb}=\frac{6}{\pi d^3}\\
+        &k^2_{gb}=\rho_{gb}Z_{gb}\\
+      \end{aligned}
+    \end{equation}
+
+    where ${d}$ is diameter of the grain, ${d=2a}$\\\\
+    Grain boundary sink strength, ${Z_{gb}}$ can also be calculated analytically by using Eq.
+\ref{equation:spherical_grain_analytical_solution} to find ${F}$ and ${C_0}$.
+This solution helps to associate the grain boundary sink strength with the domain sink strength, ${k^2}$.
+\cite{heald1977}\\
+
+    \begin{equation}
+      \begin{aligned}
+        &F=-\bigg(4\pi r^2D\frac{\partial C(r)}{\partial r}\bigg)_{r=a}\\
+        &C_0=C(r=0)\\
+        &Z_{gb}=4\pi a\bigg(\frac{ka\cosh ka-\sinh ka}{\sinh ka-ka}\bigg)\\
+        &\rho_{gb}=\frac{6}{\pi d^3}\\
+        &k^2_{gb}=\frac{12}{d^2}\bigg(\frac{ka\cosh ka-\sinh ka}{\sinh ka-ka}\bigg)\\
+      \end{aligned}
+    \end{equation}\\
+
+    Sink strengths are calculated based on MOOSE simulation results and presented in Fig.
+\ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}.
+The effect of flipping behavior is not visible in grain boundary sink strength, ${Z^{gb}}$ plot, but in total grain boundary sink strength, ${k^2}$ plot, there is a significant change on trend of ${k^2_i}$ line after critical domain size of ${\sim}$1000 nm.
+In high dose rate plot, the critical domain size is seen clearly around at ${\sim}$250 nm.
+      % \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
+      %   \centering
+      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_k}}
+      %   \qquad
+      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_Z}}
+      %   \caption{Sink Strengths for low dose rate neutron irradiation with 0\% Production Bias}
+      %   \label{figure:sink_strengths_neutron_0_1e-6}
+      % \end{figure}
+      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_k}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_Z}}
-        \caption{Sink Strengths for low dose rate neutron irradiation with 0\% Production Bias}
-        \label{figure:sink_strengths_neutron_0_1e-6}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
+        \caption{Sink Strengths for low dose rate neutron irradation with 5\% Production Bias}
+        \label{figure:sink_strengths_neutron_5_1e-6}
       \end{figure}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z}}
-        \caption{Sink Strengths for low dose rate neutron irradation with 5\% Production Bias}
-        \label{figure:sink_strengths_neutron_5_1e-6}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
+        \caption{Sink Strengths for high dose rate neutron irradation with 5\% Production Bias}
+        \label{figure:sink_strengths_neutron_5_1e-3}
       \end{figure}
-
+  \newpage
   \subsection{Ion Irradiation} \hspace{10pt}
@@
       \centering
-      \subfloat{\includegraphics[scale=0.3]{defect_production}}
+      \subfloat{\includegraphics[scale=0.27]{defect_production}}
       \qquad
@@
     \end{figure}
-    \newpage
     \subsubsection{Concentrations} \hspace{10pt}
@@
     \newpage
-    \subsubsection{Supersaturation}
+    \subsubsection{Supersaturation} \hspace{10pt}
+
+    The vacancy supersaturation curves for ion irradation case are quite similar to ones for neutron irradation case.
+The only difference is the asymmetrical shape of curves originates from concentration profiles.
+The non-linear increase in supersaturation values as domain gets larger is observed for ion irradation too.
       \begin{figure}[h!]  %Ion - %5 Bias rate
@@
       \end{figure}
-
-    \newpage
-    \subsubsection{Sink Strengths}
-      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
+    \subsubsection{Sink Strengths} \hspace{10pt}
+    The sink strengths are directly related to concentration at center and flow at boundary.
+The change in centerline defect concentrations are not as considerable as neutron case.
+So, the flow or flux at boundary becomes more dominant on sink strength profiles.
+      % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
+      %   \centering
+      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
+      %   \qquad
+      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
+      %   \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
+      %   \label{figure:sink_strengths_ion_0_1e-6}
+      % \end{figure}
+      \begin{figure}[h!]  %Sink Strength - ion 1e-6 dpa/s - 5% Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_Z_scaled}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
-        \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
-        \label{figure:sink_strengths_ion_0_1e-6}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
+        \caption{Sink Strengths for low dose rate ion irradiation with 5\% Production Bias}
+        \label{figure:sink_strengths_ion_5_1e-6}
       \end{figure}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
         \caption{Sink Strengths for high dose rate ion irradiation with 5\% Production Bias}
-        \label{figure:sink_strengths_ion_5_1e-6}
+        \label{figure:sink_strengths_ion_5_1e-3}
       \end{figure}
@@
 
+\newpage
 \section{Conclusion} \hspace{10pt}

### 2020-12-29 examples/point_defects/article/article.tex
article-edit

@@
        If production bias is applied, the steady state concentration profiles change significantly.
-The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical domain size} (${\sim}$1000 nm in Fig.
+The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig.
 \ref{figure:concentrations_neutron_5_1e-6}).
@@
 \ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}.
-The effect of flipping behavior is not visible in grain boundary sink strength, ${Z^{gb}}$ plot, but in total grain boundary sink strength, ${k^2}$ plot, there is a significant change on trend of ${k^2_i}$ line after critical domain size of ${\sim}$1000 nm.
-In high dose rate plot, the critical domain size is seen clearly around at ${\sim}$250 nm.
+The effect of flipping behavior is not visible in grain boundary sink strength, ${Z^{gb}}$ plot, but in total grain boundary sink strength, ${k^2}$ plot, there is a significant change on ${k^2_i}$ after critical grain size of ${\sim}$1000 nm.
+In high dose rate plot, the critical grain size is seen clearly around at ${\sim}$250 nm.
       % \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
@@
 The vacancy concentration profiles also become asymmetrical and shift up with increasing domain size.
-Increasing ion dose rate from 1e-6 dpa/s to 1e-3 dpa/s reduces the effect of defect production profile as well as critical domain size to flip (see Fig.
+Increasing ion dose rate from 1e-6 dpa/s to 1e-3 dpa/s reduces the effect of defect production profile as well as critical grain size to flip (see Fig.
 \ref{figure:concentrations_ion_5_1e-3}).
@@
 The change in centerline defect concentrations are not as considerable as neutron case.
-So, the flow or flux at boundary becomes more dominant on sink strength profiles.
+So, the flow or flux at boundary becomes more dominant on sink strength profiles (see Fig.
+\ref{figure:sink_strengths_ion_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}).
       % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate

### 2020-12-30 scripts/dataprep.py
article-edit

@@ -11,16 +11,23 @@ import csv
 # ======================================================= #
 # ----------------------------------------------eigenturk #
 
-n=len(sys.argv)
-csvfile=[]
-file = open(sys.argv[1])
-filenames = file.readlines()
-for i in range(0,len(filenames)):
-    csvfile.append(filenames[i][:-1])
+for i in range(1,len(sys.argv)):
+    if re.search("=",sys.argv[i]):
+        if sys.argv[i].split('=')[0]=='T':
+            T=float(sys.argv[i].split('=')[1])
+        elif sys.argv[i].split('=')[0]=='K0':
+            K0=float(sys.argv[i].split('=')[1])
+        elif sys.argv[i].split('=')[0]=='l':
+            l=float(sys.argv[i].split('=')[1])
+        elif sys.argv[i].split('=')[0]=='Cs':
+            Cs=float(sys.argv[i].split('=')[1])
 
-# open the file including csv file names`
+data_file = open('moose_data.csv', 'a')
+data_file.close()
+
+# open single/multiple file(s) including csv file names`
 # store csv files into an array
-# input desired column numbers
-# loop over all csv files
+# input desired column numbers or names
+# loop over csv file(s)
 # loop over given columns and copy data to the new file
 # make sure data has headers and can be used for 3D plotting

### 2020-12-30 scripts/plot_lengthscaled.py

@@ -17,7 +17,7 @@ scale = 1e-1 # scaling factor for imported DATA
 
 w = 9.036600512379032e-12 #time scale used in MOOSE
 l = 1e-10  #length scale used in MOOSE
-domain = "full"   #full or half
+coordinates = "spherical"   #cartesian or spherical
 
 def getHelp():
     print('\033[96m'+"\n# ------------------------------------------------------- #\n"
@@ -49,15 +49,18 @@ def getHelp():
           '\033[93m'+"\tplot filename column_x column_y1.....column_yn -g\n"+'\033[0m')
     sys.exit()
 
-def getSinkStrength(df,l,scale,domain="full"):
+def getSinkStrength(df,l,scale,coordinates="cartesian"):
     ss_file = open('sink_strength_moose.csv', 'a')
     nrow = df.shape[0] #number of columns in dataframe
-    size = df.loc[nrow-1,'x']
-    flow_area=1
-    if df.loc[nrow-1,'y']==0 and df.loc[nrow-1,'z']==0:
+    size = df.loc[nrow-1,'x']/scale
+    d = size
+    flow_area=1 # !check this number for 2D and 3D
+    if df.loc[nrow-1,'y']==0 and df.loc[nrow-1,'z']==0: # check 1D domain
         flow_area=size*size
-    if domain == "half":
-        print('\033[91m'+"Domain is choosen as \""+domain+"\""+'\033[0m')
+    if coordinates == "spherical": # for spherical grains
+        print('\033[91m'+"Coordinate system is \""+coordinates+"\""+'\033[0m')
+        d = size * 2 # dimater of grain
+        flow_area = 4*np.pi*size**2 # surface are of grain
         xi = df.loc[0,'xi']  # at center(r=0) for spherical coordinate system
         xv = df.loc[0,'xv']  # at center(r=0) for spherical coordinate system
     else:
@@ -71,7 +74,7 @@ def getSinkStrength(df,l,scale,domain="full"):
     Dv = df.loc[(nrow+1)/2,'Dv']
     Zi = Fi/(xi*Di)
     Zv = Fv/(xv*Dv)
-    rho = 6/(np.pi*(size*2)**3)
+    rho = 6/(np.pi*(d**3))
     ki = rho*Zi
     kv = rho*Zv
     print('\033[94m'+'\033[4m'+'\033[1m'+"\nNondimensionalized Results for length_scale= "+str(l)+" m"+'\033[0m')
[…]

### 2020-12-30 examples/point_defects/article/article.tex
article-edit

@@
   Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable.
-Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE, and its results are compared to analytical results for validation.
+Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE as bencmark problem, and its results are compared to analytical results for validation.
 
@@
         &F=Z_{gb}DC_0\\
+        &Z_{gb}=\frac{F}{DC_0}\\
       \end{aligned}
-    \end{equation}
+      \end{equation}\\
 
     where ${F}$ is total flow at grain boundary, ${Z_{gb}}$ is grain boundary sink strength, ${D}$ is diffusion coefficient and ${C_0}$ is defect concentration at the domain center.\\\\
-    So that the grain boundary sink strength is
+    The total flow at boundary is equal to multiplication of surface area and current as below,\\
 
@@
       \begin{aligned}
-        &Z_{gb}=\frac{F}{DC_0}\\
+        &F=-\bigg(4\pi r^2D\frac{\partial C(r)}{\partial r}\bigg)_{r=a}\\
       \end{aligned}
     \end{equation}\\
-    The total flow, ${F}$ is equal to current multiplied by surface area at grain boundary.
-${F}$ and ${C_0}$ can be taken from directly MOOSE simulation results.
     The total grain boundary sink strength, ${k^2_{gb}}$ is calculated by multiplying ${Z_{gb}}$ by the grain density, ${\rho_{gb}}$.\cite{heald1977}
-
     \begin{equation}
@@
     where ${d}$ is diameter of the grain, ${d=2a}$\\\\
-    Grain boundary sink strength, ${Z_{gb}}$ can also be calculated analytically by using Eq.
-\ref{equation:spherical_grain_analytical_solution} to find ${F}$ and ${C_0}$.
-This solution helps to associate the grain boundary sink strength with the domain sink strength, ${k^2}$.
-\cite{heald1977}\\
+    Grain boundary sink strengths, ${Z_{gb}}$ and ${k_{gb}}$, is calculated analytically by substituting Eq.
+\ref{equation:spherical_grain_analytical_solution} into expressions above.
+Thus, grain boundary sink strengths are associated with the domain sink strength, ${k^2}$.\cite{heald1977}
 
@@
       \begin{aligned}
-        &F=-\bigg(4\pi r^2D\frac{\partial C(r)}{\partial r}\bigg)_{r=a}\\
-        &C_0=C(r=0)\\
+        &C_0=C(r=0)=\frac{K_0}{Dk^2}\bigg(1-\frac{ka}{\sinh{ka}}\bigg)\\\\
+        &F=-\bigg(4\pi r^2D\frac{\partial C(r)}{\partial r}\bigg)_{r=a}=\frac{4\pi aK_0}{k^2}\bigg(ka\coth{ka}-1\bigg)\\
+      \end{aligned}
+    \end{equation}\\
+    So that, grain boundary sink strengths are
+    \begin{equation}
+      \begin{aligned}
         &Z_{gb}=4\pi a\bigg(\frac{ka\cosh ka-\sinh ka}{\sinh ka-ka}\bigg)\\
-        &\rho_{gb}=\frac{6}{\pi d^3}\\
         &k^2_{gb}=\frac{12}{d^2}\bigg(\frac{ka\cosh ka-\sinh ka}{\sinh ka-ka}\bigg)\\
@@
 
-    Sink strengths are calculated based on MOOSE simulation results and presented in Fig.
-\ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}.
+    Using appropriate diffusion coefficient (${D}$), domain sink strength (${k^2}$) and concentration (${C_0}$) will give  relevant sink strengths.
+The analytical expressions for each defect type given by following equations
+
+    \begin{equation}
+      \begin{aligned}
+        &Z_{gb,i}=4\pi a\bigg(\frac{k_ia\cosh k_ia-\sinh k_ia}{\sinh k_ia-k_ia}\bigg)\\
+        &k^2_{gb,i}=\frac{12}{d^2}\bigg(\frac{k_ia\cosh k_ia-\sinh k_ia}{\sinh k_ia-k_ia}\bigg)\\\\
+        &Z_{gb,v}=4\pi a\bigg(\frac{k_va\cosh k_va-\sinh k_va}{\sinh k_va-k_va}\bigg)\\
+        &k^2_{gb,v}=\frac{12}{d^2}\bigg(\frac{k_va\cosh k_va-\sinh k_va}{\sinh k_va-k_va}\bigg)\\
+      \end{aligned}
+    \end{equation}\\
+
+  The results of bencmark problem, previously discussed in Fig.
+\ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations.
+Table \ref{table:sink_strengths_calculations} show the comparison of calculations.
+    \begin{table}[h!]
+      \centering
+      \caption{Comparison of sink strength calculations}
+      \label{table:sink_strengths_calculations}
+      \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}||  }
+         \hline
+          & MOOSE & Analytical\\
+         \hline\hline\hline
+         ${Z_{gb,i}}$  & 1.257206e-05 m & 1.257332e-05 m\\
+         ${Z_{gb,v}}$  & 1.256941e-05 m & 1.257332e-05 m\\
+         ${k_{gb,i}}$  & 2.401086e+13 m^{-2} & 2.401327e+13 m^{-2}\\
+         ${k_{gb,v}}$  & 2.400580e+13 m^{-2} & 2.401327e+13 m^{-2}\\
+         \hline
+      \end{tabular}
+    \end{table}
+    \newpage
+    Sink strength plots are presented in Fig.
+\ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}.
 The effect of flipping behavior is not visible in grain boundary sink strength, ${Z^{gb}}$ plot, but in total grain boundary sink strength, ${k^2}$ plot, there is a significant change on ${k^2_i}$ after critical grain size of ${\sim}$1000 nm.

### 2020-12-30 scripts/plot_lengthscaled.py

@@ -17,7 +17,7 @@ scale = 1e-1 # scaling factor for imported DATA
 
 w = 9.036600512379032e-12 #time scale used in MOOSE
 l = 1e-10  #length scale used in MOOSE
-coordinates = "spherical"   #cartesian or spherical
+coordinates = "cartesian"   #cartesian or spherical
 
 def getHelp():
     print('\033[96m'+"\n# ------------------------------------------------------- #\n"

### 2020-12-30 scripts/plot_lengthscaled.py
article-edit

@@ -52,15 +52,15 @@ def getHelp():
 def getSinkStrength(df,l,scale,coordinates="cartesian"):
     ss_file = open('sink_strength_moose.csv', 'a')
     nrow = df.shape[0] #number of columns in dataframe
-    size = df.loc[nrow-1,'x']/scale
-    d = size
+    size = df.loc[nrow-1,'x']
+    d = size/scale
     flow_area=1 # !check this number for 2D and 3D
     if df.loc[nrow-1,'y']==0 and df.loc[nrow-1,'z']==0: # check 1D domain
-        flow_area=size*size
+        flow_area=d**2
     if coordinates == "spherical": # for spherical grains
         print('\033[91m'+"Coordinate system is \""+coordinates+"\""+'\033[0m')
-        d = size * 2 # dimater of grain
-        flow_area = 4*np.pi*size**2 # surface are of grain
+        d = d * 2 # dimater of grain
+        flow_area = np.pi*d**2 # surface are of grain 4pir^2=piD^2
         xi = df.loc[0,'xi']  # at center(r=0) for spherical coordinate system
         xv = df.loc[0,'xv']  # at center(r=0) for spherical coordinate system
     else:
@@ -73,23 +73,27 @@ def getSinkStrength(df,l,scale,coordinates="cartesian"):
     Di = df.loc[(nrow+1)/2,'Di']
     Dv = df.loc[(nrow+1)/2,'Dv']
     Zi = Fi/(xi*Di)
+    Zi_scaled = Zi*l
     Zv = Fv/(xv*Dv)
+    Zv_scaled = Zv*l
     rho = 6/(np.pi*(d**3))
     ki = rho*Zi
+    ki_scaled = ki/(l**2)
     kv = rho*Zv
+    kv_scaled = kv/(l**2)
     print('\033[94m'+'\033[4m'+'\033[1m'+"\nNondimensionalized Results for length_scale= "+str(l)+" m"+'\033[0m')
     print('\033[97m'+"Domain Size = "+str(size))
     print("xi = "+str(xi)+", jix = "+str(Ji)+", Di = "+str(Di))
     print("xv = "+str(xv)+", jvx = "+str(Jv)+", Dv = "+str(Dv))
[…]

### 2020-12-31 examples/point_defects/article/article.tex
article-edit

@@
 
+Scaling factors and non-dimensionalized variables are introduced as,
+
+\begin{equation}
+  \begin{aligned}
+    &X = \Omega C\\
+    &\tau = \frac{t}{\omega}\\
+  \end{aligned}
+  \label{equation:non-dimensionalization_variables}
+\end{equation}
+
+where ${\Omega}$ is atomic volume in ${m^3}$, ${l}$ is length scale in ${m}$ and ${\omega}$ is time scale in ${s}$, ${\omega= l^2/D_i}$\\
+
+After substituting Eq. \ref{equation:non-dimensionalization_variables} into \ref{equation:point_defect_equations} and reorganizing, the non-dimensionalized version of point defect equations are,
+
+\begin{equation}
+  \begin{aligned}
+    &\frac{dX_i}{dt} = \Omega\omega K_0 - \frac{\omega K_{iv}}{\Omega}X_iX_v - \frac{\omega K_{is}}{\Omega}X_iX_s + \omega D_i\nabla^2 X_i\\
+    &\frac{dX_v}{dt} = \Omega\omega K_0 - \frac{\omega K_{iv}}{\Omega}X_iX_v - \frac{\omega K_{vs}}{\Omega}X_vX_s + \omega D_v\nabla^2 X_v\\
+  \end{aligned}
+  \label{equation:non-dimensionalized_point_defect_equations}
+\end{equation}\\
+or
+\begin{equation}
+  \begin{aligned}
+    &\frac{dX_i}{dt} = \widetilde{K_0} - \widetilde{K_{iv}}X_iX_v - \widetilde{K_{is}}X_iX_s + \widetilde{D_i}\widetilde{\nabla}^2 X_i\\
+    &\frac{dX_v}{dt} = \widetilde{K_0} - \widetilde{K_{iv}}X_iX_v - \widetilde{K_{vs}}X_vX_s + \widetilde{D_v}\widetilde{\nabla}^2 X_v\\
+  \end{aligned}
+  \label{equation:non-dimensionalized_point_defect_equations}
+\end{equation}\\
+
 \subsection{Model Settings and Parameters} \hspace{10pt}
@@
   \end{figure}
+  \newpage
   \subsubsection{Concentrations} \hspace{10pt}

### 2020-12-31 scripts/plot_lengthscaled.py

@@ -93,7 +93,7 @@ def getSinkStrength(df,l,scale,coordinates="cartesian"):
 
 os.system("rm -rf sink_strength_moose.csv")
 ss_file = open('sink_strength_moose.csv', 'a')
-ss_file.write("x,Ci_Center,Cv_center,Fi,Fv,Di,Dv,rho,Zi,Zv,ki,kv,Zi_scaled,Zv_scaled,ki_scaled,kv_scaled\n")
+ss_file.write("size,Ci_Center,Cv_center,Fi,Fv,Di,Dv,rho,Zi,Zv,ki,kv,Zi_scaled,Zv_scaled,ki_scaled,kv_scaled\n")
 ss_file.close()
 
 if sys.argv[-1]=="-"+"h":

### 2020-12-31 examples/point_defects/article/plots/plot3D.py
article-edit

@@ -1,0 +1,47 @@
+import sys
+import csv
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib import cm
+from matplotlib.ticker import LinearLocator, FormatStrFormatter
+from mpl_toolkits.mplot3d import Axes3D
+
+#Read File
+filename = sys.argv[1]
+with open(filename, 'r') as f:
+    reader = csv.reader(f, delimiter=',')
+    headers = next(reader)
+    data = np.array(list(reader)).astype(float)
+df=pd.DataFrame(data,columns=headers)
+
+#Create meshgrid from dataframe
+x=df[sys.argv[2]].to_list()
+y=df[sys.argv[3]].to_list()
+z=df[sys.argv[4]].to_list()
+x=sorted(set(x))
+y=sorted(set(y))
+X,Y = np.meshgrid(x,y)
+Z = X*0
+for i in range(len(y)):
+    for j in range(len(x)):
+        for index, row in df.iterrows():
+            if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
+                Z[i][j]=row[sys.argv[4]]
+
+fig = plt.figure()
+ax = Axes3D(fig)
+surf = ax.plot_surface(X, Y, np.log10(Z), rstride=1, cstride=1, cmap=cm.coolwarm,linewidth=1, antialiased=False)
+ax.set_xlabel(sys.argv[2])
+ax.set_ylabel(sys.argv[3])
+ax.set_zlabel(sys.argv[4])
+
+# ax.set_xscale('log',basex=10)
+# ax.set_yscale('log',basex=10)
+# ax.set_zscale('log',basex=10)
+
+# ax.set_zlim(-1.01, 1.01)
+# ax.zaxis.set_major_locator(LinearLocator(10))
+# ax.zaxis.set_major_formatter(FormatStrFormatter('%.02f'))
+# fig.colorbar(surf, shrink=0.5, aspect=5)
+plt.show()

### 2021-01-01 examples/point_defects/article/article.tex
article-edit

@@
 
+    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
+      \centering
+      \subfloat{\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
+      \qquad
+      \subfloat{\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
+      \caption{Average Concentration profiles for low and high dose neutron irradation with 5\% Production Bias}
+      \label{figure:average_concentrations_neutron_5}
+    \end{figure}
+
     \newpage
@@
 In high dose rate plot, the critical grain size is seen clearly around at ${\sim}$250 nm.
-      % \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
-      %   \centering
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_k}}
-      %   \qquad
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_Z}}
-      %   \caption{Sink Strengths for low dose rate neutron irradiation with 0\% Production Bias}
-      %   \label{figure:sink_strengths_neutron_0_1e-6}
-      % \end{figure}
       \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
@@
         \label{figure:sink_strengths_neutron_5_1e-3}
+      \end{figure}
+      \begin{figure}[h!]  %GB Sink Strength - Neutron 1e-6 dpa/s
+        \centering
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zi_scaled}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zv_scaled}}
+        \caption{GB Sink Strengths for low dose rate neutron irradation}
+        \label{figure:sink_strengths_neutron_bias_Z}
+      \end{figure}
+      \begin{figure}[h!]  %Total GB Sink Strength - Neutron 1e-6 dpa/s
+        \centering
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_ki_scaled}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_kv_scaled}}
+        \caption{Total GB Sink Strengths for high dose rate neutron irradation}
+        \label{figure:sink_strengths_neutron_bias_k}
+      \end{figure}
+      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s
+        \centering
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Z_scaled}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_k_scaled}}
+        \caption{Sink Strengths for low dose rate neutron irradiation}
+        \label{figure:sink_strength_moose_neutron_3D}
       \end{figure}
@@
         \label{figure:concentrations_ion_5_1e-3}
+      \end{figure}
+      \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
+        \centering
+        \subfloat{\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.55]{average_concentration_low_ion_5_size}}
+        \caption{Average Concentration profiles for low and high dose ion irradation with 5\% Production Bias}
+        \label{figure:average_concentrations_neutron_5}
       \end{figure}

### 2021-01-01 examples/point_defects/article/plots/plot3.py

@@ -1,0 +1,59 @@
+import sys
+import csv
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib import cm
+from matplotlib.ticker import LinearLocator, FormatStrFormatter
+from mpl_toolkits.mplot3d import Axes3D
+
+#Read File
+filename = sys.argv[1]
+figname=filename[:-4]+".png"
+with open(filename, 'r') as f:
+    reader = csv.reader(f, delimiter=',')
+    headers = next(reader)
+    data = np.array(list(reader)).astype(float)
+df=pd.DataFrame(data,columns=headers)
+
+#Figure Settings
+fig = plt.figure()
+ax = Axes3D(fig)
+palette = plt.get_cmap('Set1')  # Color Scale, {Set1,Set2,Set3,Dark2,tab10},tab20,Pastel1}
+cmaps= ['Greys', 'Purples', 'Blues', 'Greens', 'Oranges', 'Reds',
+        'YlOrBr', 'YlOrRd', 'OrRd', 'PuRd', 'RdPu', 'BuPu',
+        'GnBu', 'PuBu', 'YlGnBu', 'PuBuGn', 'BuGn', 'YlGn']
+ax.set_xlabel(sys.argv[2])
+ax.set_ylabel(sys.argv[3])
+# ax.set_zlabel(sys.argv[4])
+ax.set_xlabel('Grain Size (nm)')
+ax.set_ylabel('Production Bias (%)')
+ax.set_zlabel('Total GB Sink Strength (m$^{-2}$)')
+# ax.set_zlabel('Total GB Sink Strength (1/m^2)')
+
+#Create meshgrid from dataframe
+x=df[sys.argv[2]].to_list()
+y=df[sys.argv[3]].to_list()
+# z=df[sys.argv[4]].to_list()
+x=sorted(set(x))
+y=sorted(set(y))
+X,Y = np.meshgrid(x,y)
+for id in range(4,len(sys.argv)):
+    Z = X*0
+    for i in range(len(y)):
+        for j in range(len(x)):
+            for index, row in df.iterrows():
+                if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
+                    Z[i][j]=row[sys.argv[id]]
[…]

### 2021-01-01 examples/point_defects/article/plots/plot3D.py

@@ -1,47 +1,0 @@
-import sys
-import csv
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-from matplotlib import cm
-from matplotlib.ticker import LinearLocator, FormatStrFormatter
-from mpl_toolkits.mplot3d import Axes3D
-
-#Read File
-filename = sys.argv[1]
-with open(filename, 'r') as f:
-    reader = csv.reader(f, delimiter=',')
-    headers = next(reader)
-    data = np.array(list(reader)).astype(float)
-df=pd.DataFrame(data,columns=headers)
-
-#Create meshgrid from dataframe
-x=df[sys.argv[2]].to_list()
-y=df[sys.argv[3]].to_list()
-z=df[sys.argv[4]].to_list()
-x=sorted(set(x))
-y=sorted(set(y))
-X,Y = np.meshgrid(x,y)
-Z = X*0
-for i in range(len(y)):
-    for j in range(len(x)):
-        for index, row in df.iterrows():
-            if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
-                Z[i][j]=row[sys.argv[4]]
-
-fig = plt.figure()
-ax = Axes3D(fig)
-surf = ax.plot_surface(X, Y, np.log10(Z), rstride=1, cstride=1, cmap=cm.coolwarm,linewidth=1, antialiased=False)
-ax.set_xlabel(sys.argv[2])
-ax.set_ylabel(sys.argv[3])
-ax.set_zlabel(sys.argv[4])
-
-# ax.set_xscale('log',basex=10)
-# ax.set_yscale('log',basex=10)
-# ax.set_zscale('log',basex=10)
-
-# ax.set_zlim(-1.01, 1.01)
-# ax.zaxis.set_major_locator(LinearLocator(10))
-# ax.zaxis.set_major_formatter(FormatStrFormatter('%.02f'))
-# fig.colorbar(surf, shrink=0.5, aspect=5)
-plt.show()

### 2021-01-01 scripts/plot3D.py

@@ -1,0 +1,56 @@
+import sys
+import csv
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib import cm
+from matplotlib.ticker import LinearLocator, FormatStrFormatter
+from mpl_toolkits.mplot3d import Axes3D
+
+#Read File
+filename = sys.argv[1]
+figname=filename[:-4]+".png"
+with open(filename, 'r') as f:
+    reader = csv.reader(f, delimiter=',')
+    headers = next(reader)
+    data = np.array(list(reader)).astype(float)
+df=pd.DataFrame(data,columns=headers)
+
+#Figure Settings
+fig = plt.figure()
+ax = Axes3D(fig)
+palette = plt.get_cmap('Set1')  # Color Scale, {Set1,Set2,Set3,Dark2,tab10},tab20,Pastel1}
+cmaps= ['Greys', 'Purples', 'Blues', 'Greens', 'Oranges', 'Reds',
+        'YlOrBr', 'YlOrRd', 'OrRd', 'PuRd', 'RdPu', 'BuPu',
+        'GnBu', 'PuBu', 'YlGnBu', 'PuBuGn', 'BuGn', 'YlGn']
+ax.set_xlabel(sys.argv[2])
+ax.set_ylabel(sys.argv[3])
+ax.set_zlabel(sys.argv[4])
+# ax.set_zlabel('Total GB Sink Strength (1/m^2)')
+
+#Create meshgrid from dataframe
+x=df[sys.argv[2]].to_list()
+y=df[sys.argv[3]].to_list()
+# z=df[sys.argv[4]].to_list()
+x=sorted(set(x))
+y=sorted(set(y))
+X,Y = np.meshgrid(x,y)
+for id in range(4,len(sys.argv)):
+    Z = X*0
+    for i in range(len(y)):
+        for j in range(len(x)):
+            for index, row in df.iterrows():
+                if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
+                    Z[i][j]=row[sys.argv[id]]
+    surf = ax.plot_wireframe(X, Y, np.log10(Z), label=sys.argv[id], cmap=cmaps[id-4], linewidth=1, color=palette(id-4), antialiased=False)
+
+# ax.set_xscale('log',basex=10)
+# ax.set_yscale('log',basex=10)
+# ax.set_zscale('log',basex=10)
[…]

### 2021-01-01 scripts/plot_lengthscaled.py

@@ -93,7 +93,7 @@ def getSinkStrength(df,l,scale,coordinates="cartesian"):
 
 os.system("rm -rf sink_strength_moose.csv")
 ss_file = open('sink_strength_moose.csv', 'a')
-ss_file.write("size,Ci_Center,Cv_center,Fi,Fv,Di,Dv,rho,Zi,Zv,ki,kv,Zi_scaled,Zv_scaled,ki_scaled,kv_scaled\n")
+ss_file.write("size,Ci_center,Cv_center,Fi,Fv,Di,Dv,rho,Zi,Zv,ki,kv,Zi_scaled,Zv_scaled,ki_scaled,kv_scaled\n")
 ss_file.close()
 
 if sys.argv[-1]=="-"+"h":

### 2021-01-01 scripts/plot_timescaled.py

@@ -1,3 +1,4 @@
+import re
 import os
 import sys
 import csv
@@ -5,10 +6,18 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 
-scale = 9.036600512379032e-12 # for time scale
-# scale = 1e-1 #for length scale
-# omega = 1.206e-29 # Atomic volume for Nickel
-cve = 3.7e-11   #vacancy equilibrium concentration for Nickel
+
+# -------------------------------------------------------------------------------------------------------------- #
+# ============================================================================================================== #
+#                           Pyhton script to plot data from MOOSE csv output files.                              #
+# ============================================================================================================== #
+# -----------------------------------------------------------------------------------------------------eigenturk #
+
+scale = 9.036600512379032e-12 # scaling factor for imported DATA
+
+w = 9.036600512379032e-12 #time scale used in MOOSE
+l = 1e-10  #length scale used in MOOSE
+coordinates = "cartesian"   #cartesian or spherical
 
 def getHelp():
     print('\033[96m'+"\n# ------------------------------------------------------- #\n"
@@ -17,121 +26,119 @@ def getHelp():
           "# ======================================================= #\n"
           "# ----------------------------------------------eigenturk #\n"+'\033[0m')
     print("This script is a tool for plotting csv files based on specified column numbers.\n\n"
-          "Usage: plot [filename] [column_number1] [column_number2] ... [-f] [-s]\n\n"
+          "Usage: plot [filename] [column_number1] [column_number2] ... [-h] [-s]\n\n"
           "Arguments:\n\n"
           "\tfilename\t\tName of the data file with extension\n"
-          "\tcolumn_number\t\tThe column number of the data in csv file\n\n"
+          "\tcolumn(number or name)\t\tThe column number(name) of the data in csv file\n\n"
           "Optional arguments:\n\n"
           "  -h, Show this help message and exit.\n"
[…]

### 2021-01-04 examples/point_defects/article/article.tex
article-edit

@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zi_scaled}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron_500-5000nm}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zv_scaled}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
         \caption{GB Sink Strengths for low dose rate neutron irradation}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_ki_scaled}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron_500-5000nm}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_kv_scaled}}
-        \caption{Total GB Sink Strengths for high dose rate neutron irradation}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
+        \caption{Total GB Sink Strengths for low dose rate neutron irradation}
         \label{figure:sink_strengths_neutron_bias_k}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Z_scaled}}
+        \subfloat{a)\includegraphics[scale=0.45]{sink_strength_moose_neutron_3D_Zi_scaled}}
+        \subfloat{b)\includegraphics[scale=0.45]{sink_strength_moose_neutron_3D_Zv_scaled}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_k_scaled}}
+        \subfloat{c)\includegraphics[scale=0.45]{sink_strength_moose_neutron_3D_ki_scaled}}
+        \subfloat{d)\includegraphics[scale=0.45]{sink_strength_moose_neutron_3D_kv_scaled}}
         \caption{Sink Strengths for low dose rate neutron irradiation}
@@
 % appear again in nano-scale domain.
+\newpage
+\section{Discussion} \hspace{10pt}
+-Comparison of Neutron and Ion irradation.
 

### 2021-01-04 examples/point_defects/article/plots/plot3.py

@@ -28,7 +28,7 @@ ax.set_ylabel(sys.argv[3])
 # ax.set_zlabel(sys.argv[4])
 ax.set_xlabel('Grain Size (nm)')
 ax.set_ylabel('Production Bias (%)')
-ax.set_zlabel('Total GB Sink Strength (m$^{-2}$)')
+ax.set_zlabel('logZ$_i$ (m)')
 # ax.set_zlabel('Total GB Sink Strength (1/m^2)')
 
 #Create meshgrid from dataframe
@@ -45,7 +45,8 @@ for id in range(4,len(sys.argv)):
             for index, row in df.iterrows():
                 if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
                     Z[i][j]=row[sys.argv[id]]
-    surf = ax.plot_wireframe(X, Y, np.log10(Z), label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cmaps[id-4], linewidth=1, color=palette(id-4), antialiased=False)
+    # surf = ax.plot_wireframe(X, Y, np.log10(Z), label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cmaps[id-4], linewidth=1, color=palette(id-4), antialiased=False)
+    surf = ax.plot_surface(X, Y, np.log10(Z), label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cm.coolwarm, linewidth=1, antialiased=True)
 
 # ax.set_xscale('log',basex=10)
 # ax.set_yscale('log',basex=10)
@@ -54,6 +55,6 @@ for id in range(4,len(sys.argv)):
 # ax.zaxis.set_major_locator(LinearLocator(10))
 # ax.zaxis.set_major_formatter(FormatStrFormatter('%.02f'))
 # fig.colorbar(surf, shrink=0.5, aspect=5)
-plt.legend(loc=0, ncol=1,fontsize='medium')
+# plt.legend(loc=0, ncol=1,fontsize='medium')
 plt.show()
 fig.savefig(figname, bbox_inches='tight',dpi=150, transparent=False)

### 2021-01-05 scripts/dataprep.py
article-edit

@@ -1,9 +1,11 @@
+import pandas as pd
 import numpy as np
-import math
 import subprocess
-import os
+import math
 import sys
 import csv
+import os
+import re
 
 # ------------------------------------------------------- #
 # ======================================================= #
@@ -11,19 +13,62 @@ import csv
 # ======================================================= #
 # ----------------------------------------------eigenturk #
 
-for i in range(1,len(sys.argv)):
-    if re.search("=",sys.argv[i]):
-        if sys.argv[i].split('=')[0]=='T':
-            T=float(sys.argv[i].split('=')[1])
-        elif sys.argv[i].split('=')[0]=='K0':
-            K0=float(sys.argv[i].split('=')[1])
-        elif sys.argv[i].split('=')[0]=='l':
-            l=float(sys.argv[i].split('=')[1])
-        elif sys.argv[i].split('=')[0]=='Cs':
-            Cs=float(sys.argv[i].split('=')[1])
 
-data_file = open('moose_data.csv', 'a')
-data_file.close()
+#Read Command Line Arguments
+n=len(sys.argv)
+
+for i in range(2,len(sys.argv)):
+    arg = sys.argv[i]
+    if re.search("=",arg):
+        arg_name = arg.split('=')[0]
+        if re.search(',',arg.split('=')[1]):
+            str_arg_value = arg.split('=')[1].split(',')
+            arg_value = [float(str_arg_value[a]) for a in range(0,len(str_arg_value))]
+        # elif re.search(":",arg.split('=')[1]):
+        #     range = arg.split('=')[1]
+        #     #Check range Argument
+        #     [l,u,ck] = range.split(':')
+        #     [lower,upper] = [float(l),float(u)]
+        #     if re.search('x',ck):
+        #         n = int(ck.split('x')[0])
+        #         arg_value = np.arange(lower, upper+1, float((upper-lower)/(n-1)))
+        #     else:
+        #         arg_value = np.arange(lower, upper+1, float(ck))
+        else:
+            arg_value=[float(arg.split('=')[1])]
+
+print(arg_name,arg_value)
+
+filename = sys.argv[1]
+file = open(filename)
+lines = file.readlines()
+fmode = False
+if re.search(".csv",lines[0]):
+    fmode = True
+    filenames = lines
+    # Read file names from file
+    csvfile=[]
+    for fid in range(0,len(filenames)):
[…]

### 2021-01-05 scripts/plot.py

@@ -58,11 +58,6 @@ if sys.argv[-2]=="-"+"f" or sys.argv[-1]=="-"+"f":   # WILL BE DEPRICATED
     fmode = True
     n=n-1
 
-gmode = False   #black and white mode
-if sys.argv[-2]=="-"+"g" or sys.argv[-1]=="-"+"g":
-    gmode = True
-    n=n-1
-
 if re.search(".csv",file.readlines()[0]):
     print('\033[92m'+"Multiple File Mode : Data from multiple files was plotted on the same figure.\n"+'\033[0m')
     fmode = True
@@ -76,6 +71,12 @@ else:
     fmode = False
     print('\033[92m'+"Single File Mode : Data from a single file was plotted.\n"+'\033[0m')
     csvfile = [filename]
+
+
+gmode = False   #black and white mode
+if sys.argv[-2]=="-"+"g" or sys.argv[-1]=="-"+"g":
+    gmode = True
+    n=n-1
 
 smode = False
 if sys.argv[-2]=="-"+"s" or sys.argv[-1]=="-"+"s":

### 2021-01-05 scripts/plot3D.py

@@ -8,6 +8,7 @@ from matplotlib.ticker import LinearLocator, FormatStrFormatter
 from mpl_toolkits.mplot3d import Axes3D
 
 #Read File
+n = len(sys.argv)
 filename = sys.argv[1]
 figname=filename[:-4]+".png"
 with open(filename, 'r') as f:
@@ -16,6 +17,11 @@ with open(filename, 'r') as f:
     data = np.array(list(reader)).astype(float)
 df=pd.DataFrame(data,columns=headers)
 
+#Read Command Line Arguments
+wf = False   # wireframe plot
+if sys.argv[-2]=="-"+"w"+"f" or sys.argv[-1]=="-"+"w"+"f":
+    wf = True
+    n=n-1
 #Figure Settings
 fig = plt.figure()
 ax = Axes3D(fig)
@@ -35,14 +41,18 @@ y=df[sys.argv[3]].to_list()
 x=sorted(set(x))
 y=sorted(set(y))
 X,Y = np.meshgrid(x,y)
-for id in range(4,len(sys.argv)):
+for id in range(4,n):
     Z = X*0
     for i in range(len(y)):
         for j in range(len(x)):
             for index, row in df.iterrows():
                 if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
                     Z[i][j]=row[sys.argv[id]]
-    surf = ax.plot_wireframe(X, Y, np.log10(Z), label=sys.argv[id], cmap=cmaps[id-4], linewidth=1, color=palette(id-4), antialiased=False)
+    if wf == True:
+        wf = ax.plot_wireframe(X, Y, np.log10(Z), label=sys.argv[id], linewidth=1, color=palette(id-4), antialiased=False)
+    else:
+        surf = ax.plot_surface(X, Y, np.log10(Z), label=sys.argv[id], cmap=cm.coolwarm, linewidth=1, antialiased=True)
+
 
 # ax.set_xscale('log',basex=10)
 # ax.set_yscale('log',basex=10)

### 2021-01-05 scripts/plot_lengthscaled.py

@@ -51,7 +51,7 @@ def getHelp():
 
 def getSinkStrength(df,l,scale,coordinates="cartesian"):
     ss_file = open('sink_strength_moose.csv', 'a')
-    nrow = df.shape[0] #number of columns in dataframe
+    nrow = df.shape[0] #number of rows in dataframe
     size = df.loc[nrow-1,'x']
     d = size/scale
     flow_area=1 # !check this number for 2D and 3D

### 2021-01-05 scripts/plot3D.py
article-edit

@@ -49,9 +49,9 @@ for id in range(4,n):
                 if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
                     Z[i][j]=row[sys.argv[id]]
     if wf == True:
-        wf = ax.plot_wireframe(X, Y, np.log10(Z), label=sys.argv[id], linewidth=1, color=palette(id-4), antialiased=False)
+        wf = ax.plot_wireframe(X, Y, Z, label=sys.argv[id], linewidth=1, color=palette(id-4), antialiased=False)
     else:
-        surf = ax.plot_surface(X, Y, np.log10(Z), label=sys.argv[id], cmap=cm.coolwarm, linewidth=1, antialiased=True)
+        surf = ax.plot_surface(X, Y, Z, label=sys.argv[id], cmap=cm.coolwarm, linewidth=1, antialiased=True)
 
 
 # ax.set_xscale('log',basex=10)

### 2021-01-06 examples/point_defects/article/Frontiers_LaTex_Templates/article_frontiers.tex
article-edit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.
%                                              %
%                                                                                                                                                         %
% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 3.4 Generated 2018/06/15 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%

\documentclass[utf8]{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
%\documentclass[utf8]{frontiersHLTH} % for Health articles
%\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and Statistics articles

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}

\linenumbers

% Leave a blank line between paragraphs instead of using \\

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{First Author\,$^{1,*}$, Co-Author\,$^{2}$ and Co-Author\,$^{1,2}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Laboratory X, Institute X, Department X, Organization X, City X , State XX (only USA, Canada and Australia), Country X \\
$^{2}$Laboratory X, Institute X, Department X, Organization X, City X , State XX (only USA, Canada and Australia), Country X  }
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Corresponding Author}

\def\corrEmail{email@uni.edu}

\begin{document}
\onecolumn
\firstpage{1}

\title[Running Title]{Article Title}

\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}

\maketitle

\begin{abstract}

%%% Leave the Abstract empty if your article does not require one, please see the Summary Table for full details.
\section{}
We present a detailed investigation of the effect of size on the segregation of point defects to interfaces and the resultant nucleation of voids. We utilize the spatially-resolved rate-theory (SRRT) modeling technique valid for modeling surfaces as discrete sinks. The effects of defect production rate, bias, and profile are thoroughly studied. The model predictions are generally different from the textbook ones obtained by the classical homogenized rate theory approach. The simulations show a strong dependence of the steady state defect profiles on the grain size, temperature, and production rate, bias, and profile. Moreover, the sink strength of each boundary is also affected by these factors. Furthermore, it is predicted that whenever there is a production bias, no neutral sinks can exist, i.e., there is always a preference for surfaces/interfaces to absorb one type of defects over another. The model predictions demonstrate the shortcomings of the classical homogenous rate-theory approach and shed light on the limitations of using ion irradiation to mimic neutron irradiation.

\tiny
 \keyFont{ \section{Keywords:} keyword, keyword, keyword, keyword, keyword, keyword, keyword, keyword} %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

\section{Introduction}

For Original Research Articles \citep{conference}, Clinical Trial Articles \citep{article}, and Technology Reports \citep{patent}, the introduction should be succinct, with no subheadings \citep{book}. For Case Reports the Introduction should include symptoms at presentation \citep{chapter}, physical exams and lab results \citep{dataset}.

\section{Article types}

For requirements for a specific article type please refer to the Article Types on any Frontiers journal page. Please also refer to  \href{http://home.frontiersin.org/about/author-guidelines#Sections}{Author Guidelines} for further information on how to organize your manuscript in the required sections or their equivalents for your field

% For Original Research articles, please note that the Material and Methods section can be placed in any of the following ways: before Results, before Discussion or after Discussion.

\section{Manuscript Formatting}

\subsection{Heading Levels}

%There are 5 heading levels

\subsection{Level 2}
\subsubsection{Level 3}
\paragraph{Level 4}
\subparagraph{Level 5}

\subsection{Equations}
Equations should be inserted in editable format from the equation editor.

\begin{equation}
\sum x+ y =Z\label{eq:01}
\end{equation}

\subsection{Figures}
Frontiers requires figures to be submitted individually, in the same order as they are referred to in the manuscript. Figures will then be automatically embedded at the bottom of the submitted manuscript. Kindly ensure that each table and figure is mentioned in the text and in numerical order. Figures must be of sufficient resolution for publication \href{http://home.frontiersin.org/about/author-guidelines#ResolutionRequirements}{see here for examples and minimum requirements}. Figures which are not according to the guidelines will cause substantial delay during the production process. Please see \href{http://home.frontiersin.org/about/author-guidelines#GeneralStyleGuidelinesforFigures}{here} for full figure guidelines. Cite figures with subfigures as figure \ref{fig:2}B.

\subsubsection{Permission to Reuse and Copyright}
Figures, tables, and images will be published under a Creative Commons CC-BY licence and permission must be obtained for use of copyrighted material from other sources (including re-published/adapted/modified/partial figures and images from the internet). It is the responsibility of the authors to acquire the licenses, to follow any citation instructions requested by third-party rights holders, and cover any supplementary charges.
%%Figures, tables, and images will be published under a Creative Commons CC-BY licence and permission must be obtained for use of copyrighted material from other sources (including re-published/adapted/modified/partial figures and images from the internet). It is the responsibility of the authors to acquire the licenses, to follow any citation instructions requested by third-party rights holders, and cover any supplementary charges.

\subsection{Tables}
Tables should be inserted at the end of the manuscript. Please build your table directly in LaTeX.Tables provided as jpeg/tiff files will not be accepted. Please note that very large tables (covering several pages) cannot be included in the final PDF for reasons of space. These tables will be published as \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} on the online article page at the time of acceptance. The author will be notified during the typesetting of the final article if this is the case.

\section{Nomenclature}

\subsection{Resource Identification Initiative}
To take part in the Resource Identification Initiative, please use the corresponding catalog number and RRID in your current manuscript. For more information about the project and for steps on how to search for an RRID, please click \href{http://www.frontiersin.org/files/pdf/letter_to_author.pdf}{here}.

\subsection{Life Science Identifiers}
Life Science Identifiers (LSIDs) for ZOOBANK registered names or nomenclatural acts should be listed in the manuscript before the keywords. For more information on LSIDs please see \href{http://www.frontiersin.org/about/AuthorGuidelines#InclusionofZoologicalNomenclature}{Inclusion of Zoological Nomenclature} section of the guidelines.

\section{Additional Requirements}

For additional requirements for specific article types and further information please refer to \href{http://www.frontiersin.org/about/AuthorGuidelines#AdditionalRequirements}{Author Guidelines}.

\section*{Conflict of Interest Statement}
%All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed. If no such relationship exists, authors will be asked to confirm the following statement:

The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

\section*{Author Contributions}

The Author Contributions section is mandatory for all articles, including articles by sole authors. If an appropriate statement is not provided on submission, a standard one will be inserted during the production process. The Author Contributions statement must describe the contributions of individual authors referred to by their initials and, in doing so, all authors agree to be accountable for the content of the work. Please see  \href{http://home.frontiersin.org/about/author-guidelines#AuthorandContributors}{here} for full authorship criteria.

\section*{Funding}
Details of all funding sources should be provided, including grant numbers if applicable. Please ensure to add all necessary funding information, as after publication this is no longer possible.

\section*{Acknowledgments}
This is a short text to acknowledge the contributions of specific colleagues, institutions, or agencies that aided the efforts of the authors.

\section*{Supplemental Data}
 \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.

\section*{Data Availability Statement}
The datasets [GENERATED/ANALYZED] for this study can be found in the [NAME OF REPOSITORY] [LINK].
% Please see the availability of data guidelines for more information, at https://www.frontiersin.org/about/author-guidelines#AvailabilityofData

\bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
\bibliography{test}

%%% Make sure to upload the bib file along with the tex file and PDF
%%% Please see the test.bib file for some examples of references

\section*{Figure captions}

%%% Please be aware that for original research articles we only permit a combined number of 15 figures and tables, one figure with multiple subfigures will count as only one figure.
%%% Use this if adding the figures directly in the mansucript, if so, please remember to also upload the files when submitting your article
%%% There is no need for adding the file termination, as long as you indicate where the file is saved. In the examples below the files (logo1.eps and logos.eps) are in the Frontiers LaTeX folder
%%% If using *.tif files convert them to .jpg or .png
%%%  NB logo1.eps is required in the path in order to correctly compile front page header %%%

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm]{logo1}% This is a *.eps file
\end{center}
\caption{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures}\label{fig:1}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=15cm]{logos}
\end{center}
\caption{This is a figure with sub figures, \textbf{(A)} is one logo, \textbf{(B)} is a different logo.}\label{fig:2}
\end{figure}

%%% If you are submitting a figure with subfigures please combine these into one image file with part labels integrated.
%%% If you don't add the figures in the LaTeX files, please upload them when submitting the article.
%%% Frontiers will add the figures at the end of the provisional pdf automatically
%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should be avoided. They should be external callouts including graphics.

\end{document}

### 2021-01-06 examples/point_defects/article/article.tex
article-edit

--- 2020-12-31 examples/point_defects/article/article.tex
@@
 The effect of irradiation dose rate, sink density, temperature, uniform defect production, non-uniform defect production and biased defect production on steady state defect concentration profile and on grain boundary sink strength are studied.
-The calculations are also repeated for different domain sizes changing from 5\emph{nm} to 5$\mu$\emph{m} to investigate the effect of grain size on defect concentration and grain boundary sink strength.
-According to results, the domain size and defect production profile/bias have a significant effect on concentration profiles.
+The calculations are also repeated for different grain sizes changing from 5\emph{nm} to 5$\mu$\emph{m} to investigate the effect of grain size on defect concentration and grain boundary sink strength.
+According to results, the grain size and defect production profile/bias have a significant effect on concentration profiles.
 They could create a flipped concentration profile through domain, which ends up with a defect segregation near grain boundary.
@@
 The results obtained from MOOSE simulations are presented in this section by plots of defect concentration, vacancy supersaturation and sink strengths.
-%The calculated sink strengths are also tabulated for different domain size and bias rates.
+%The calculated sink strengths are also tabulated for different grain size and bias rates.
 
@@
 
-  In this approach the mutual recombination term in Eq.
+  In this approach, unlike the simulations in this study, the mutual recombination term in Eq.
 \ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\
@@
   \subsubsection{Concentrations} \hspace{10pt}
-  Even though atomic collisions create vacancy-interstitial pairs, following events creates gap between the amount of point defects in favor of vacancies.
-At steady state condition, there are more vacancies than interstitials in microstructure.
-Since producing equal amount of point defects is not physically correct, production bias is used to ensure this imbalance in modeling point defects.
+  The defect concentrations can follow different patterns depending on their properties.
+Interstitials diffuse through sinks faster than vacancies, so their steady state concentrations becomes lower (see Fig.
+\ref{figure:average_concentrations_neutron_5}).
+The effect of grain size and dose rate are shown in the same figure.
+As seen, grain size could change the entire behavior of average defect concentration, while dose rate changes the gap between defect concentrations.
+
+    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
+      \centering
+      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
+      \qquad
+      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
+      \caption{Average Concentration profiles for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
+      \label{figure:average_concentrations_neutron_5}
+    \end{figure}
+
+    Atomic collisions create vacancy-interstitial pairs, but following events cause a vacancy dense defect population.
+This situation must be considered to make simulations physically more accurate.
+Production bias is used to ensure this imbalance in modeling point defects.
+The equal defect production, unbiased condition, is also studied for comparison.
+
     For unbiased case, as a result of uniform defect production and equilibrium condition at boundaries, the concentration profiles are symmetrical around domain center.
-The steady state concentration at center is not changing significantly with increasing size as shown in Fig.
+The steady state concentration at center doesn't change significantly with increasing size as shown in Fig.
 \ref{figure:concentrations_neutron_0_1e-6}.
@@
       \centering
-      \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
+      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
       \qquad
-      \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
+      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
       \caption{Concentration profiles for low dose rate neutron irradation with 0\% Production Bias}
@@
       \centering
-      \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
+      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
       \qquad
-      \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
+      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
       \caption{Concentration profiles for high dose neutron irradation with 0\% Production Bias}
@@
     \newpage
-     If production bias is applied, the steady state concentration profiles change significantly.
+     If production bias (\%5) is applied, the steady state concentration profiles change considerably.
 The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig.
-\ref{figure:concentrations_neutron_5_1e-6}).
-Moreover, the depth of profile gets larger with increasing domain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary.
-The vacancy concentration, on the other hand, increases proportional to domain size, and its profile having peak at higher concentrations as shown in Fig.
-\ref{figure:concentrations_neutron_5_1e-6}.\\
+\ref{figure:concentrations_neutron_5_1e-6}a).
+Moreover, the depth of profile gets larger with increasing grain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary.
+The vacancy concentration, on the other hand, increases proportional to grain size, and its profile starts having peak at higher concentrations as seen in Fig.
+\ref{figure:concentrations_neutron_5_1e-6}b.\\
     \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
       \centering
-      \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
+      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
       \qquad
-      \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
+      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
       \caption{Concentration profiles for low dose rate neutron irradation with 5\% Production Bias}
@@
     Similar to unbiased case, average concentration levels increases with dose rate.
-But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller domain sizes than 500 nm (see Fig.
+But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig.
 \ref{figure:concentrations_neutron_5_1e-3}).\\
@@
       \centering
-      \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}}
+      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}}
       \qquad
-      \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
+      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
       \caption{Concentration profiles for high dose neutron irradation with 5\% Production Bias}
@@
 
-    The effective vacancy supersaturation, ${S_v}$ is calculated by using following equation,\cite{was2016}\\
+    The effective vacancy supersaturation, ${S_v}$ is calculated by using following equation, \cite{was2016}\\
 
@@
 \ref{figure:vacancy_supersaturation_neutron_5}.
-Since the defect concentrations are symmetrical for neutron irradation, supersaturation curves are also symmetrical around domain center.
-The plot shows a non-linear increase in supersaturation values as domain gets larger.
+Since the defect concentrations have symmetrical profiles for neutron irradation, supersaturation curves are also symmetrical around grain center.
+The plot shows a non-linear increase in supersaturation values as grain gets larger.
       \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
         \centering
-        \subfloat{\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}}
+        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
-        \caption{Vacancy Supersaturation profiles for low and high dose neutron irradation with 5\% Production Bias}
+        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
+        \caption{Vacancy Supersaturation profiles for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
         \label{figure:vacancy_supersaturation_neutron_5}
@@
 
+    \newpage
     \subsubsection{Sink Strengths} \hspace{10pt}
@@
 \ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}.
-The effect of flipping behavior is not visible in grain boundary sink strength, ${Z^{gb}}$ plot, but in total grain boundary sink strength, ${k^2}$ plot, there is a significant change on ${k^2_i}$ after critical grain size of ${\sim}$1000 nm.
-In high dose rate plot, the critical grain size is seen clearly around at ${\sim}$250 nm.
-      % \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
-      %   \centering
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_k}}
-      %   \qquad
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_Z}}
-      %   \caption{Sink Strengths for low dose rate neutron irradiation with 0\% Production Bias}
-      %   \label{figure:sink_strengths_neutron_0_1e-6}
-      % \end{figure}
+The effect of flipping behavior is not visible in the plot of grain boundary sink strength, ${Z^{gb}}$, but there is a significant change on total grain boundary sink strength, ${k^2_i}$ after critical grain size of ${\sim}$1000 nm.
+In case of high dose rate, the critical grain size drops to ${\sim}$250 nm (Fig.
+\ref{figure:sink_strengths_neutron_5_1e-6}b).
       \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
-        \caption{Sink Strengths for low dose rate neutron irradation with 5\% Production Bias}
+        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
+        \caption{GB Sink Strength for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
         \label{figure:sink_strengths_neutron_5_1e-6}
       \end{figure}
+
       \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
-        \caption{Sink Strengths for high dose rate neutron irradation with 5\% Production Bias}
+        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
+        \caption{Total GB Sink Strengths for high dose neutron irradation with 5\% Production Bias}
         \label{figure:sink_strengths_neutron_5_1e-3}
       \end{figure}
+
+      \newpage
+      The calculated sink strengths for different production bias and for different grain sizes are presented by a 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
+      \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
+        \centering
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}}
+        \subfloat{b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}}
+        \qquad
+        \subfloat{c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}}
+        \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
+        \caption{Sink Strengths for low dose rate neutron irradiation}
+        \label{figure:sink_strength_moose_neutron_3D}
+      \end{figure}
+
+      \begin{figure}[h!]  %GB Sink Strength - Neutron 1e-6 dpa/s
+        \centering
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron}}
+        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron}}
+        \qquad
+        % \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron_500-5000nm}}
+        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
+        \caption{GB Sink Strengths for low dose rate neutron irradation}
+        \label{figure:sink_strengths_neutron_bias_Z}
+      \end{figure}
+
+      \begin{figure}[h!]  %Total GB Sink Strength - Neutron 1e-6 dpa/s
+        \centering
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron}}
+        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron}}
+        \qquad
+        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron_500-5000nm}}
+        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
+        \caption{Total GB Sink Strengths for low dose rate neutron irradation}
+        \label{figure:sink_strengths_neutron_bias_k}
+      \end{figure}
+
   \newpage
@@
 These characteristic causes a non-uniform defect production profile.
-The defect production profile used for ion irradation simulations are shown in Fig.
-\ref{figure:defect_production}.
-The dose rate, K\textsubscript{0} and domain size (1000 nm) would be scaled for different cases, but the profile is going to stay unchanged.
+Figure \ref{figure:defect_production} shows the profile used for ion irradation simulations.
+The dose rate, K\textsubscript{0} and grain size (1000 nm) would be scaled for the case of interest, but the profile doesn't change.
     \begin{figure}[h!]  %Ion irradation
@@
     \subsubsection{Concentrations} \hspace{10pt}
-    The effect of defect production distribution is the first thing that can be observed easily on concentration profiles.
-Since, all defect production profiles having peak at around half of the domain, the concentration profiles are also showing the same behavior and reaching maximum at the center of domain, then waning through boundaries.
+    Even though ion irradation has non-uniform defect production, average defect concentrations show a time-dependent trend that is identical to the one in neutron irradation case.
+The only difference is the change in concentration levels as a result of less defect production (see Fig.
+\ref{figure:average_concentrations_ion_5}).
 
-    If production bias is zero, maximum concentration that point defects can reach is equal for all different domain sizes shown in Fig.
+    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
+      \centering
+      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
+      \qquad
+      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_low_ion_5_size}}
+      \caption{Average Concentration profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
+      \label{figure:average_concentrations_ion_5}
+    \end{figure}
+
+    \newpage
+    The effect of defect production distribution can be observed obviously in concentration profiles.
+Since, defect production has peak at around half of the grain, the concentration profiles are taking shape under same behavior and reaching maximum at the center of domain, then waning through boundaries.
+
+    If production bias is zero, maximum concentration of each type of point defect becomes independent of grain sizes shown in Fig.
 \ref{figure:concentrations_ion_0_1e-6}.
-High ion dose rate is scaling up the concentration levels without making a significant change in profiles (see Fig.
+High ion dose rate only scales up the concentration levels without making any significant change in profiles (see Fig.
 \ref{figure:concentrations_ion_0_1e-3}).
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
+        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
+        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
         \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
+        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
+        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
         \caption{Concentration profiles for high dose rate ion irradiation with 0\% Production Bias}
@@
       In case of applying production bias, profiles become completely different.
-Although the flipping behavior observed in neutron irradation case is also visible in ion irradation case, the non-uniform defect production causes asymmetrical interstitial concentration profile in Fig.
-\ref{figure:concentrations_ion_5_1e-6}.
-The vacancy concentration profiles also become asymmetrical and shift up with increasing domain size.
-Increasing ion dose rate from 1e-6 dpa/s to 1e-3 dpa/s reduces the effect of defect production profile as well as critical grain size to flip (see Fig.
-\ref{figure:concentrations_ion_5_1e-3}).
+The flipping behavior observed in neutron irradation case repeats on ion irradation case.
+In addition, the non-uniform defect production causes asymmetrical interstitial concentration profile given in Fig.
+\ref{figure:concentrations_ion_5_1e-6}a.
+The vacancy concentration profiles also loose their symmetry and shift up with increasing grain size (see Fig.
+\ref{figure:concentrations_ion_5_1e-6}b).
+Increase on ion dose rate, from 1e-6 dpa/s to 1e-3 dpa/s, combines with the effect of defect production profile and reduces the critical grain size to ${\sim}$250 nm.
+The flipping start to be visible through end of the grains.
+(see Fig.
+\ref{figure:concentrations_ion_5_1e-3}a).
       \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
+        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
+        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
         \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
+        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
+        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
         \caption{Concentration profiles for high dose rate ion irradation with 5\% Production Bias}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
+        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
-        \caption{Vacancy Supersaturation profiles for low dose and ion irradation with 5\% Production Bias}
+        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
+        \caption{Vacancy Supersaturation profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
         \label{figure:vacancy_supersaturation_ion_5}
       \end{figure}
+      \newpage
     \subsubsection{Sink Strengths} \hspace{10pt}
@@
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
-        \caption{Sink Strengths for low dose rate ion irradiation with 5\% Production Bias}
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
+        \caption{GB Sink Strengths for low(a) and high(b) dose rate ion irradiation with 5\% Production Bias}
         \label{figure:sink_strengths_ion_5_1e-6}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
+        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
         \qquad
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
-        \caption{Sink Strengths for high dose rate ion irradiation with 5\% Production Bias}
+        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
+        \caption{Total GB Sink Strengths for low(a) and high(b) dose rate ion irradiation with 5\% Production Bias}
         \label{figure:sink_strengths_ion_5_1e-3}
@@
 
-% In nano-scale case, since the domain size is not big enough, the boundaries become
+% In nano-scale case, since the grain size is not big enough, the boundaries become
 % closer to each other. This causes point defects to reach sinks before they react with each other
@@
 % appear again in nano-scale domain.
+  \subsection{Discussion} \hspace{10pt}
+  -Comparison of Neutron and Ion irradation.
 
@@
 The behavior of concentration distributions are controlled by parameters given in equation, representing their reactions and diffusion in domain.
-According to the results obtained in this study, the combination of production bias, production dose rate, production profile and domain size determine whether the steady state point defect concentration profile is symmetrical, flipped or both.
+According to the results obtained in this study, the combination of production bias, production dose rate, production profile and grain size determine whether the steady state point defect concentration profile is symmetrical, flipped or both.
 There is always a critical value for parameters that could change the defect concentration profile entirely.

### 2021-01-06 examples/point_defects/article/article.tex
article-edit

@@
 \title{Numerical Solution of Point Defect Equations by MOOSE}
-\author{Abdurrahman Ozturk$^{1}$, Author2$^{1}$, Author3$^{1}$, Karim Ahmed$^{1}$  \\
+\author{Abdurrahman Ozturk$^{1}$, Author$^{1}$, Author$^{1}$, Karim Ahmed$^{1}$  \\
         \small $^{1}$Texas A\&M University \\
@@
       \centering
-      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
+      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_low_ion_5_size}}
       \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_low_ion_5_size}}
+      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
       \caption{Average Concentration profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
@@
         \centering
-        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
+        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
         \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
+        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
         \caption{Vacancy Supersaturation profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
@@
   \subsection{Discussion} \hspace{10pt}
-  -Comparison of Neutron and Ion irradation.
+  What happens when switched from neutron irradation to ion irradiation
+  \begin{enumerate}
+    \item Loosing symmetry/uniformity in concentration profiles
+    \item Reduction in average concentration
+    \item Reduction in supersaturation
+  \end{enumerate}
 

### 2021-01-08 examples/point_defects/article/article.tex
article-edit

@@
 \usepackage{verbatim}
+\usepackage[font=scriptsize]{caption}
 \pagenumbering{arabic}
@@
       \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
-      \caption{Average Concentration profiles for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
+      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a)low neutron dose rate, b) high neutron dose rate}
       \label{figure:average_concentrations_neutron_5}
@@
       \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
-      \caption{Concentration profiles for low dose rate neutron irradation with 0\% Production Bias}
+      \caption{Concentration profiles for low neutron dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
       \label{figure:concentrations_neutron_0_1e-6}
@@
       \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
-      \caption{Concentration profiles for high dose neutron irradation with 0\% Production Bias}
+      \caption{Concentration profiles for high neutron dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
       \label{figure:concentrations_neutron_0_1e-3}
@@
       \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
-      \caption{Concentration profiles for low dose rate neutron irradation with 5\% Production Bias}
+      \caption{Concentration profiles for low neutron dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
       \label{figure:concentrations_neutron_5_1e-6}
@@
       \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
-      \caption{Concentration profiles for high dose neutron irradation with 5\% Production Bias}
+      \caption{Concentration profiles for high neutron dose rate with 0\% production bias, a) interstitial concentration b) vacancy concentration}
       \label{figure:concentrations_neutron_5_1e-3}
@@
         \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
-        \caption{Vacancy Supersaturation profiles for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
+        \caption{Vacancy supersaturation profiles for 5\% production bias, a)low neutron dose rate, b) high neutron dose rate}
         \label{figure:vacancy_supersaturation_neutron_5}
@@
         \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
-        \caption{GB Sink Strength for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
+        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
         \label{figure:sink_strengths_neutron_5_1e-6}
@@
         \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
-        \caption{Total GB Sink Strengths for high dose neutron irradation with 5\% Production Bias}
+        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
         \label{figure:sink_strengths_neutron_5_1e-3}
@@
         \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
-        \caption{Sink Strengths for low dose rate neutron irradiation}
+        \caption{Change of sink strengths with grain size and production bias for low neutron dose rate in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
         \label{figure:sink_strength_moose_neutron_3D}
@@
         \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron}}
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron}}
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_Zi_scaled_nolegend}}
+        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_Zv_scaled_nolegend}}
+        \subfloat{\includegraphics[scale=0.35]{legend}}
         \qquad
@@
         % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
-        \caption{GB Sink Strengths for low dose rate neutron irradation}
+        \caption{Change of sink strengths with production bias for low neutron dose rate, a) interstitial GB sink strength, b) vacancy GB sink strength}
         \label{figure:sink_strengths_neutron_bias_Z}
@@
         \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron}}
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron}}
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_ki_scaled_nolegend}}
+        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_kv_scaled_nolegend}}                \subfloat{\includegraphics[scale=0.35]{legend}}
         \qquad
@@
         % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
-        \caption{Total GB Sink Strengths for low dose rate neutron irradation}
+        \caption{Change of sink strengths with production bias for low neutron dose rate, a) total interstitial GB sink strength, b) total vacancy GB sink strength}
         \label{figure:sink_strengths_neutron_bias_k}
@@
     \end{figure}
+    \newpage
     \subsubsection{Concentrations} \hspace{10pt}
@@
       \subfloat{b)\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
-      \caption{Average Concentration profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
+      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a) low ion dose rate, b) high ion dose rate}
       \label{figure:average_concentrations_ion_5}
@@
 
-    \newpage
     The effect of defect production distribution can be observed obviously in concentration profiles.
@@
         \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
-        \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
+        \caption{Concentration profiles for low ion dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
         \label{figure:concentrations_ion_0_1e-6}
@@
         \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
-        \caption{Concentration profiles for high dose rate ion irradiation with 0\% Production Bias}
+        \caption{Concentration profiles for high ion dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
         \label{figure:concentrations_ion_0_1e-3}
@@
         \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
-        \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
+        \caption{Concentration profiles for low ion dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
         \label{figure:concentrations_ion_5_1e-6}
@@
         \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
-        \caption{Concentration profiles for high dose rate ion irradation with 5\% Production Bias}
+        \caption{Concentration profiles for high ion dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
         \label{figure:concentrations_ion_5_1e-3}
@@
         \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
-        \caption{Vacancy Supersaturation profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
+        \caption{Vacancy supersaturation profiles for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
         \label{figure:vacancy_supersaturation_ion_5}
@@
         \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
-        \caption{GB Sink Strengths for low(a) and high(b) dose rate ion irradiation with 5\% Production Bias}
+        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
         \label{figure:sink_strengths_ion_5_1e-6}
@@
         \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
-        \caption{Total GB Sink Strengths for low(a) and high(b) dose rate ion irradiation with 5\% Production Bias}
+        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
         \label{figure:sink_strengths_ion_5_1e-3}

### 2021-01-08 examples/point_defects/article/plots/plot3.py

@@ -28,7 +28,7 @@ ax.set_ylabel(sys.argv[3])
 # ax.set_zlabel(sys.argv[4])
 ax.set_xlabel('Grain Size (nm)')
 ax.set_ylabel('Production Bias (%)')
-ax.set_zlabel('logZ$_i$ (m)')
+ax.set_zlabel('logC$_{i,center}$')
 # ax.set_zlabel('Total GB Sink Strength (1/m^2)')
 
 #Create meshgrid from dataframe

### 2021-01-08 scripts/plot3D.py

@@ -7,6 +7,8 @@ from matplotlib import cm
 from matplotlib.ticker import LinearLocator, FormatStrFormatter
 from mpl_toolkits.mplot3d import Axes3D
 
+scale = 1e-1 # scaling factor for imported DATA
+
 #Read File
 n = len(sys.argv)
 filename = sys.argv[1]
@@ -15,6 +17,9 @@ with open(filename, 'r') as f:
     reader = csv.reader(f, delimiter=',')
     headers = next(reader)
     data = np.array(list(reader)).astype(float)
+
+#scaling data
+data[:,1] *= scale
 df=pd.DataFrame(data,columns=headers)
 
 #Read Command Line Arguments

### 2021-01-11 examples/point_defects/article/article.tex
article-edit

@@
   Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable.
-Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE as bencmark problem, and its results are compared to analytical results for validation.
+Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE as benchmark problem, and its results are compared to analytical results for validation.
 
   In this approach, unlike the simulations in this study, the mutual recombination term in Eq.
-\ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\
+\ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for a spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\
 
@@
 
-  As seen in Fig. \ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.
+  This approach is tested in MOOSE by solving point defect concentrations for a spherical grain having radius of 500 nm.
+As seen in Fig.
+\ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.
   \begin{figure}[h!]
@@
     \includegraphics[scale=0.55]{concentration_profiles_MOOSE_Analytical_Neutron_0}
-    \caption{Comparison of MOOSE results with analytical solution for spherical grain.}
+    \caption{Comparison of MOOSE results with analytical solution for spherical grain (\textit{a}=500 nm).}
     \label{figure:concentrations_MOOSE_analytical}
@@
   The defect concentrations can follow different patterns depending on their properties.
-Interstitials diffuse through sinks faster than vacancies, so their steady state concentrations becomes lower (see Fig.
+Interstitials diffuse to sinks faster than vacancies, so their steady state concentrations becomes lower (see Fig.
 \ref{figure:average_concentrations_neutron_5}).
 The effect of grain size and dose rate are shown in the same figure.
-As seen, grain size could change the entire behavior of average defect concentration, while dose rate changes the gap between defect concentrations.
+The effect of grain size on the point defect kinetics resembles to some extent the effect of temperature.
+This is due to the fact that both factors affect the diffusion kinetics of defects.
+However, as will be discussed shortly, its effect on the spatial steady-state profiles is even more complex.
+The dose rate acts like an amplifier and change intensity of the defect behavior, thus the seperation between defect concentrations becomes more explicit.
 
@@
       \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
-      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a)low neutron dose rate, b) high neutron dose rate}
+      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a)low dose rate neutron, b) high dose rate neutron}
       \label{figure:average_concentrations_neutron_5}
@@
 \ref{figure:concentrations_neutron_0_1e-6}.
-In case of high neutron dose rate, concentration levels increase, profiles become more stable (see Fig.
+In case of high dose rate neutron, concentration levels increase at the center of domain with higher gradients close to the boundaries.
+(see Fig.
 \ref{figure:concentrations_neutron_0_1e-3}).\\
@@
       \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
-      \caption{Concentration profiles for low neutron dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
+      \caption{Concentration profiles for low dose rate neutron with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
       \label{figure:concentrations_neutron_0_1e-6}
@@
       \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
-      \caption{Concentration profiles for high neutron dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
+      \caption{Concentration profiles for high dose rate neutron with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
       \label{figure:concentrations_neutron_0_1e-3}
@@
       \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
-      \caption{Concentration profiles for low neutron dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
+      \caption{Concentration profiles for low dose rate neutron with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
       \label{figure:concentrations_neutron_5_1e-6}
@@
     Similar to unbiased case, average concentration levels increases with dose rate.
-But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig.
+But, the most important effect of high dose rate neutron is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig.
 \ref{figure:concentrations_neutron_5_1e-3}).\\
@@
       \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
-      \caption{Concentration profiles for high neutron dose rate with 0\% production bias, a) interstitial concentration b) vacancy concentration}
+      \caption{Concentration profiles for high dose rate neutron with 0\% production bias, a) interstitial concentration b) vacancy concentration}
       \label{figure:concentrations_neutron_5_1e-3}
@@
         \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
-        \caption{Vacancy supersaturation profiles for 5\% production bias, a)low neutron dose rate, b) high neutron dose rate}
+        \caption{Vacancy supersaturation profiles for 5\% production bias, a)low dose rate neutron, b) high dose rate neutron}
         \label{figure:vacancy_supersaturation_neutron_5}
@@
         \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
-        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
+        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low dose rate neutron, b) high dose rate neutron}
         \label{figure:sink_strengths_neutron_5_1e-6}
@@
         \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
-        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
+        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low dose rate neutron, b) high dose rate neutron}
         \label{figure:sink_strengths_neutron_5_1e-3}
@@
         \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
-        \caption{Change of sink strengths with grain size and production bias for low neutron dose rate in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
+        \caption{Change of sink strengths with grain size and production bias for low dose rate neutron in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
         \label{figure:sink_strength_moose_neutron_3D}
@@
         % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
-        \caption{Change of sink strengths with production bias for low neutron dose rate, a) interstitial GB sink strength, b) vacancy GB sink strength}
+        \caption{Change of sink strengths with production bias for low dose rate neutron, a) interstitial GB sink strength, b) vacancy GB sink strength}
         \label{figure:sink_strengths_neutron_bias_Z}
@@
         % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
-        \caption{Change of sink strengths with production bias for low neutron dose rate, a) total interstitial GB sink strength, b) total vacancy GB sink strength}
+        \caption{Change of sink strengths with production bias for low dose rate neutron, a) total interstitial GB sink strength, b) total vacancy GB sink strength}
         \label{figure:sink_strengths_neutron_bias_k}
@@
         \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
-        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
+        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low dose rate neutron, b) high dose rate neutron}
         \label{figure:sink_strengths_ion_5_1e-3}

### 2021-01-11 examples/point_defects/article/plots/plot3.py

@@ -7,6 +7,8 @@ from matplotlib import cm
 from matplotlib.ticker import LinearLocator, FormatStrFormatter
 from mpl_toolkits.mplot3d import Axes3D
 
+scale=0.1
+
 #Read File
 filename = sys.argv[1]
 figname=filename[:-4]+".png"
@@ -25,10 +27,14 @@ cmaps= ['Greys', 'Purples', 'Blues', 'Greens', 'Oranges', 'Reds',
         'GnBu', 'PuBu', 'YlGnBu', 'PuBuGn', 'BuGn', 'YlGn']
 ax.set_xlabel(sys.argv[2])
 ax.set_ylabel(sys.argv[3])
-# ax.set_zlabel(sys.argv[4])
-ax.set_xlabel('Grain Size (nm)')
+ax.set_zlabel(sys.argv[4])
+
+#Custom Labels
+ax.set_xlabel('x (nm)')
+# ax.set_xlabel('Grain Size (nm)')
 ax.set_ylabel('Production Bias (%)')
-ax.set_zlabel('logC$_{i,center}$')
+ax.set_zlabel('Interstitial Concentration')
+# ax.set_zlabel('logC$_{i,center}$')
 # ax.set_zlabel('Total GB Sink Strength (1/m^2)')
 
 #Create meshgrid from dataframe
@@ -44,9 +50,9 @@ for id in range(4,len(sys.argv)):
         for j in range(len(x)):
             for index, row in df.iterrows():
                 if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
-                    Z[i][j]=row[sys.argv[id]]
+                    Z[i][j]=row[sys.argv[id]]+1e-15
     # surf = ax.plot_wireframe(X, Y, np.log10(Z), label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cmaps[id-4], linewidth=1, color=palette(id-4), antialiased=False)
-    surf = ax.plot_surface(X, Y, np.log10(Z), label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cm.coolwarm, linewidth=1, antialiased=True)
+    surf = ax.plot_surface(X*scale, Y, Z, label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cm.coolwarm, linewidth=1, antialiased=True)
 
[…]

### 2021-01-14 examples/point_defects/article/plots/plot3.py
article-edit

@@ -30,11 +30,11 @@ ax.set_ylabel(sys.argv[3])
 ax.set_zlabel(sys.argv[4])
 
 #Custom Labels
-ax.set_xlabel('x (nm)')
-# ax.set_xlabel('Grain Size (nm)')
+# ax.set_xlabel('x (nm)')
+ax.set_xlabel('Grain Size (nm)')
 ax.set_ylabel('Production Bias (%)')
-ax.set_zlabel('Interstitial Concentration')
-# ax.set_zlabel('logC$_{i,center}$')
+# ax.set_zlabel('Interstitial Concentration')
+ax.set_zlabel('C$_{i,center}$')
 # ax.set_zlabel('Total GB Sink Strength (1/m^2)')
 
 #Create meshgrid from dataframe
@@ -63,5 +63,5 @@ for id in range(4,len(sys.argv)):
 # fig.colorbar(surf, shrink=0.5, aspect=5)
 # plt.legend(loc=0, ncol=1,fontsize='medium')
 ax.view_init(elev=20., azim=-122)
-# plt.show()
+plt.show()
 fig.savefig(figname, bbox_inches='tight',dpi=150, transparent=False)

### 2021-01-14 scripts/plot_lengthscaled.py

@@ -81,19 +81,20 @@ def getSinkStrength(df,l,scale,coordinates="cartesian"):
     ki_scaled = ki/(l**2)
     kv = rho*Zv
     kv_scaled = kv/(l**2)
+    super_saturation = df.loc[(nrow+1)/2,'super_saturation']
     print('\033[94m'+'\033[4m'+'\033[1m'+"\nNondimensionalized Results for length_scale= "+str(l)+" m"+'\033[0m')
     print('\033[97m'+"Domain Size = "+str(size))
     print("xi = "+str(xi)+", jix = "+str(Ji)+", Di = "+str(Di))
     print("xv = "+str(xv)+", jvx = "+str(Jv)+", Dv = "+str(Dv))
     print('\033[93m'+"Zi: "+str(Zi)+" \nZv: "+str(Zv))
     print('\033[97m'+"ki^2: "+str(ki)+" \nkv^2: "+str(kv)+" "+'\033[0m')
-    ss_file.write(str(size)+","+str(xi)+","+str(xv)+","+str(Fi)+","+str(Fv)+","+str(Di)+","+str(Dv)+","+str(rho)+","+str(Zi)+","+str(Zv)+","+str(ki)+","+str(kv)+","+str(Zi_scaled)+","+str(Zv_scaled)+","+str(ki_scaled)+","+str(kv_scaled)+"\n")
+    ss_file.write(str(size)+","+str(xi)+","+str(xv)+","+str(Fi)+","+str(Fv)+","+str(Di)+","+str(Dv)+","+str(rho)+","+str(Zi)+","+str(Zv)+","+str(ki)+","+str(kv)+","+str(Zi_scaled)+","+str(Zv_scaled)+","+str(ki_scaled)+","+str(kv_scaled)+","+str(super_saturation)+"\n")
     ss_file.close()
     return 0
 
 os.system("rm -rf sink_strength_moose.csv")
 ss_file = open('sink_strength_moose.csv', 'a')
-ss_file.write("size,Ci_center,Cv_center,Fi,Fv,Di,Dv,rho,Zi,Zv,ki,kv,Zi_scaled,Zv_scaled,ki_scaled,kv_scaled\n")
+ss_file.write("size,Ci_center,Cv_center,Fi,Fv,Di,Dv,rho,Zi,Zv,ki,kv,Zi_scaled,Zv_scaled,ki_scaled,kv_scaled,super_saturation\n")
 ss_file.close()
 
 if sys.argv[-1]=="-"+"h":

### 2021-01-16 examples/point_defects/article/plots/plot3.py
article-edit

@@ -30,11 +30,11 @@ ax.set_ylabel(sys.argv[3])
 ax.set_zlabel(sys.argv[4])
 
 #Custom Labels
-# ax.set_xlabel('x (nm)')
-ax.set_xlabel('Grain Size (nm)')
+ax.set_xlabel('x (nm)')
+# ax.set_xlabel('Grain Size (nm)')
 ax.set_ylabel('Production Bias (%)')
-# ax.set_zlabel('Interstitial Concentration')
-ax.set_zlabel('C$_{i,center}$')
+ax.set_zlabel('Interstitial Concentration')
+# ax.set_zlabel('C$_{i,center}$')
 # ax.set_zlabel('Total GB Sink Strength (1/m^2)')
 
 #Create meshgrid from dataframe
@@ -51,7 +51,7 @@ for id in range(4,len(sys.argv)):
             for index, row in df.iterrows():
                 if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
                     Z[i][j]=row[sys.argv[id]]+1e-15
-    # surf = ax.plot_wireframe(X, Y, np.log10(Z), label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cmaps[id-4], linewidth=1, color=palette(id-4), antialiased=False)
+    # surf = ax.plot_wireframe(X*scale, Y, Z, label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cmaps[id-4], linewidth=1, color=palette(id-4), antialiased=False)
     surf = ax.plot_surface(X*scale, Y, Z, label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cm.coolwarm, linewidth=1, antialiased=True)
 
 # ax.set_xscale('log',basex=10)

### 2021-01-16 examples/point_defects/article/plots/plot3.py
article-edit

@@ -33,7 +33,8 @@ ax.set_zlabel(sys.argv[4])
 ax.set_xlabel('x (nm)')
 # ax.set_xlabel('Grain Size (nm)')
 ax.set_ylabel('Production Bias (%)')
-ax.set_zlabel('Interstitial Concentration')
+ax.set_zlabel('S$_v$')
+# ax.set_zlabel('Interstitial Concentration')
 # ax.set_zlabel('C$_{i,center}$')
 # ax.set_zlabel('Total GB Sink Strength (1/m^2)')
 

### 2021-01-17 scripts/dataprep.py
article-edit

@@ -17,27 +17,30 @@ import re
 #Read Command Line Arguments
 n=len(sys.argv)
 
-for i in range(2,len(sys.argv)):
-    arg = sys.argv[i]
-    if re.search("=",arg):
-        arg_name = arg.split('=')[0]
-        if re.search(',',arg.split('=')[1]):
-            str_arg_value = arg.split('=')[1].split(',')
-            arg_value = [float(str_arg_value[a]) for a in range(0,len(str_arg_value))]
-        # elif re.search(":",arg.split('=')[1]):
-        #     range = arg.split('=')[1]
-        #     #Check range Argument
-        #     [l,u,ck] = range.split(':')
-        #     [lower,upper] = [float(l),float(u)]
-        #     if re.search('x',ck):
-        #         n = int(ck.split('x')[0])
-        #         arg_value = np.arange(lower, upper+1, float((upper-lower)/(n-1)))
-        #     else:
-        #         arg_value = np.arange(lower, upper+1, float(ck))
-        else:
-            arg_value=[float(arg.split('=')[1])]
+argmode = False
+if len(sys.argv)>2:
+    argmode = True
+    for i in range(2,len(sys.argv)):
+        arg = sys.argv[i]
+        if re.search("=",arg):
+            arg_name = arg.split('=')[0]
+            if re.search(',',arg.split('=')[1]):
+                str_arg_value = arg.split('=')[1].split(',')
+                arg_value = [float(str_arg_value[a]) for a in range(0,len(str_arg_value))]
+            # elif re.search(":",arg.split('=')[1]):
+            #     range = arg.split('=')[1]
+            #     #Check range Argument
+            #     [l,u,ck] = range.split(':')
+            #     [lower,upper] = [float(l),float(u)]
+            #     if re.search('x',ck):
+            #         n = int(ck.split('x')[0])
+            #         arg_value = np.arange(lower, upper+1, float((upper-lower)/(n-1)))
+            #     else:
+            #         arg_value = np.arange(lower, upper+1, float(ck))
+            else:
+                arg_value=[float(arg.split('=')[1])]
 
-print(arg_name,arg_value)
+    print(arg_name,arg_value)
 
 filename = sys.argv[1]
 file = open(filename)
@@ -52,6 +55,7 @@ if re.search(".csv",lines[0]):
         csvfile.append(filenames[fid][:-1])
 else:
     csvfile = [filename]
[…]

### 2021-01-17 scripts/plot_lengthscaled.py

@@ -50,7 +50,7 @@ def getHelp():
     sys.exit()
 
 def getSinkStrength(df,l,scale,coordinates="cartesian"):
-    ss_file = open('sink_strength_moose.csv', 'a')
+    ss_file = open(ss_filename, 'a')
     nrow = df.shape[0] #number of rows in dataframe
     size = df.loc[nrow-1,'x']
     d = size/scale
@@ -81,21 +81,17 @@ def getSinkStrength(df,l,scale,coordinates="cartesian"):
     ki_scaled = ki/(l**2)
     kv = rho*Zv
     kv_scaled = kv/(l**2)
-    super_saturation = df.loc[(nrow+1)/2,'super_saturation']
+    super_saturation_center = df.loc[(nrow+1)/2,'super_saturation']
     print('\033[94m'+'\033[4m'+'\033[1m'+"\nNondimensionalized Results for length_scale= "+str(l)+" m"+'\033[0m')
     print('\033[97m'+"Domain Size = "+str(size))
     print("xi = "+str(xi)+", jix = "+str(Ji)+", Di = "+str(Di))
     print("xv = "+str(xv)+", jvx = "+str(Jv)+", Dv = "+str(Dv))
     print('\033[93m'+"Zi: "+str(Zi)+" \nZv: "+str(Zv))
     print('\033[97m'+"ki^2: "+str(ki)+" \nkv^2: "+str(kv)+" "+'\033[0m')
-    ss_file.write(str(size)+","+str(xi)+","+str(xv)+","+str(Fi)+","+str(Fv)+","+str(Di)+","+str(Dv)+","+str(rho)+","+str(Zi)+","+str(Zv)+","+str(ki)+","+str(kv)+","+str(Zi_scaled)+","+str(Zv_scaled)+","+str(ki_scaled)+","+str(kv_scaled)+","+str(super_saturation)+"\n")
+    ss_file.write(str(size)+","+str(xi)+","+str(xv)+","+str(Fi)+","+str(Fv)+","+str(Di)+","+str(Dv)+","+str(rho)+","+str(Zi)+","+str(Zv)+","+str(ki)+","+str(kv)+","+str(Zi_scaled)+","+str(Zv_scaled)+","+str(ki_scaled)+","+str(kv_scaled)+","+str(super_saturation_center)+"\n")
     ss_file.close()
     return 0
 
[…]

### 2021-01-19 examples/point_defects/article/abstract.tex
article-edit

--- 2021-01-06 examples/point_defects/article/article.tex
@@
 \usepackage{verbatim}
+\usepackage{xcolor}
+\usepackage[font=scriptsize]{caption}
 \pagenumbering{arabic}
@@
 \title{Numerical Solution of Point Defect Equations by MOOSE}
-\author{Abdurrahman Ozturk$^{1}$, Author$^{1}$, Author$^{1}$, Karim Ahmed$^{1}$  \\
+\author{Abdurrahman Ozturk$^{1}$, Karim Ahmed$^{1}$  \\
         \small $^{1}$Texas A\&M University \\
@@
 
-\section{Introduction} \hspace{10pt}
-\newpage
-\section{Methodology} \hspace{10pt}
-
-\subsection{Point Defect Equations} \hspace{10pt}
-The irradiation of a material causes the creation of vacancies and interstitial because of
-atomic collisions. The point defects can diffuse through material, recombine with each other,
-and react with sinks which are present in microstructure. The concentration of point defects is
-described mathematically by the chemical rate balance equations given in following sets of equations.\\
-
-\begin{equation}
-  \begin{aligned}
-    &\frac{dC_i}{dt} = K_0 - K_{iv}C_iC_v - K_{is}C_iC_s + \nabla\cdot D_i\nabla C_i\\
-    &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - K_{vs}C_vC_s + \nabla\cdot D_v\nabla C_v\\
-  \end{aligned}
-  \label{equation:point_defect_equations}
-\end{equation}\\
-
-There are different terms with different rate coefficients as seen in Eq.
-\ref{equation:point_defect_equations}.
-The first term on the RHS is a source term, representing defect generation with rate of \textit{K\textsubscript{0}}.
-In vacancy equation, \textit{b} is used as percent production bias to create a difference between interstitial and vacancy generation in domain.
-The second term is a reaction term, referring the recombination process if the defect \textit{x} reacts with defect \textit{y} with a rate of \textit{K\textsubscript{xy}}.
-The third term is also a reaction term, representing the reaction between the defect \textit{x} and the sink \text{s} with a rate of \textit{K\textsubscript{xs}}.
-In this study, the sink concentration is assumed constant and uniformly distributed over domain.
-The last term is diffusion term which is resolving the spatial behavior of defects.\\
-
-Another form of point defect equations can be written by using sink strength, \textit{k} definition for sink reaction term.\\
-
-\begin{equation}
-  \begin{aligned}
-    &k_i^2D_iC_i = K_{is}C_iC_s \\
-    &k_v^2D_vC_v = K_{vs}C_vC_s \\
-  \end{aligned}
-  \label{equation:sink_reaction_term}
-\end{equation}\\
-\begin{equation}
-  \begin{aligned}
-    &\frac{dC_i}{dt} = K_0 - K_{iv}C_iC_v - k_i^2D_iC_i + \nabla\cdot D_i\nabla C_i\\
-    &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - k_v^2D_vC_v + \nabla\cdot D_v\nabla C_v\\
-  \end{aligned}
-  \label{equation:point_defect_equations_sink_strength}
-\end{equation}\\
-
-\subsection{Non-dimensionalization of Point Defect Equations} \hspace{10pt}
-The time space of defect interactions is enormously large, which could differ from nanoseconds to hours.
-In addition, rate coefficients also have different orders.
-To make it easier to solve point defect equations numerically, their non-dimensionalized forms are implemented in MOOSE.
-The non-dimensionalization scheme and final form of equations are given in this section.
-
-Scaling factors and non-dimensionalized variables are introduced as,
-
-\begin{equation}
-  \begin{aligned}
-    &X = \Omega C\\
-    &\tau = \frac{t}{\omega}\\
-  \end{aligned}
-  \label{equation:non-dimensionalization_variables}
-\end{equation}
-
-where ${\Omega}$ is atomic volume in ${m^3}$, ${l}$ is length scale in ${m}$ and ${\omega}$ is time scale in ${s}$, ${\omega= l^2/D_i}$\\
-
-After substituting Eq. \ref{equation:non-dimensionalization_variables} into \ref{equation:point_defect_equations} and reorganizing, the non-dimensionalized version of point defect equations are,
-
-\begin{equation}
-  \begin{aligned}
-    &\frac{dX_i}{dt} = \Omega\omega K_0 - \frac{\omega K_{iv}}{\Omega}X_iX_v - \frac{\omega K_{is}}{\Omega}X_iX_s + \omega D_i\nabla^2 X_i\\
-    &\frac{dX_v}{dt} = \Omega\omega K_0 - \frac{\omega K_{iv}}{\Omega}X_iX_v - \frac{\omega K_{vs}}{\Omega}X_vX_s + \omega D_v\nabla^2 X_v\\
-  \end{aligned}
-  \label{equation:non-dimensionalized_point_defect_equations}
-\end{equation}\\
-or
-\begin{equation}
-  \begin{aligned}
-    &\frac{dX_i}{dt} = \widetilde{K_0} - \widetilde{K_{iv}}X_iX_v - \widetilde{K_{is}}X_iX_s + \widetilde{D_i}\widetilde{\nabla}^2 X_i\\
-    &\frac{dX_v}{dt} = \widetilde{K_0} - \widetilde{K_{iv}}X_iX_v - \widetilde{K_{vs}}X_vX_s + \widetilde{D_v}\widetilde{\nabla}^2 X_v\\
-  \end{aligned}
-  \label{equation:non-dimensionalized_point_defect_equations}
-\end{equation}\\
-
-\subsection{Model Settings and Parameters} \hspace{10pt}
-Nickel is selected as a base material, and its properties are used in calculations.
-
-\begin{table}[h!]
-  \centering
-  \caption{Material Properties for Nickel\cite{walgraef1996}}
-  \label{table:Ni_material_properties}
-  \begin{tabular}{ ||p{2cm}|p{2cm}||  }
-     % \hline
-     % \multicolumn{5}{|c|}{Material Properties} \\
-     \hline
-     Property & Value\\
-     \hline\hline
-     a  & 0.352 nm\\
-     V  & 0.01206 nm^3\\
-     E_{m,i}  & 0.30 eV\\
-     E_{m,v}  & 1.30 eV\\
-     E_{f,i}  & 4.27 eV\\
-     E_{f,v}  & 1.60 eV\\
-     D_{0,i}  & 1e-7 m^2/s\\
-     D_{0,v}  & 6e-5 m^2/s\\
-
-     \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[h!]
-  \centering
-  \caption{Simulation Parameters}
-  \label{table:simulation_parameters}
-  \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}||  }
-     % \multicolumn{5}{|c|}{Simulation Parameters} \\
-     \hline
-     Type & Dose Rate (dpa/s) & Defect Production & Temperature (K) & Sink Density (m^{-3})\\
-     \hline
-     \hline
-     Neutron  & 1e-3  & Uniform     & 773 & 1e18\\
-              & 1e-6  & Uniform     & 773 & 1e18\\
-     \hline
-     Ion      & 1e-3  & Distributed & 773 & 1e18\\
-              & 1e-6  & Distributed & 773 & 1e18\\
-     \hline
-  \end{tabular}
-\end{table}
-
-\newpage
-\section{Results} \hspace{10pt}
-
-In reactor environment, materials are exposed to different types of particle radiation such as electron, proton, neutron and ion.
-This study covers two most significant irradation types, neutrons and ions.
-The results obtained from MOOSE simulations are presented in this section by plots of defect concentration, vacancy supersaturation and sink strengths.
-%The calculated sink strengths are also tabulated for different grain size and bias rates.
-
-  \subsection{Neutron Irradiation} \hspace{10pt}
-  Neutrons have an energy spectrum that varies a couple of orders of magnitude.
-This makes defect generation possible at different energies.
-Also, the high penetration depth of neutrons allow them to travel through material corresponding to their energies.
-Thus, they cause a uniform or flat-like defect production profile in material.\cite{was2016}
-
-  Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable.
-Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE as bencmark problem, and its results are compared to analytical results for validation.
-
-  In this approach, unlike the simulations in this study, the mutual recombination term in Eq.
-\ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\
-
-  \begin{equation}
-    \begin{aligned}
-      &0 = \frac{K_0}{D_i} - k_i^2C_i + \frac{d^2C_i}{dr^2}+\frac{2}{r}\frac{dC_i}{dr}\\
-      &0 = \frac{K_0}{D_v} - k_v^2C_v + \frac{d^2C_v}{dr^2}+\frac{2}{r}\frac{dC_v}{dr}\\
-    \end{aligned}
-    \label{equation:spherical_norecomb_point_defect_equations}
-  \end{equation}\\
-  \begin{equation}
-    \begin{aligned}
-      &C_i(r)=\frac{K_0}{D_ik_i^2}\bigg(1-\frac{a\sinh{k_ir}}{r\sinh{k_ia}}\bigg)\\
-      &C_v(r)=\frac{K_0}{D_vk_v^2}\bigg(1-\frac{a\sinh{k_vr}}{r\sinh{k_va}}\bigg)\\
-    \end{aligned}
-    \label{equation:spherical_grain_analytical_solution}
-  \end{equation}\\
-
-  As seen in Fig. \ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[scale=0.55]{concentration_profiles_MOOSE_Analytical_Neutron_0}
-    \caption{Comparison of MOOSE results with analytical solution for spherical grain.}
-    \label{figure:concentrations_MOOSE_analytical}
-  \end{figure}
-  \newpage
-  \subsubsection{Concentrations} \hspace{10pt}
-  The defect concentrations can follow different patterns depending on their properties.
-Interstitials diffuse through sinks faster than vacancies, so their steady state concentrations becomes lower (see Fig.
-\ref{figure:average_concentrations_neutron_5}).
-The effect of grain size and dose rate are shown in the same figure.
-As seen, grain size could change the entire behavior of average defect concentration, while dose rate changes the gap between defect concentrations.
-
-    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
-      \caption{Average Concentration profiles for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
-      \label{figure:average_concentrations_neutron_5}
-    \end{figure}
-
-    Atomic collisions create vacancy-interstitial pairs, but following events cause a vacancy dense defect population.
-This situation must be considered to make simulations physically more accurate.
-Production bias is used to ensure this imbalance in modeling point defects.
-The equal defect production, unbiased condition, is also studied for comparison.
-
-    For unbiased case, as a result of uniform defect production and equilibrium condition at boundaries, the concentration profiles are symmetrical around domain center.
-The steady state concentration at center doesn't change significantly with increasing size as shown in Fig.
-\ref{figure:concentrations_neutron_0_1e-6}.
-In case of high neutron dose rate, concentration levels increase, profiles become more stable (see Fig.
-\ref{figure:concentrations_neutron_0_1e-3}).\\
-
-    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
-      \caption{Concentration profiles for low dose rate neutron irradation with 0\% Production Bias}
-      \label{figure:concentrations_neutron_0_1e-6}
-    \end{figure}
-    \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
-      \caption{Concentration profiles for high dose neutron irradation with 0\% Production Bias}
-      \label{figure:concentrations_neutron_0_1e-3}
-    \end{figure}
-    \newpage
-     If production bias (\%5) is applied, the steady state concentration profiles change considerably.
-The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig.
-\ref{figure:concentrations_neutron_5_1e-6}a).
-Moreover, the depth of profile gets larger with increasing grain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary.
-The vacancy concentration, on the other hand, increases proportional to grain size, and its profile starts having peak at higher concentrations as seen in Fig.
-\ref{figure:concentrations_neutron_5_1e-6}b.\\
-    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
-      \caption{Concentration profiles for low dose rate neutron irradation with 5\% Production Bias}
-      \label{figure:concentrations_neutron_5_1e-6}
-    \end{figure}\\
-
-    Similar to unbiased case, average concentration levels increases with dose rate.
-But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig.
-\ref{figure:concentrations_neutron_5_1e-3}).\\
-    \begin{figure}[htb!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
-      \caption{Concentration profiles for high dose neutron irradation with 5\% Production Bias}
-      \label{figure:concentrations_neutron_5_1e-3}
-    \end{figure}
-
-    \newpage
-    \subsubsection{Supersaturation} \hspace{10pt}
-    Supersaturation is a condition that the actual concentration of point defect is larger than its equilibrium concentration.
-The opposite condition is called undersaturation which is being smaller than equilibrium concentration.
-In both cases, the system is not at the minimum free energy.
-Both vacancies and interstitials could be supersaturated, then aggiomerate into voids or discs of interstitial atoms.
-These can produce stacking faults in crystal microstructure.
-
-    The effective vacancy supersaturation, ${S_v}$ is calculated by using following equation, \cite{was2016}\\
-
-    \begin{equation}
-      \begin{aligned}
-        &S_v=\frac{D_vC_v-D_iC_i}{D_vC_v^e}\\
-      \end{aligned}
-    \end{equation}\\
-
-    The vacancy supersaturation curves for biased neutron irradation is given in Fig.
-\ref{figure:vacancy_supersaturation_neutron_5}.
-Since the defect concentrations have symmetrical profiles for neutron irradation, supersaturation curves are also symmetrical around grain center.
-The plot shows a non-linear increase in supersaturation values as grain gets larger.
-      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
-        \caption{Vacancy Supersaturation profiles for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
-        \label{figure:vacancy_supersaturation_neutron_5}
-      \end{figure}
-
-    \newpage
-    \subsubsection{Sink Strengths} \hspace{10pt}
-    The sink reaction term in Eq.
-\ref{equation:point_defect_equations_sink_strength} represents the total loss of point defects to sinks that are voids and dislocations within the domain.
-It can be written in expanded form as below,
-
-    \begin{equation}
-      \begin{aligned}
-        &k^2DC=(Z\rho_d+4\pi r_h\rho_h)DC\\
-      \end{aligned}
-    \end{equation}\\
-    Similarly, grain boundary sink strength can be calculated by considering total flow of point defect to grain boundary.
-
-    \begin{equation}
-      \begin{aligned}
-        &F=Z_{gb}DC_0\\
-        &Z_{gb}=\frac{F}{DC_0}\\
-      \end{aligned}
-      \end{equation}\\
-
-    where ${F}$ is total flow at grain boundary, ${Z_{gb}}$ is grain boundary sink strength, ${D}$ is diffusion coefficient and ${C_0}$ is defect concentration at the domain center.\\\\
-    The total flow at boundary is equal to multiplication of surface area and current as below,\\
-
-    \begin{equation}
-      \begin{aligned}
-        &F=-\bigg(4\pi r^2D\frac{\partial C(r)}{\partial r}\bigg)_{r=a}\\
-      \end{aligned}
-    \end{equation}\\
-    The total grain boundary sink strength, ${k^2_{gb}}$ is calculated by multiplying ${Z_{gb}}$ by the grain density, ${\rho_{gb}}$.\cite{heald1977}
-    \begin{equation}
-      \begin{aligned}
-        &\rho_{gb}=\frac{6}{\pi d^3}\\
-        &k^2_{gb}=\rho_{gb}Z_{gb}\\
-      \end{aligned}
-    \end{equation}
-
-    where ${d}$ is diameter of the grain, ${d=2a}$\\\\
-    Grain boundary sink strengths, ${Z_{gb}}$ and ${k_{gb}}$, is calculated analytically by substituting Eq.
-\ref{equation:spherical_grain_analytical_solution} into expressions above.
-Thus, grain boundary sink strengths are associated with the domain sink strength, ${k^2}$.\cite{heald1977}
-
-    \begin{equation}
-      \begin{aligned}
-        &C_0=C(r=0)=\frac{K_0}{Dk^2}\bigg(1-\frac{ka}{\sinh{ka}}\bigg)\\\\
-        &F=-\bigg(4\pi r^2D\frac{\partial C(r)}{\partial r}\bigg)_{r=a}=\frac{4\pi aK_0}{k^2}\bigg(ka\coth{ka}-1\bigg)\\
-      \end{aligned}
-    \end{equation}\\
-    So that, grain boundary sink strengths are
-    \begin{equation}
-      \begin{aligned}
-        &Z_{gb}=4\pi a\bigg(\frac{ka\cosh ka-\sinh ka}{\sinh ka-ka}\bigg)\\
-        &k^2_{gb}=\frac{12}{d^2}\bigg(\frac{ka\cosh ka-\sinh ka}{\sinh ka-ka}\bigg)\\
-      \end{aligned}
-    \end{equation}\\
-
-    Using appropriate diffusion coefficient (${D}$), domain sink strength (${k^2}$) and concentration (${C_0}$) will give  relevant sink strengths.
-The analytical expressions for each defect type given by following equations
-
-    \begin{equation}
-      \begin{aligned}
-        &Z_{gb,i}=4\pi a\bigg(\frac{k_ia\cosh k_ia-\sinh k_ia}{\sinh k_ia-k_ia}\bigg)\\
-        &k^2_{gb,i}=\frac{12}{d^2}\bigg(\frac{k_ia\cosh k_ia-\sinh k_ia}{\sinh k_ia-k_ia}\bigg)\\\\
-        &Z_{gb,v}=4\pi a\bigg(\frac{k_va\cosh k_va-\sinh k_va}{\sinh k_va-k_va}\bigg)\\
-        &k^2_{gb,v}=\frac{12}{d^2}\bigg(\frac{k_va\cosh k_va-\sinh k_va}{\sinh k_va-k_va}\bigg)\\
-      \end{aligned}
-    \end{equation}\\
-
-  The results of bencmark problem, previously discussed in Fig.
-\ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations.
-Table \ref{table:sink_strengths_calculations} show the comparison of calculations.
-    \begin{table}[h!]
-      \centering
-      \caption{Comparison of sink strength calculations}
-      \label{table:sink_strengths_calculations}
-      \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}||  }
-         \hline
-          & MOOSE & Analytical\\
-         \hline\hline\hline
-         ${Z_{gb,i}}$  & 1.257206e-05 m & 1.257332e-05 m\\
-         ${Z_{gb,v}}$  & 1.256941e-05 m & 1.257332e-05 m\\
-         ${k_{gb,i}}$  & 2.401086e+13 m^{-2} & 2.401327e+13 m^{-2}\\
-         ${k_{gb,v}}$  & 2.400580e+13 m^{-2} & 2.401327e+13 m^{-2}\\
-         \hline
-      \end{tabular}
-    \end{table}
-    \newpage
-    Sink strength plots are presented in Fig.
-\ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}.
-The effect of flipping behavior is not visible in the plot of grain boundary sink strength, ${Z^{gb}}$, but there is a significant change on total grain boundary sink strength, ${k^2_i}$ after critical grain size of ${\sim}$1000 nm.
-In case of high dose rate, the critical grain size drops to ${\sim}$250 nm (Fig.
-\ref{figure:sink_strengths_neutron_5_1e-6}b).
-      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
-        \caption{GB Sink Strength for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
-        \label{figure:sink_strengths_neutron_5_1e-6}
-      \end{figure}
-
-      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
-        \caption{Total GB Sink Strengths for high dose neutron irradation with 5\% Production Bias}
-        \label{figure:sink_strengths_neutron_5_1e-3}
-      \end{figure}
-
-      \newpage
-      The calculated sink strengths for different production bias and for different grain sizes are presented by a 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
-      \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}}
-        \subfloat{b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}}
-        \qquad
-        \subfloat{c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}}
-        \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
-        \caption{Sink Strengths for low dose rate neutron irradiation}
-        \label{figure:sink_strength_moose_neutron_3D}
-      \end{figure}
-
-      \begin{figure}[h!]  %GB Sink Strength - Neutron 1e-6 dpa/s
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron}}
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron}}
-        \qquad
-        % \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron_500-5000nm}}
-        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
-        \caption{GB Sink Strengths for low dose rate neutron irradation}
-        \label{figure:sink_strengths_neutron_bias_Z}
-      \end{figure}
-
-      \begin{figure}[h!]  %Total GB Sink Strength - Neutron 1e-6 dpa/s
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron}}
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron}}
-        \qquad
-        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron_500-5000nm}}
-        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
-        \caption{Total GB Sink Strengths for low dose rate neutron irradation}
-        \label{figure:sink_strengths_neutron_bias_k}
-      \end{figure}
-
-  \newpage
-  \subsection{Ion Irradiation} \hspace{10pt}
-  Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic.
-Furthermore, they cannot penetrate through material too much because of their high energy loss in collisions.
-These characteristic causes a non-uniform defect production profile.
-Figure \ref{figure:defect_production} shows the profile used for ion irradation simulations.
-The dose rate, K\textsubscript{0} and grain size (1000 nm) would be scaled for the case of interest, but the profile doesn't change.
-    \begin{figure}[h!]  %Ion irradation
-      \centering
-      \subfloat{\includegraphics[scale=0.27]{defect_production}}
-      \qquad
-      \caption{Defect production profile for ion irradation.}
-      \label{figure:defect_production}
-    \end{figure}
-    \subsubsection{Concentrations} \hspace{10pt}
-    Even though ion irradation has non-uniform defect production, average defect concentrations show a time-dependent trend that is identical to the one in neutron irradation case.
-The only difference is the change in concentration levels as a result of less defect production (see Fig.
-\ref{figure:average_concentrations_ion_5}).
-
-    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_low_ion_5_size}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
-      \caption{Average Concentration profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
-      \label{figure:average_concentrations_ion_5}
-    \end{figure}
-
-    \newpage
-    The effect of defect production distribution can be observed obviously in concentration profiles.
-Since, defect production has peak at around half of the grain, the concentration profiles are taking shape under same behavior and reaching maximum at the center of domain, then waning through boundaries.
-
-    If production bias is zero, maximum concentration of each type of point defect becomes independent of grain sizes shown in Fig.
-\ref{figure:concentrations_ion_0_1e-6}.
-High ion dose rate only scales up the concentration levels without making any significant change in profiles (see Fig.
-\ref{figure:concentrations_ion_0_1e-3}).
-      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
-        \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
-        \label{figure:concentrations_ion_0_1e-6}
-      \end{figure}
-      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
-        \caption{Concentration profiles for high dose rate ion irradiation with 0\% Production Bias}
-        \label{figure:concentrations_ion_0_1e-3}
-      \end{figure}
-      \newpage
-      In case of applying production bias, profiles become completely different.
-The flipping behavior observed in neutron irradation case repeats on ion irradation case.
-In addition, the non-uniform defect production causes asymmetrical interstitial concentration profile given in Fig.
-\ref{figure:concentrations_ion_5_1e-6}a.
-The vacancy concentration profiles also loose their symmetry and shift up with increasing grain size (see Fig.
-\ref{figure:concentrations_ion_5_1e-6}b).
-Increase on ion dose rate, from 1e-6 dpa/s to 1e-3 dpa/s, combines with the effect of defect production profile and reduces the critical grain size to ${\sim}$250 nm.
-The flipping start to be visible through end of the grains.
-(see Fig.
-\ref{figure:concentrations_ion_5_1e-3}a).
-      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
-        \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
-        \label{figure:concentrations_ion_5_1e-6}
-      \end{figure}
-      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
-        \caption{Concentration profiles for high dose rate ion irradation with 5\% Production Bias}
-        \label{figure:concentrations_ion_5_1e-3}
-      \end{figure}
-
-    \newpage
-    \subsubsection{Supersaturation} \hspace{10pt}
-
-    The vacancy supersaturation curves for ion irradation case are quite similar to ones for neutron irradation case.
-The only difference is the asymmetrical shape of curves originates from concentration profiles.
-The non-linear increase in supersaturation values as domain gets larger is observed for ion irradation too.
-      \begin{figure}[h!]  %Ion - %5 Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
-        \caption{Vacancy Supersaturation profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
-        \label{figure:vacancy_supersaturation_ion_5}
-      \end{figure}
-      \newpage
-    \subsubsection{Sink Strengths} \hspace{10pt}
-    The sink strengths are directly related to concentration at center and flow at boundary.
-The change in centerline defect concentrations are not as considerable as neutron case.
-So, the flow or flux at boundary becomes more dominant on sink strength profiles (see Fig.
-\ref{figure:sink_strengths_ion_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}).
-      % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
-      %   \centering
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
-      %   \qquad
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
-      %   \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
-      %   \label{figure:sink_strengths_ion_0_1e-6}
-      % \end{figure}
-      \begin{figure}[h!]  %Sink Strength - ion 1e-6 dpa/s - 5% Bias rate
-        \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_Z_scaled}}
-        \qquad
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
-        \caption{GB Sink Strengths for low(a) and high(b) dose rate ion irradiation with 5\% Production Bias}
-        \label{figure:sink_strengths_ion_5_1e-6}
-      \end{figure}
-      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 5% Bias rate
-        \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
-        \caption{Total GB Sink Strengths for low(a) and high(b) dose rate ion irradiation with 5\% Production Bias}
-        \label{figure:sink_strengths_ion_5_1e-3}
-      \end{figure}
-
-% In nano-scale case, since the grain size is not big enough, the boundaries become
-% closer to each other. This causes point defects to reach sinks before they react with each other
-% and recombination plateau to disappear as it can be seen in Fig. 2. The nanoscale case acts like
-% a high-sink and high-temp condition case despite its low-sink and low-temperature. Therefore,
-% change in production bias does not have a significant effect on average concentration behavior
-% in nanoscale
-%
-% On the other hand, in micro-scale case, the domain has reasonable size, and thus
-% boundaries are far from each other. This provides defects more time to accumulate inside the
-% domain and recombine with each other after they reach a specific concentration. Figure 3
-% clearly shows the effect of production bias on average concentration.
-%
-% Effect of production bias on spatial profile of defect concentrations for nanoscale is
-% shown in Figure 4. The results seem not affected too much because of the same reasons
-% mentioned previously for average concentration.
-%
-% The micro-scale results (Fig. 5) are quite interesting and worth to think over. The
-% concentration profiles of interstitials for 0.1%, 5% and 10% cases are flipped over. A closer look
-% at evolution of 5% case over time in Fig. 6, after the end of quasi-steady-state region (t=10 -4 s in
-% Fig 3.), the average interstitial concentration starts to decrease as they segregate through sinks.
-% At steady state, the average interstitial concentration becomes minimum at the center and
-% maximum near boundaries because of segregation.
-%
-% The defect production rate (K 0 ) is the source term in point defect equations and has a
-% significant effect on concentrations.
-% In nano-scale case, the average concentration behavior is like high-sink density behavior
-% because of narrow domain. But, when the defect production rate increases, the average
-% concentration is shifted upward, and interstitial and vacancy average concentrations get closer
-% to each other because the production compensates more absorption at sinks than previous.
-% Based on this, if the production rate increased sufficiently, the recombination zone would
-% appear again in nano-scale domain.
-  \subsection{Discussion} \hspace{10pt}
-  What happens when switched from neutron irradation to ion irradiation
-  \begin{enumerate}
-    \item Loosing symmetry/uniformity in concentration profiles
-    \item Reduction in average concentration
-    \item Reduction in supersaturation
-  \end{enumerate}
-
-\newpage
-\section{Conclusion} \hspace{10pt}
-
-The rate theory equations resolve the temporal and spatial concentration profiles of point defects.
-The behavior of concentration distributions are controlled by parameters given in equation, representing their reactions and diffusion in domain.
-According to the results obtained in this study, the combination of production bias, production dose rate, production profile and grain size determine whether the steady state point defect concentration profile is symmetrical, flipped or both.
-There is always a critical value for parameters that could change the defect concentration profile entirely.
-
-% An online tool could be created to play with different parameters.
-% \begin{thebibliography}{00}
-% \bibitem{b2} Garry S. Was.
-% \end{thebibliography}
-\addcontentsline{toc}{section}{References}
-\bibliographystyle{unsrt}
-\bibliography{ref}
-
 \end{document}

### 2021-01-19 examples/point_defects/article/article.tex
article-edit

@@
 \usepackage{verbatim}
+\usepackage{xcolor}
 \usepackage[font=scriptsize]{caption}
@@
 Nickel is selected as a base material, and its properties are used in calculations.
+
+\textcolor{red}{!!!!!!!!!!!!!!!!!!!!!!!ADD PARAGRAPH!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
 
@@
 
+    \begin{figure}[htb!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
+      \centering
+      \subfloat{a)\includegraphics[scale=0.28]{data_neutron_250nm}}
+      \qquad
+      \subfloat{b)\includegraphics[scale=0.28]{data_neutron_1000nm}}
+      \caption{Change of interstitial concentration profiles with production bias for low dose rate neutron in a grain of a) 250 $nm$ and b) 1000 $nm$ }
+      \label{figure:3D_concentrations_neutron_1e-6}
+    \end{figure}
+
     \newpage
@@
 The plot shows a non-linear increase in supersaturation values as grain gets larger.
-      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
+      \begin{figure}[h!]  %Neutron - Vacancy Supersaturation - 5% Bias
         \centering
@@
 
+      \begin{figure}[htb!]  %Neutron - Vacancy Supersaturation
+        \centering
+        \subfloat{a)\includegraphics[scale=0.38]{data_neutron_Sv_center}}
+        \qquad
+        \subfloat{b)\includegraphics[scale=0.38]{data_high_neutron_Sv_center}}
+        \caption{Change of vacancy supersaturation at center with grain size and production bias for a)low dose rate neutron, b) high dose rate neutron}
+        \label{figure:3D_supersaturation_neutron}
+      \end{figure}
     \newpage
@@
 
+      \begin{figure}[htb!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
+        \centering
+        \subfloat{a)\includegraphics[scale=0.28]{data_low_ion_250nm}}
+        \qquad
+        \subfloat{b)\includegraphics[scale=0.28]{data_low_ion_1000nm}}
+        \caption{Change of interstitial concentration profiles with production bias for low dose rate ion in a grain of a) 250 $nm$ and b) 1000 $nm$ }
+        \label{figure:3D_concentrations_ion_1e-6}
+      \end{figure}
+
     \newpage
@@
       \end{figure}
+
+      \begin{figure}[htb!]  %Neutron - Vacancy Supersaturation
+        \centering
+        \subfloat{a)\includegraphics[scale=0.38]{data_low_ion_Sv_center}}
+        \qquad
+        \subfloat{b)\includegraphics[scale=0.38]{data_ion_Sv_center}}
+        \caption{Change of vacancy supersaturation at center with grain size and production bias for a) low dose rate ion, b) high dose rate ion}
+        \label{figure:3D_supersaturation_ion}
+      \end{figure}
+
+      The vacancy supersaturation behavior, shown in Fig.
+\ref{figure:3D_supersaturation_ion}, is identical to one in given for neutron irradiation case (see Fig.
+\ref{figure:3D_supersaturation_neutron}).
+This similarity makes it possible to use ions instead of neutrons to analyze swelling of reactor materials.
+
       \newpage
@@
 \ref{figure:sink_strengths_ion_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}).
-      % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
-      %   \centering
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
-      %   \qquad
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
-      %   \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
-      %   \label{figure:sink_strengths_ion_0_1e-6}
-      % \end{figure}
+      \begin{figure}[h!]  %
+        \centering
+        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_5-5000nm-low_ion-5}}
+        \qquad
+        \subfloat{b)\includegraphics[scale=0.55]{interstitial_concentration_5-5000nm-ion-5}}
+        \caption{Interstitial concentration profiles with 5\% production bias for a) low ion dose rate, b) high ion dose rate}
+        \label{figure:concentrations_ion_5_1e-3_5-5000nm}
+      \end{figure}
+
+      As it is discussed previously, since ions can not penetrate till the end of domain, they cause a non-uniform defect production.
+If the grain is small enough compared to penetration depth, concentration profiles are symmetrical, and the effect of distribution profile is not visible (up to 1000 $nm$ in Fig.
+\ref{figure:concentrations_ion_5_1e-3_5-5000nm}a and 50 $nm$ in Fig.
+\ref{figure:concentrations_ion_5_1e-3_5-5000nm}b).
+Yet, for larger grains, the defect concentrations are highly affected by non-uniformity.
+The flux at the far boundary oscillates and approaches to zero as grain size increases.
+Since sink strengths are related to the ratio of flux to concentration, they are affected by the oscillations in flux and concentration (see Fig.
+\ref{figure:sink_strengths_ion_5_1e-6}).
+
       \begin{figure}[h!]  %Sink Strength - ion 1e-6 dpa/s - 5% Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_Z_scaled}}
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_Z_scaled}}
         \qquad
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
+        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
         \caption{Change of GB sink strength with grain size for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
@@
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
         \qquad
@@
         \label{figure:sink_strengths_ion_5_1e-3}
+      \end{figure}
+
+      \begin{figure}[h!]  %Sink Strength 3D - Ion 1e-6 dpa/s
+        \centering
+        \subfloat{a)\includegraphics[scale=0.25]{data_low_ion_Zi}}
+        \subfloat{b)\includegraphics[scale=0.25]{data_low_ion_Zv}}
+        \qquad
+        \subfloat{c)\includegraphics[scale=0.25]{data_low_ion_ki}}
+        \subfloat{d)\includegraphics[scale=0.25]{data_low_ion_kv}}
+        \caption{Change of sink strengths with grain size and production bias for low dose rate ion in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
+        \label{figure:sink_strength_moose_neutron_3D}
       \end{figure}
@@
 % appear again in nano-scale domain.
+\newpage
   \subsection{Discussion} \hspace{10pt}
@@
 
-\newpage
 \section{Conclusion} \hspace{10pt}
@@
 There is always a critical value for parameters that could change the defect concentration profile entirely.
+
+Suplementary materials and extra figures are available at https://github.com/abdurrahmanozturk/articles
 

### 2021-01-25 examples/point_defects/article/abstract.tex
article-edit

--- 2021-01-11 examples/point_defects/article/article.tex
@@
 \title{Numerical Solution of Point Defect Equations by MOOSE}
-\author{Abdurrahman Ozturk$^{1}$, Author$^{1}$, Author$^{1}$, Karim Ahmed$^{1}$  \\
+\author{Abdurrahman Ozturk$^{1}$, Merve Gencturk$^{1}$, Author$^{1}$, Karim Ahmed$^{1}$  \\
         \small $^{1}$Texas A\&M University \\
@@
 Furthermore, it is predicted that whenever there is a production bias, no neutral sinks can exist, i.e., there is always a preference for surfaces/interfaces to absorb one type of defects over another.
-The model predictions demonstrate the shortcomings of the classical homogenous rate-theory approach and shed light on the limitations of using ion irradiation to mimic neutron irradiation.
+The model predictions demonstrate the shortcomings of the classical homogeneous rate-theory approach and shed light on the limitations of using ion irradiation to mimic neutron irradiation.
 
@@
 \newpage
+//
+radiation damage/interactions//
+motivation about paper//
+Harsh conditions//
+neutron-ion case comparison//
+instabilities, extended defects (Ghoniem paper)//
+in this study, focusing effect of grain size, bias, discrete surfaces,
+homogenized RT, spatially resolution//
+qualifying extended defects//
+profiles change with increasing radiation damage//
+
 \section{Methodology} \hspace{10pt}
@@
 The second term is a reaction term, referring the recombination process if the defect \textit{x} reacts with defect \textit{y} with a rate of \textit{K\textsubscript{xy}}.
-The third term is also a reaction term, representing the reaction between the defect \textit{x} and the sink \text{s} with a rate of \textit{K\textsubscript{xs}}.
+The third term is also a reaction term, representing the reaction between the defect \textit{x} and the sink \textit{s} with a rate of \textit{K\textsubscript{xs}}.
 In this study, the sink concentration is assumed constant and uniformly distributed over domain.
@@
 To make it easier to solve point defect equations numerically, their non-dimensionalized forms are implemented in MOOSE.
-The non-dimensionalization scheme and final form of equations are given in this section.
+The Multiphysics Object-Oriented Simulation Environment (MOOSE) is an open-source framework that provides users to solve partial differential equations (PDEs) and build a state-of-the-art, computationally scalable finite element-based simulations.
+\textcolor{red}{ref.} \\ The non-dimensionalization scheme and final form of equations are given in this section.
 
@@
 \subsection{Model Settings and Parameters} \hspace{10pt}
-Nickel is selected as a base material, and its properties are used in calculations.
+    Ni-based alloys have been used in many nuclear reactors applications because of their excellent corrosion resistance and high mechanical properties.
+For example, Ni-based alloys containing 15-30\% Cr are generally used in the cooling systems of reactors due to their corrosion resistance.
+However, radiation embrittlement, phase instability, and swelling caused by radiation in these materials can cause them to lose their properties.
+It is essential to predict the material structure changes due to radiation accurately.
+    To make a more detailed examination, for the neutron irradiation and ion irradiation case, Nickel is selected as a base material, and its properties are used in calculations.
 
@@
   \label{table:Ni_material_properties}
-  \begin{tabular}{ ||p{2cm}|p{2cm}||  }
+  \begin{tabular}{ ||p{5.5cm}|p{2cm}|p{2cm}||p{2cm}|p{2cm}||  }
      % \hline
@@
      \hline
-     Property & Value\\
+     Input Parameter & Symbol & Value & Units\\
      \hline\hline
-     a  & 0.352 nm\\
-     V  & 0.01206 nm^3\\
-     E_{m,i}  & 0.30 eV\\
-     E_{m,v}  & 1.30 eV\\
-     E_{f,i}  & 4.27 eV\\
-     E_{f,v}  & 1.60 eV\\
-     D_{0,i}  & 1e-7 m^2/s\\
-     D_{0,v}  & 6e-5 m^2/s\\
+
+    Lattice parameter & a  & 0.352  & nm\\
+    Volume & V  & 0.01206 & nm^3 \\
+    Migration energy for interstitial & E_{m,i}  & 0.30 & eV \\
+    Migration energy for vacancy & E_{m,v}  & 1.30 & eV \\
+    Formation energy for interstitial & E_{f,i}  & 4.27 & eV \\
+    Formation energy for vacancy & E_{f,v}  & 1.60 & eV  \\
+    Diffusion coefficient for interstitial & D_{0,i}  & 1e-7 & m^2/s  \\
+    Diffusion coefficient for vacancy & D_{0,v}  & 6e-5 & m^2/s  \\
 
@@
 
-In reactor environment, materials are exposed to different types of particle radiation such as electron, proton, neutron and ion.
-This study covers two most significant irradation types, neutrons and ions.
+Regarding cost and time, it can be understood that ion radiation has been used for a long time in experimental studies.
+However, with the development of reactor designs and the increase of long-term licensed reactors, it has been necessary to search for more reliable materials that can operate for a long time under extreme conditions.
+Therefore, it is essential to investigate the effects of neutron irradiation and ion irradiation in microstructure to determine the equality of neutron and ion irradiation results.
+
 The results obtained from MOOSE simulations are presented in this section by plots of defect concentration, vacancy supersaturation and sink strengths.
+The equations are solved in one direction using Lagrange elements and a second-order time integration scheme.
+In this work, the surfaces represent free surfaces or grain boundaries.
 %The calculated sink strengths are also tabulated for different grain size and bias rates.
@@
   Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable.
-Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE as benchmark problem, and its results are compared to analytical results for validation.
+Before presenting results from this study, a simple spherical grain problem for neutron irradiation is solved by MOOSE as benchmark problem, and its results are compared to analytical results for validation.
 
@@
   The defect concentrations can follow different patterns depending on their properties.
-Interstitials diffuse to sinks faster than vacancies, so their steady state concentrations becomes lower (see Fig.
+Interstitials diffuse to sinks faster than vacancies, so their steady-state concentrations become lower (see Fig.
 \ref{figure:average_concentrations_neutron_5}).
@@
 This is due to the fact that both factors affect the diffusion kinetics of defects.
-However, as will be discussed shortly, its effect on the spatial steady-state profiles is even more complex.
-The dose rate acts like an amplifier and change intensity of the defect behavior, thus the seperation between defect concentrations becomes more explicit.
+However, as will be discussed shortly, its effect on the steady-state spatial profiles is even more complicated.
+The dose rate acts as an amplifier and changes the intensity of the defect behavior.
+Thus the separation between defect concentrations becomes more explicit.
+
+//
+instability (flipping) affects the steady state concentrations levels//
+abnormal concentration behaviors for both transient(proposed in papers) steady state(observed in this study)//
+with grain size increase, defect concentrations diverges. this might initiate problems for physical properties, mechanical properties//
+less recombination, more vacancy more void more swelling//
 
@@
 
-    For unbiased case, as a result of uniform defect production and equilibrium condition at boundaries, the concentration profiles are symmetrical around domain center.
-The steady state concentration at center doesn't change significantly with increasing size as shown in Fig.
+    As a result of uniform defect production and equilibrium condition at boundaries, the concentration profiles are symmetrical around the domain center for an unbiased case.
+The steady-state concentration at the center doesn't change significantly with increasing size, as shown in Fig.
 \ref{figure:concentrations_neutron_0_1e-6}.
-In case of high dose rate neutron, concentration levels increase at the center of domain with higher gradients close to the boundaries.
+In the case of high dose rate neutron, concentration levels increase at the center of domain with higher gradients close to the boundaries.
 (see Fig.
@@
     \newpage
-     If production bias (\%5) is applied, the steady state concentration profiles change considerably.
+    Whenever a production bias exists, the steady-state profiles of defects show different trends.
+Depending on production rate and bias, a critical grain size exists above which the spatial dependence of the interstitial, the defect type with lower production rate, is reversed.
+This result can be attributed to the fact that production bias breaks the symmetry of the point defect balance leading to the manifestation of distinct steady-state profiles for the different defects.
+It is worth noting that such instability will make irradiation damage more pronounced.
+    Since it will enhance the clustering of different point defects into distinct extended defects, vacancies at the center of the domain will cluster into voids.
+Simultaneously, interstitials close to the boundaries will form dislocation loops.
+     In (\%5) production bias case, we have observed that the steady-state concentration profile has changed significantly.
 The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig.
 \ref{figure:concentrations_neutron_5_1e-6}a).
-Moreover, the depth of profile gets larger with increasing grain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary.
-The vacancy concentration, on the other hand, increases proportional to grain size, and its profile starts having peak at higher concentrations as seen in Fig.
+Moreover, the depth of profile gets larger with increasing grain size, which could be explained as accumulation of more interstitial atoms trying to reach equilibrium at boundary.
+On the other hand, the vacancy concentration increases equivalent to grain size, as seen in Fig.
 \ref{figure:concentrations_neutron_5_1e-6}b.\\
@@
 
-    Similar to unbiased case, average concentration levels increases with dose rate.
-But, the most important effect of high dose rate neutron is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig.
+    Similar to the unbiased case, average concentration levels increase with the dose rate.
+The most significant effect of high dose rate neutron is causing the interstitial concentration profile to reverse in smaller grain sizes than 500 nm.
+(see Fig.
 \ref{figure:concentrations_neutron_5_1e-3}).\\
@@
 
+    \begin{figure}[htb!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
+      \centering
+      \subfloat{a)\includegraphics[scale=0.28]{data_neutron_250nm}}
+      \qquad
+      \subfloat{b)\includegraphics[scale=0.28]{data_neutron_1000nm}}
+      \caption{Change of interstitial concentration profiles with production bias for low dose rate neutron in a grain of a) 250 $nm$ and b) 1000 $nm$ }
+      \label{figure:3D_concentrations_neutron_1e-6}
+    \end{figure}
+
+//
+change font size //
+comment on trends//
+1 paragraph//
+being radiation tolerant of nanocrystals//
+larger grain size increases clustering//
+
     \newpage
     \subsubsection{Supersaturation} \hspace{10pt}
+    Voids are the result of vacancy agglomeration.
+Therefore,  supersaturated vacancies in microstructure can lead to void formation.
+Moreover, void formation affects the properties of the material as it will change the material volume.
+The volume expansion of materials under irradiation is known as void swelling.
+In order to understand the details of void swelling behavior as a function of irradiation dose rate, the effective vacancy supersaturation is calculated.
+
     Supersaturation is a condition that the actual concentration of point defect is larger than its equilibrium concentration.
@@
 In both cases, the system is not at the minimum free energy.
-Both vacancies and interstitials could be supersaturated, then aggiomerate into voids or discs of interstitial atoms.
-These can produce stacking faults in crystal microstructure.
 
@@
 
-    The vacancy supersaturation curves for biased neutron irradation is given in Fig.
+    The vacancy supersaturation curves for biased neutron irradiation is given in Fig.
 \ref{figure:vacancy_supersaturation_neutron_5}.
-Since the defect concentrations have symmetrical profiles for neutron irradation, supersaturation curves are also symmetrical around grain center.
+Since the defect concentrations have symmetrical profiles for neutron irradiation, supersaturation curves are also symmetrical around grain center.
 The plot shows a non-linear increase in supersaturation values as grain gets larger.
-      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
+      \begin{figure}[h!]  %Neutron - Vacancy Supersaturation - 5% Bias
         \centering
@@
       \end{figure}
+
+      \begin{figure}[htb!]  %Neutron - Vacancy Supersaturation
+        \centering
+        \subfloat{a)\includegraphics[scale=0.38]{data_neutron_Sv_center}}
+        \qquad
+        \subfloat{b)\includegraphics[scale=0.38]{data_high_neutron_Sv_center}}
+        \caption{Change of vacancy supersaturation at center with grain size and production bias for a)low dose rate neutron, b) high dose rate neutron}
+        \label{figure:3D_supersaturation_neutron}
+      \end{figure}
+
+//
+linear dependence with production rate, non linear dependency with grain size and production bias//
 
@@
 
-    Using appropriate diffusion coefficient (${D}$), domain sink strength (${k^2}$) and concentration (${C_0}$) will give  relevant sink strengths.
-The analytical expressions for each defect type given by following equations
+    Using appropriate diffusion coefficient (${D}$), domain sink strength (${k^2}$) and// concentration (${C_0}$) will give  relevant sink strengths.
+The analytical expressions for each defect type given by following equations//
 
@@
 
-  The results of bencmark problem, previously discussed in Fig.
+  The results of benchmark problem, previously discussed in Fig.
 \ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations.
@@
 \ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}.
-The effect of flipping behavior is not visible in the plot of grain boundary sink strength, ${Z^{gb}}$, but there is a significant change on total grain boundary sink strength, ${k^2_i}$ after critical grain size of ${\sim}$1000 nm.
+The effect of reversal behavior is not visible in the plot of grain boundary sink strength, ${Z^{gb}}$, but there is a significant change on total grain boundary sink strength, ${k^2_i}$ after critical grain size of ${\sim}$1000 nm.
 In case of high dose rate, the critical grain size drops to ${\sim}$250 nm (Fig.
+
+    //
+    more comment on trends related to grain size, production bias, production rate//
+    critical grain size >>> critical size//
+
     \ref{figure:sink_strengths_neutron_5_1e-6}b).
@@
       \newpage
-      The calculated sink strengths for different production bias and for different grain sizes are presented by a 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
-      \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}}
-        \subfloat{b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}}
-        \qquad
-        \subfloat{c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}}
-        \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
-        \caption{Change of sink strengths with grain size and production bias for low dose rate neutron in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
-        \label{figure:sink_strength_moose_neutron_3D}
-      \end{figure}
 
@@
       \end{figure}
-
+  \newpage
+      The calculated sink strengths for different production bias and for different grain sizes are presented by a 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
+      \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
+        \centering
+        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}}
+        \subfloat{b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}}
+        \qquad
+        \subfloat{c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}}
+        \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
+        \caption{Change of sink strengths with grain size and production bias for low dose rate neutron in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
+        \label{figure:sink_strength_moose_neutron_3D}
+      \end{figure}
   \newpage
   \subsection{Ion Irradiation} \hspace{10pt}
-  Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic.
-Furthermore, they cannot penetrate through material too much because of their high energy loss in collisions.
-These characteristic causes a non-uniform defect production profile.
-Figure \ref{figure:defect_production} shows the profile used for ion irradation simulations.
-The dose rate, K\textsubscript{0} and grain size (1000 nm) would be scaled for the case of interest, but the profile doesn't change.
-    \begin{figure}[h!]  %Ion irradation
+  Contrary to neutrons, ions have a relatively narrow energy channel width, which is almost monoenergetic.
+Furthermore, they cannot penetrate through material excessively because of their high energy loss in collisions.
+This characteristic behavior causes a non-uniform defect production profile.
+Figure \ref{figure:defect_production} shows the profile used for ion irradiation simulations.
+The dose rate, K\textsubscript{0} and grain size (1000 nm) would be scaled for the case of interest, but it does not create a change in the profile.
+    \begin{figure}[h!]  %Ion irradiation
       \centering
@@
       \qquad
-      \caption{Defect production profile for ion irradation.}
+      \caption{Defect production profile for ion irradiation.}
       \label{figure:defect_production}
@@
     \subsubsection{Concentrations} \hspace{10pt}
-    Even though ion irradation has non-uniform defect production, average defect concentrations show a time-dependent trend that is identical to the one in neutron irradation case.
+    Even though ion irradiation has non-uniform defect production, average defect concentrations show a time-dependent trend that is identical to the one in neutron irradiation case.
 The only difference is the change in concentration levels as a result of less defect production (see Fig.
@@
       \subfloat{b)\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
-      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a) low ion dose rate, b) high ion dose rate}
+      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a) low dose rate ion, b) high dose rate ion}
       \label{figure:average_concentrations_ion_5}
@@
 \ref{figure:concentrations_ion_0_1e-6}.
-High ion dose rate only scales up the concentration levels without making any significant change in profiles (see Fig.
+High dose rate ion only scales up the concentration levels without making any significant change in profiles (see Fig.
 \ref{figure:concentrations_ion_0_1e-3}).
@@
         \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
-        \caption{Concentration profiles for low ion dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
+        \caption{Concentration profiles for low dose rate ion with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
         \label{figure:concentrations_ion_0_1e-6}
@@
         \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
-        \caption{Concentration profiles for high ion dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
+        \caption{Concentration profiles for high dose rate ion with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
         \label{figure:concentrations_ion_0_1e-3}
@@
       \newpage
-      In case of applying production bias, profiles become completely different.
-The flipping behavior observed in neutron irradation case repeats on ion irradation case.
+      In the case of applying production bias, profiles become completely different.
+The reversal behavior observed in neutron irradiation case repeats on ion irradiation case.
 In addition, the non-uniform defect production causes asymmetrical interstitial concentration profile given in Fig.
@@
 Increase on ion dose rate, from 1e-6 dpa/s to 1e-3 dpa/s, combines with the effect of defect production profile and reduces the critical grain size to ${\sim}$250 nm.
-The flipping start to be visible through end of the grains.
+The reversal start to be visible through end of the grains.
 (see Fig.
@@
         \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
-        \caption{Concentration profiles for low ion dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
+        \caption{Concentration profiles for low dose rate ion with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
         \label{figure:concentrations_ion_5_1e-6}
@@
         \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
-        \caption{Concentration profiles for high ion dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
+        \caption{Concentration profiles for high dose rate ion with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
         \label{figure:concentrations_ion_5_1e-3}
+      \end{figure}
+
+      \begin{figure}[htb!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
+        \centering
+        \subfloat{a)\includegraphics[scale=0.28]{data_low_ion_250nm}}
+        \qquad
+        \subfloat{b)\includegraphics[scale=0.28]{data_low_ion_1000nm}}
+        \caption{Change of interstitial concentration profiles with production bias for low dose rate ion in a grain of a) 250 $nm$ and b) 1000 $nm$ }
+        \label{figure:3D_concentrations_ion_1e-6}
       \end{figure}
@@
 
-    The vacancy supersaturation curves for ion irradation case are quite similar to ones for neutron irradation case.
+    The vacancy supersaturation curves for ion irradiation case are quite similar to ones for neutron irradiation case.
 The only difference is the asymmetrical shape of curves originates from concentration profiles.
-The non-linear increase in supersaturation values as domain gets larger is observed for ion irradation too.
+The non-linear increase in supersaturation values as domain gets larger is observed for ion irradiation too.
+
+    %\textcolor{blue}
+    The vacancy supersaturation behavior, shown in Fig.
+\ref{figure:3D_supersaturation_ion}, is identical to one in given for neutron irradiation case (see Fig.
+\ref{figure:3D_supersaturation_neutron}).
+The only difference is the asymmetrical shape of curves originating from defect production distribution.
+This similarity makes it possible to use ions instead of neutrons to predict the swelling behavior of reactor materials.
+The non-linear increase in supersaturation peak values might result in more void creation and undesired swelling behavior.
+
       \begin{figure}[h!]  %Ion - %5 Bias rate
@@
         \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
-        \caption{Vacancy supersaturation profiles for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
+        \caption{Vacancy supersaturation profiles for 5\% production bias, a) low dose rate ion, b) high dose rate ion}
         \label{figure:vacancy_supersaturation_ion_5}
       \end{figure}
+
+      \begin{figure}[htb!]  %Neutron - Vacancy Supersaturation
+        \centering
+        \subfloat{a)\includegraphics[scale=0.38]{data_low_ion_Sv_center}}
+        \qquad
+        \subfloat{b)\includegraphics[scale=0.38]{data_ion_Sv_center}}
+        \caption{Change of vacancy supersaturation at center with grain size and production bias for a) low dose rate ion, b) high dose rate ion}
+        \label{figure:3D_supersaturation_ion}
+      \end{figure}
+
     \newpage
@@
 \ref{figure:sink_strengths_ion_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}).
-      % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
-      %   \centering
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
-      %   \qquad
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
-      %   \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
-      %   \label{figure:sink_strengths_ion_0_1e-6}
-      % \end{figure}
+      \begin{figure}[h!]  %
+        \centering
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_5-5000nm-low_ion-5}}
+        \qquad
+        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_5-5000nm-ion-5}}
+        \caption{Interstitial concentration profiles with 5\% production bias for a) low dose rate ion, b) high dose rate ion}
+        \label{figure:concentrations_ion_5_1e-3_5-5000nm}
+      \end{figure}
+
+      %\textcolor{blue}{
+        As discussed previously, since ions can not penetrate until the end of the domain, they cause a non-uniform defect production.
+If the grain is small enough compared to penetration depth, concentration profiles become symmetrical (similar to neutron case), and the effect of distribution profile is not visible (up to 1000 $nm$ in Fig.
+\ref{figure:concentrations_ion_5_1e-3_5-5000nm}a and 50 $nm$ in Fig.
+\ref{figure:concentrations_ion_5_1e-3_5-5000nm}b).
+Yet, for larger grains, the defect concentrations are highly affected by non-uniformity.
+The flux at the far boundary oscillates and approaches zero as grain size increases.
+Since sink strengths are related to the ratio of flux to concentration, they are affected by those oscillations on the order of $10^{-9}$ (see Fig.
+\ref{figure:sink_strengths_ion_5_1e-6}).
+    %  }
+
+\newpage
       \begin{figure}[h!]  %Sink Strength - ion 1e-6 dpa/s - 5% Bias rate
@@
         \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
-        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
+        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low dose rate ion, b) high dose rate ion}
         \label{figure:sink_strengths_ion_5_1e-6}
@@
         \label{figure:sink_strengths_ion_5_1e-3}
+      \end{figure}
+
+//plot 3D sink strengths on python
+
+      \begin{figure}[h!]  %Sink Strength 3D - Ion 1e-6 dpa/s
+        \centering
+        \subfloat{a)\includegraphics[scale=0.25]{data_low_ion_Zi}}
+        \subfloat{b)\includegraphics[scale=0.25]{data_low_ion_Zv}}
+        \qquad
+        \subfloat{c)\includegraphics[scale=0.25]{data_low_ion_ki}}
+        \subfloat{d)\includegraphics[scale=0.25]{data_low_ion_kv}}
+        \caption{Change of sink strengths with grain size and production bias for low dose rate ion in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
+        \label{figure:sink_strength_moose_ion_3D}
       \end{figure}
@@
 % appear again in nano-scale domain.
+
+\clearpage
+    \subsection{Radiation-induced Segregation} \hspace{10pt}
+
+    Ni-Cr based alloys is one of the most important structural materials for current and future advanced fission reactor designs.
+Currently, Ni-Cr based alloys are used widely in light water reactors (LWR), particularly for reactor coolant systems.
+These alloys show high strength and resistance to swelling at high temperatures and superior corrosion performance.
+Despite their many advantages, however, irradiation may cause dramatic changes to composition of alloy following that radiation induced segregation (RIS) can take place near microstructural defects where materials are sensitive to corrosive attack.
+Point defects can migrate, recombine, and cancel each other out on numerous sinks i.e., dislocations, free surfaces, or grain boundaries.
+The migration of these point defects causes significant changes in microstructure with similar changes in behavior.
+Ni-Cr based alloys contains a high Cr content to prevent corrosion.
+The decrease in the local composition of Cr may result in severe structural changes.
+Predictions of the effects of RIS in Ni-Cr based alloys are crucial for determining safe limits in the work environment.
+
+    In this section, in order to understand the effect of production bias on the various spatial profile of atom and defect concentrations, we used 5\%, 10\%, and 20\% production bias factors to produce a difference between interstitial and vacancy generation.
+
+    \subsubsection{Rate Theory model for RIS} \hspace{10pt}
+
+    This model considers the coupling of defects and atom fluxes through migration of interstitials and vacancies in a binary Ni-Cr alloy.
+
+    \begin{equation}
+        \begin{aligned}
+        &\frac{dC_i}{dt} = - \nabla\cdot J_i + K_0 - K_{iv}C_iC_v - S \\
+        &\frac{dC_v}{dt} = - \nabla\cdot J_v + K_0 - K_{iv}C_iC_v - S\\
+        &\frac{dC_{Cr}}{dt} = - \nabla\cdot J_{Cr} \\
+        \end{aligned}
+        \label{equation:RIS_equations}
+     \end{equation}\\
+    In the above, $\nabla\cdot J_i$ and $\nabla\cdot J_v$ are the divergences of the vacancy and interstitial fluxes at defect sinks, and $K_0$, $K_{iv}C_IC_V$, S terms are the local total rates of production, recombination of point defects per unit volume and sink absorption rate respectively.
+    Vacancy and interstitial concentrations were determined as the concentrations at thermal equilibrium for the initial conditions of system.
+Cr concentration is taken as the nominal value in the alloy composition.
+We assume that the alloy atoms are randomly distributed throughout the grain at the initial time.
+The equations were solved numerically with the initial and boundary conditions, and one-dimension calculations were performed.
+
+    \begin{table}[h!]
+  \centering
+  \caption{Input Parameters for RIS }
+  \label{table:Input_parameters_for_RIS}
+  \begin{tabular}{ ||p{7cm}|p{1cm}|p{2cm}||p{1cm}|p{1.5cm}||  }
+     % \hline
+     % \multicolumn{5}{|c|}{Material Properties} \\
+     \hline
+     Input Parameter & Symbol & Value & Units &  Reference\\
+     \hline\hline
+
+     Vacancy jump frequency for Ni & \omega_{Ni,v}  & 0 & s^{-1} &\\
+     Vacancy jump frequency for Cr & \omega_{Cr,v}  & 0 & s^{-1} &\\
+     Interstitial jump frequency for Ni & \omega_{Ni,,i}  & 0 & s^{-1} &\\
+     Interstitial jump frequency for Cr & \omega_{Cr,i}  & 0 & s^{-1} &\\
+     Vacancy migration energy for Ni & E_{Ni,v}^m  & 0 & eV & \\
+     Vacancy migration energy for Cr & E_{Cr,v}^m  & 0 & eV & \\
+     Interstitial migration energy for Ni & E_{Ni,i}^m  & 0 & eV & \\
+     Interstitial migration energy for Cr  & E_{Cr,i}^m  & 0 & eV & \\
+     Vacancy jump correlation factor for Ni  & f_vNi  & 0 & unitless & \\
+     Vacancy jump correlation factor for Cr  & f_vCr  & 0 & unitless & \\
+     Interstitial jump correlation factor for Ni   & f_iNi  & 0 & unitless & \\
+     Interstitial jump correlation factor for Cr  & f_iCr  & 0 & unitless & \\
+     \hline
+  \end{tabular}
+\end{table}
+
+    \begin{equation}
+        \begin{aligned}
+        d_{z}^{v,i}\ =\frac{1}{6}\lambda^2 \omega f exp(\frac{-E_{z-v,i}^m}{k_B T})
+        \end{aligned}
+        \label{equation:RIS_equations}
+    \end{equation}\\
+    $d_{a}^{v,i}$ represents diffusivity coefficient for the atom-defect pairs.
+For the chosen z atom, in this work z is Ni and Cr atoms, $\lambda$ is jump distance, $\omega$ is jump frequency and f is correlation factor.
+For vacancy and interstitial, $E_{z-v,i}^m$ is migration energy and $k_B$ is Boltzmann constant.
+
+        RIS behavior in the alloy with Ni-18Cr composition shows a vacancy-driven inverse Kirkendall mechanism.
+While chromium diffuses rapidly with vacancy flux, the concentration of chromium decreases at the grain boundaries, and the concentration of Nickel moving slower than Chromium increases at the grain boundary.
+
+  \newpage
+
+     The concentration profiles of defects and Cr atoms at various production biases and grain sizes are presented in Figure \ref{figure:RIS}.
+Results show that at 50 nm grain size, effect of 5\%, 10\%, and 20\% production bias on interstitials does not show reversal behavior.
+Yet, at the grain size of 500 nm, the production bias effect shows reversal behavior on interstitials concentration.
+This conclusion also influences the Cr concentration profile.\\
+     The most critical consequence of the reversal behavior and sink density is that fast interstitials find sinks before vacancies.
+As a result of the interstitials finding sinks faster than vacancies, vacancy concentration continues to increase.
+This competition between interstitial and vacancy results in interstitials disappearing at the sink and recombining with vacancies.
+
+      \begin{figure}[h!]  %
+        \centering
+        \subfloat{a)\includegraphics[scale=0.55]{RIS_50nm_vacancy_concentraiton_bias.png}}
+        \subfloat{b)\includegraphics[scale=0.55]{RIS_500nm_vacancy_concentration_bias.png}}
+        \\
+        \subfloat{c)\includegraphics[scale=0.55]{RIS_50nm_interstitial_concentration_bias.png}}
+        \subfloat{d)\includegraphics[scale=0.55]{RIS_500nm_interstitial_concentration_bias.png}}
+        \\
+        \subfloat{e)\includegraphics[scale=0.55]{RIS_50nm_chromium_concentration_bias.png}}
+        \subfloat{f)\includegraphics[scale=0.55]{RIS_500nm_chromium_concentration_bias.png}}
+        \caption{Concentration profiles for high dose rate neutron with 0\%, 5\%, 10\%, and 20\% production bias a) 50 nm, vacancy concentration b) 500 nm, vacancy concentration c) 50 nm, interstitial concentration d) 500 nm, interstitial concentration e) 50 nm, chromium concentration f) 500 nm, chromium concentration }
+        \label{figure:RIS}
+      \end{figure}
+
+\clearpage
+
+    Fig.\ref{figure:RIS_Cr_concentration} shows the Cr concentration varying according to grain sizes and production bias.
+In Fig.\ref{figure:RIS_Cr_concentration}a, the vacancies and interstitials have the same generation rate.
+The change in Cr concentration profile between 50 and 1000 grain sizes is insignificant.
+We can say that as the grain size increases, the Cr segregation profile change is observed, but it is not marked clearly.
+With the purpose of effect of production bias, the production generation was re-analyzed with 20\% bias in the calculations.
+Fig.\ref{figure:RIS_Cr_concentration}b displays the Cr segregation profiles calculated with 20\% production bias in various grain sizes.
+It has been recognized that the area of Cr segregation increases with the increase of production bias and grain size.
+
+    \begin{figure}[h!]  %
+        \centering
+        \subfloat{a)\includegraphics[scale=0.55]{RIS_domainsize_all.png}}
+        \subfloat{b)\includegraphics[scale=0.55]{RIS_domainsize_all_20.png}}
+        \caption{Chromium concentration profiles with a) 0\% and b) 20\% production bias }
+        \label{figure:RIS_Cr_concentration}
+    \end{figure}
+
+        Trends in radiation-induced segregation in Ni-18Cr alloy occur with Cr depletion. The significance of the Cr segregation, related to the combination of production bias and domain size.\\
+
+\clearpage
+
   \subsection{Discussion} \hspace{10pt}
-  What happens when switched from neutron irradation to ion irradiation
+
+  What happens when switched from neutron irradiation to ion irradiation
   \begin{enumerate}
@@
 The behavior of concentration distributions are controlled by parameters given in equation, representing their reactions and diffusion in domain.
-According to the results obtained in this study, the combination of production bias, production dose rate, production profile and grain size determine whether the steady state point defect concentration profile is symmetrical, flipped or both.
+According to the results obtained in this study, the combination of production bias, production dose rate, production profile and grain size determine whether the steady state point defect concentration profile is symmetrical, reversed or both.
 There is always a critical value for parameters that could change the defect concentration profile entirely.
+The dependence of radiation induced segregation (RIS) on production biases and grain sizes was reproduced.
+Results shows that a combination of production bias and grain size results in the change of Cr segregation area.
 
@@
 \bibliographystyle{unsrt}
-\bibliography{ref}
+\bibliography{references}
 

### 2021-01-25 examples/point_defects/article/article.tex
article-edit

@@
         \caption{Change of sink strengths with grain size and production bias for low dose rate ion in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
-        \label{figure:sink_strength_moose_neutron_3D}
+        \label{figure:sink_strength_moose_ion_3D}
       \end{figure}

### 2021-01-25 examples/point_defects/article/plots/plot3.py

@@ -7,7 +7,7 @@ from matplotlib import cm
 from matplotlib.ticker import LinearLocator, FormatStrFormatter
 from mpl_toolkits.mplot3d import Axes3D
 
-scale=0.1
+scale=1
 
 #Read File
 filename = sys.argv[1]
@@ -27,15 +27,17 @@ cmaps= ['Greys', 'Purples', 'Blues', 'Greens', 'Oranges', 'Reds',
         'GnBu', 'PuBu', 'YlGnBu', 'PuBuGn', 'BuGn', 'YlGn']
 ax.set_xlabel(sys.argv[2])
 ax.set_ylabel(sys.argv[3])
-ax.set_zlabel(sys.argv[4])
+ax.set_zlabel(sys.argv[4],rotation=180)
 
 #Custom Labels
-ax.set_xlabel('x (nm)')
-# ax.set_xlabel('Grain Size (nm)')
+# ax.set_xlabel('x (nm)')
+ax.set_xlabel('Grain Size (nm)')
 ax.set_ylabel('Production Bias (%)')
-ax.set_zlabel('S$_v$')
+# ax.set_zlabel('S$_v$')
 # ax.set_zlabel('Interstitial Concentration')
 # ax.set_zlabel('C$_{i,center}$')
+# ax.set_zlabel('log Z$_v$ (m)')
+ax.set_zlabel('log k$^2_v$ (m$^{-2}$)')
 # ax.set_zlabel('Total GB Sink Strength (1/m^2)')
 
 #Create meshgrid from dataframe
@@ -53,7 +55,7 @@ for id in range(4,len(sys.argv)):
                 if row[sys.argv[2]]==X[i][j] and row[sys.argv[3]]==Y[i][j]:
                     Z[i][j]=row[sys.argv[id]]+1e-15
     # surf = ax.plot_wireframe(X*scale, Y, Z, label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cmaps[id-4], linewidth=1, color=palette(id-4), antialiased=False)
-    surf = ax.plot_surface(X*scale, Y, Z, label=r'log-${}_{}^2$'.format(sys.argv[id][0],sys.argv[id][1]), cmap=cm.coolwarm, linewidth=1, antialiased=True)
[…]

### 2021-02-12 examples/point_defects/article/abstract.tex
article-edit

@@
 \usepackage{xcolor}
+\usepackage{gensymb}
 \usepackage[font=scriptsize]{caption}
@@
 
+\color{red} Hoca, bu type neutron,ion kısım için neutron case de high dose rate için proton diyerek ekleyebiliriz bu kısmı tartışalım dedi.
+Apo'nun yazdığı kısmı etkileyecek hocam apo ile beraber tekrar tartışalım dedim.
+Bu kısmı sorarız tekrar.
+
 \begin{table}[h!]
@@
   \label{table:simulation_parameters}
-  \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}||  }
+  \begin{tabular}{ ||p{3cm}|p{2cm}|p{3cm}|p{3cm}|p{3cm}||  }
      % \multicolumn{5}{|c|}{Simulation Parameters} \\
      \hline
-     Type & Dose Rate (dpa/s) & Defect Production & Temperature (K) & Sink Density (m^{-3})\\
+     Defect Production & Type & Dose Rate (dpa/s) & Temperature (K) & Sink Density (m^{-3})\\
      \hline
      \hline
-     Neutron  & 1e-3  & Uniform     & 773 & 1e18\\
-              & 1e-6  & Uniform     & 773 & 1e18\\
+     Uniform     & Neutron  & 1e-6  & 773 & 1e18\\
+                 & Proton   & 1e-3  & 773 & 1e18\\
      \hline
-     Ion      & 1e-3  & Distributed & 773 & 1e18\\
-              & 1e-6  & Distributed & 773 & 1e18\\
+     Distributed & Ion      & 1e-3  & 773 & 1e18\\
+     % Distributed &           & 1e-6  & 773 & 1e18\\
      \hline
@@
       \centering
-      \subfloat{a)\includegraphics[scale=0.28]{data_neutron_250nm}}
+      \subfloat{a)\includegraphics[scale=0.25]{data_neutron_250nm}}
       \qquad
-      \subfloat{b)\includegraphics[scale=0.28]{data_neutron_1000nm}}
+      \subfloat{b)\includegraphics[scale=0.25]{data_neutron_1000nm}}
       \caption{Change of interstitial concentration profiles with production bias for low dose rate neutron in a grain of a) 250 $nm$ and b) 1000 $nm$ }
@@
 In case of high dose rate, the critical grain size drops to ${\sim}$250 nm (Fig.
+\ref{figure:sink_strengths_neutron_5_1e-6}b).
 
@@
     more comment on trends related to grain size, production bias, production rate//
-    critical grain size >>> critical size//
+    critical grain size $>$ critical size//
 
-    \ref{figure:sink_strengths_neutron_5_1e-6}b).
       \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
@@
         \centering
-        \subfloat{a)\includegraphics[scale=0.28]{data_low_ion_250nm}}
+        \subfloat{a)\includegraphics[scale=0.25]{data_low_ion_250nm}}
         \qquad
-        \subfloat{b)\includegraphics[scale=0.28]{data_low_ion_1000nm}}
+        \subfloat{b)\includegraphics[scale=0.25]{data_low_ion_1000nm}}
         \caption{Change of interstitial concentration profiles with production bias for low dose rate ion in a grain of a) 250 $nm$ and b) 1000 $nm$ }
@@
 
-//plot 3D sink strengths on python
+      //
+      plot 3D sink strength plots on python
 
@@
         \centering
-        \subfloat{a)\includegraphics[scale=0.25]{data_low_ion_Zi}}
-        \subfloat{b)\includegraphics[scale=0.25]{data_low_ion_Zv}}
+        \subfloat{a)\includegraphics[scale=0.55]{data_ion_sink_strength_Zi}}
+        \subfloat{b)\includegraphics[scale=0.55]{data_ion_sink_strength_Zv}}
         \qquad
-        \subfloat{c)\includegraphics[scale=0.25]{data_low_ion_ki}}
-        \subfloat{d)\includegraphics[scale=0.25]{data_low_ion_kv}}
+        \subfloat{c)\includegraphics[scale=0.55]{data_ion_sink_strength_ki}}
+        \subfloat{d)\includegraphics[scale=0.55]{data_ion_sink_strength_kv}}
         \caption{Change of sink strengths with grain size and production bias for low dose rate ion in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
@@
 
+        To examine the segregation effect at low temperature and high temperature, low-temperature 200\degree C, high-temperature 800\degree C, and 500\degree C temperature were selected as parameters.
+For Ni-18Cr alloy, Cr depletion was seen in the range from 200\degree C to 800\degree C.
+However, the highest Cr depletion effect was 20\% bias at 500\degree C.
+In general, it was observed that Cr depletion at 200\degree C increased at 500\degree C and decreased again at 800\degree C.
+It was found that this effect continues to increase in direct proportion to the increase in the production bias effect.\\
+
+        20\% production bias at 500\degree C shows the most remarkable Cr depletion effect, followed by 10\%  production bias at the same temperature.
+At high temperatures, the amount of Cr depletion is effectively reduced in the grain boundary.
+This may be due to the fact that at high temperatures, the interstitial concentration began to dominate the vacancy concentration.
+
+    \begin{figure}[h!]  %
+        \centering
+        \subfloat{a)\includegraphics[scale=0.55]{apo_article/plots/RIS_1vs10vs20_473_773_1073_Cr_conc.png}}
+        \subfloat{b)\includegraphics[scale=0.55]{apo_article/plots/RIS_1vs10vs20_473_773_1073_interstitial_conc.png}}
+        \subfloat{c)\includegraphics[scale=0.55]{apo_article/plots/RIS_1vs10vs20_473_773_1073_vacancy_conc.png}}
+        \caption{Concentration profiles at different temperatures and with 1\%, 10\% and 20\% bias a) chromium b) vacancy and c) interstitial concentration}
+        \label{figure:RIS_temperature}
+    \end{figure}
+
 \clearpage

### 2021-02-12 examples/point_defects/article/article.tex
article-edit

--- 2021-01-11 examples/point_defects/article/article.tex
@@
-\documentclass[a4paper]{article}
-\usepackage[margin=25mm]{geometry}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{verbatim}
-\usepackage[font=scriptsize]{caption}
-\pagenumbering{arabic}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
+% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.
+%                                              %
+%                                                                                                                                                         %
+% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% Version 3.4 Generated 2018/06/15 %%%
+%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
+%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
+%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%
+
+\documentclass[utf8]{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
+%\documentclass[utf8]{frontiersHLTH} % for Health articles
+%\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and Statistics articles
+
+%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
+\usepackage{url,hyperref,lineno,microtype,subcaption}
+\usepackage[onehalfspacing]{setspace}
 \graphicspath{ {./plots/} }
 
-% Keywords command
-\providecommand{\keywords}[1]
-{
-  \small
-  \textbf{\textit{Keywords---}} #1
-}
+% \linenumbers
 
-% \tableofcontents
+% Leave a blank line between paragraphs instead of using \\
 
-\title{Numerical Solution of Point Defect Equations by MOOSE}
-\author{Abdurrahman Ozturk$^{1}$, Author$^{1}$, Author$^{1}$, Karim Ahmed$^{1}$  \\
-        \small $^{1}$Texas A\&M University \\
-        % \small $^{2}$University B \\
-}
-% \date{} % Comment this line to show today's date
+\def\keyFont{\fontsize{8}{11}\helveticabold }
+\def\firstAuthorLast{Ozturk {et~al.}} %use et al only if is more than 1 author
+\def\Authors{Abdurrahman Ozturk\,$^{1,*}$, Merve Gencturk\,$^{1}$, Karim Ahmed\,$^{1}$}
+% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
+% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
+\def\Address{$^{1}$Department of Nuclear Engineering, Texas A\&M University, USA}
+% The Corresponding Author should be marked with an asterisk
+% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
+\def\corrAuthor{Abdurrahman Ozturk}
+\def\corrEmail{aozturk@tamu.edu}
+
 \begin{document}
+\onecolumn
+\firstpage{1}
+
+\title[Numerical Solution of Rate Theory Equations]{Numerical Solution of Point Defect(Rate Theory) Equations (in MOOSE)}
+
+\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
+\address{} %This field will be automatically populated
+\correspondance{} %This field will be automatically populated
+
+\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
+%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
+
 \maketitle
@@
 
+%%% Leave the Abstract empty if your article does not require one, please see the Summary Table for full details.
+\section{}
 We present a detailed investigation of the effect of size on the segregation of point defects to interfaces and the resultant nucleation of voids.
@@
 Furthermore, it is predicted that whenever there is a production bias, no neutral sinks can exist, i.e., there is always a preference for surfaces/interfaces to absorb one type of defects over another.
-The model predictions demonstrate the shortcomings of the classical homogenous rate-theory approach and shed light on the limitations of using ion irradiation to mimic neutron irradiation.
+The model predictions demonstrate the shortcomings of the classical homogeneous rate-theory approach and shed light on the limitations of using ion irradiation to mimic neutron irradiation.
 
-% Irradiation of a material creates point defects, vacancies and interstitials, as a result of
-% atomic collisions. Those point defects are mobile and able to diffuse through material, recombine with each other,
-% and disappear when they react with sinks.
-The concentration of both vacancy and interstitial can be described mathematically by chemical rate balance equations, named point defect equations (rate theory equations).
-Production, recombination, diffusion and reaction of point defects are given by separate terms in those equations, which makes it easy to solve and analyze each of them individually.
-In this work, spatially resolved non-dimensional point defect equations are solved in 1D by using MOOSE Framework.
-The effect of irradiation dose rate, sink density, temperature, uniform defect production, non-uniform defect production and biased defect production on steady state defect concentration profile and on grain boundary sink strength are studied.
-The calculations are also repeated for different grain sizes changing from 5\emph{nm} to 5$\mu$\emph{m} to investigate the effect of grain size on defect concentration and grain boundary sink strength.
-According to results, the grain size and defect production profile/bias have a significant effect on concentration profiles.
-They could create a flipped concentration profile through domain, which ends up with a defect segregation near grain boundary.
+\tiny
+ \keyFont{ \section{Keywords:} point defect equations, rate theory, interstitial, vacancy, radiation damage, MOOSE} %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+\end{abstract}
 
-\end{abstract} \hspace{10pt}
+\section{Introduction}
 
-%TC:ignore
-\keywords{point defect equations, rate theory, interstitial, vacancy, radiation damage, MOOSE}
-%TC:endignore
+\textcolor{red}{
+-articles about neutron, proton, ion irradiation\\
+radiation damage/interactions//
+motivation about paper//
+Harsh conditions//
+neutron-ion case comparison//
+instabilities, extended defects (Ghoniem paper)//
+in this study, focusing effect of grain size, bias, discrete surfaces,
+homogenized RT, spatially resolution//
+qualifying extended defects//
+profiles change with increasing radiation damage
+}
+% For Original Research Articles \citep{conference}, Clinical Trial Articles \citep{article}, and Technology Reports \citep{patent}, the introduction should be succinct, with no subheadings \citep{book}.
+For Case Reports the Introduction should include symptoms at presentation \citep{chapter}, physical exams and lab results \citep{dataset}.
 
-% Word count
-% \verbatiminput{\jobname.wordcount.tex}
+\section{Methodology}
 
-% \listoftables
-% \listoffigures
+% For requirements for a specific article type please refer to the Article Types on any Frontiers journal page.
+Please also refer to  \href{http://home.frontiersin.org/about/author-guidelines#Sections}{Author Guidelines} for further information on how to organize your manuscript in the required sections or their equivalents for your field
 
-\section{Introduction} \hspace{10pt}
-\newpage
-\section{Methodology} \hspace{10pt}
+% For Original Research articles, please note that the Material and Methods section can be placed in any of the following ways: before Results, before Discussion or after Discussion.
 
-\subsection{Point Defect Equations} \hspace{10pt}
-The irradiation of a material causes the creation of vacancies and interstitial because of
-atomic collisions. The point defects can diffuse through material, recombine with each other,
-and react with sinks which are present in microstructure. The concentration of point defects is
-described mathematically by the chemical rate balance equations given in following sets of equations.\\
+\subsection{Point Defect Equations}
+    The irradiation of a material causes the creation of vacancies and interstitial because of atomic collisions.
+The point defects can diffuse through material, recombine with each other, and react with sinks which are present in microstructure.
+The concentration of point defects is described mathematically by the chemical rate balance equations given in following sets of equations.
 
@@
     &\frac{dC_i}{dt} = K_0 - K_{iv}C_iC_v - K_{is}C_iC_s + \nabla\cdot D_i\nabla C_i\\
-    &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - K_{vs}C_vC_s + \nabla\cdot D_v\nabla C_v\\
+    &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - K_{vs}C_vC_s + \nabla\cdot D_v\nabla C_v
   \end{aligned}
   \label{equation:point_defect_equations}
-\end{equation}\\
+\end{equation}
 
@@
 The second term is a reaction term, referring the recombination process if the defect \textit{x} reacts with defect \textit{y} with a rate of \textit{K\textsubscript{xy}}.
-The third term is also a reaction term, representing the reaction between the defect \textit{x} and the sink \text{s} with a rate of \textit{K\textsubscript{xs}}.
+The third term is also a reaction term, representing the reaction between the defect \textit{x} and the sink \textit{s} with a rate of \textit{K\textsubscript{xs}}.
 In this study, the sink concentration is assumed constant and uniformly distributed over domain.
 The last term is diffusion term which is resolving the spatial behavior of defects.\\
-
-Another form of point defect equations can be written by using sink strength, \textit{k} definition for sink reaction term.\\
+    Another form of point defect equations can be written by using sink strength, \textit{k} definition for sink reaction term.
 
@@
 
-\subsection{Non-dimensionalization of Point Defect Equations} \hspace{10pt}
+\subsection{Non-dimensionalization of Point Defect Equations}
     The time space of defect interactions is enormously large, which could differ from nanoseconds to hours.
-In addition, rate coefficients also have different orders.
-To make it easier to solve point defect equations numerically, their non-dimensionalized forms are implemented in MOOSE.
-The non-dimensionalization scheme and final form of equations are given in this section.
-
-Scaling factors and non-dimensionalized variables are introduced as,
+Additionally, reaction rate coefficients also have different orders of magnitude.
+To deal with inconsistent dimensions, non-dimensionalized form of equations can be considered for numerical solution.
+To that end, the following non-dimensionalization scheme and scaling factors are introduced.
 
@@
 
-After substituting Eq. \ref{equation:non-dimensionalization_variables} into \ref{equation:point_defect_equations} and reorganizing, the non-dimensionalized version of point defect equations are,
+    After substituting Eq.
+\ref{equation:non-dimensionalization_variables} into \ref{equation:point_defect_equations} and reorganizing, final form  of non-dimensionalized point defect equations become,
 
@@
       \label{equation:non-dimensionalized_point_defect_equations}
-\end{equation}\\
+    \end{equation}
 
-\subsection{Model Settings and Parameters} \hspace{10pt}
-Nickel is selected as a base material, and its properties are used in calculations.
+    The Multiphysics Object-Oriented Simulation Environment (MOOSE) is used as tool to solve point defect equations numerically.
+MOOSE is an open-source framework that provides users to solve partial differential equations (PDEs) and build a state-of-the-art, computationally scalable finite element-based simulations.
+\textcolor{red}{ref.}\\
 
+\subsection{Model Settings and Parameters}
+    Ni-based alloys have been used in many nuclear reactors applications because of their excellent corrosion resistance and high mechanical properties.
+For example, Ni-based alloys containing 15-30\% Cr are generally used in reactor cooling systems due to their corrosion resistance.
+However, their properties change under irradiation and needs to be investigated.
+\textcolor{red}{irradiation induced embrittlement, phase instability, and swelling.
+It is essential to predict the material structure changes due to radiation accurately.} \citep{walgraef1996}
+
+    \textcolor{blue}{
+    Nickel is selected as base material for this study, and its properties; lattice parameter, $a$, is 0.352 $nm$, atomic volume, $V$, is 0.01206 $nm^3$, migration energy for interstitial, $E_{m,i}$, is 0.30 $eV$, migration energy for vacancy, $E_{m,v}$, is 1.30 $eV$, formation energy for interstitial, $E_{f,i}$, is 4.27 $eV$, formation energy for vacancy, $E_{f,v}$, is 1.60 $eV$, diffusion coefficient for interstitial, $D_{0,i}$, is 1e-7 $m^2/s$, and diffusion coefficient for vacancy, $D_{0,v}$, is 6e-5 $m^2/s$.
+    \citep{ref}
+    }\\
+
+    \textcolor{blue}{
+    In this study, three different irradiation types, neutrons, protons and ions, are considered.
+Their simulations are categorized into two groups based on defect production profile; uniform and non-uniform defect production.
+Neutrons are highly penetrable and causes uniform defect production on target material.
+Protons are not able to penetrate as much as neutrons do, but for small domain sizes, their defect production can be assumed as uniform.
+Ions or heavy charged particles loose their energies quickly and cause a non-uniform defect production.
+Table \ref{table:simulation_parameters} shows simulation parameters and values.
+    }
     \begin{table}[h!]
-  \centering
-  \caption{Material Properties for Nickel\cite{walgraef1996}}
-  \label{table:Ni_material_properties}
-  \begin{tabular}{ ||p{2cm}|p{2cm}||  }
-     % \hline
-     % \multicolumn{5}{|c|}{Material Properties} \\
+      \caption{Simulation Parameters}
+      \label{table:simulation_parameters}
+      \begin{tabular}{ ||>{\centering\arraybackslash}p{3.5cm}|>{\centering\arraybackslash}p{2cm}|>{\centering\arraybackslash}p{3cm}|>{\centering\arraybackslash}p{3cm}|>{\centering\arraybackslash}p{3.5cm}||  }
+         % \multicolumn{5}{|c|}{Simulation Parameters} \\
          \hline
-     Property & Value\\
-     \hline\hline
-     a  & 0.352 nm\\
-     V  & 0.01206 nm^3\\
-     E_{m,i}  & 0.30 eV\\
-     E_{m,v}  & 1.30 eV\\
-     E_{f,i}  & 4.27 eV\\
-     E_{f,v}  & 1.60 eV\\
-     D_{0,i}  & 1e-7 m^2/s\\
-     D_{0,v}  & 6e-5 m^2/s\\
-
+         Defect Production & Type & Dose Rate (dpa/s) & Temperature (K) & Sink Density (m^{-3})\\
+         \hline
+         \hline
+         Uniform     & Neutron  & 1e-6  & 773 & 1e18\\
+                     & Proton   & 1e-3  & 773 & 1e18\\
+         \hline
+         Non-Uniform & Ion      & 1e-3  & 773 & 1e18\\
+         % Distributed &           & 1e-6  & 773 & 1e18\\
          \hline
@@
 
-\begin{table}[h!]
-  \centering
-  \caption{Simulation Parameters}
-  \label{table:simulation_parameters}
-  \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}||  }
-     % \multicolumn{5}{|c|}{Simulation Parameters} \\
-     \hline
-     Type & Dose Rate (dpa/s) & Defect Production & Temperature (K) & Sink Density (m^{-3})\\
-     \hline
-     \hline
-     Neutron  & 1e-3  & Uniform     & 773 & 1e18\\
-              & 1e-6  & Uniform     & 773 & 1e18\\
-     \hline
-     Ion      & 1e-3  & Distributed & 773 & 1e18\\
-              & 1e-6  & Distributed & 773 & 1e18\\
-     \hline
-  \end{tabular}
-\end{table}
+% \textcolor{red}{
+% Hoca, bu type neutron,ion kısım için neutron case de high dose rate için proton diyerek ekleyebiliriz bu kısmı tartışalım dedi.
+Apo'nun yazdığı kısmı etkileyecek hocam apo ile beraber tekrar tartışalım dedim.
+Bu kısmı sorarız tekrar.
+% }
 
-\newpage
-\section{Results} \hspace{10pt}
+% \textcolor{red}{
+% Tables should be inserted at the end of the manuscript.
+Please build your table directly in LaTeX.Tables provided as jpeg/tiff files will not be accepted.
+Please note that very large tables (covering several pages) cannot be included in the final PDF for reasons of space.
+These tables will be published as \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} on the online article page at the time of acceptance.
+The author will be notified during the typesetting of the final article if this is the case.
+% }
 
-In reactor environment, materials are exposed to different types of particle radiation such as electron, proton, neutron and ion.
-This study covers two most significant irradation types, neutrons and ions.
+\section{Results}
+
+    Regarding cost and time, it can be understood that ion radiation has been used for a long time in experimental studies.
+However, with the development of reactor designs and the increase of long-term licensed reactors, it has been necessary to search for more reliable materials that can operate for a long time under extreme conditions.
+Therefore, it is essential to investigate the effects of neutron irradiation and ion irradiation in microstructure to determine the equality of neutron and ion irradiation results.
+
     The results obtained from MOOSE simulations are presented in this section by plots of defect concentration, vacancy supersaturation and sink strengths.
-%The calculated sink strengths are also tabulated for different grain size and bias rates.
+The equations are solved in one direction using Lagrange elements and a second-order time integration scheme.
+In this work, the surfaces represent free surfaces or grain boundaries.\\ %The calculated sink strengths are also tabulated for different grain size and bias rates.
 
-  \subsection{Neutron Irradiation} \hspace{10pt}
+\subsection{Uniform Irradiation}
     Neutrons have an energy spectrum that varies a couple of orders of magnitude.
@@
 Also, the high penetration depth of neutrons allow them to travel through material corresponding to their energies.
-Thus, they cause a uniform or flat-like defect production profile in material.\cite{was2016}
+Thus, they cause a uniform or flat-like defect production profile in material.
+\citep{was2017}
 
     Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable.
-Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE as benchmark problem, and its results are compared to analytical results for validation.
+Before presenting results from this study, a simple spherical grain problem for neutron irradiation is solved by MOOSE as benchmark problem, and its results are compared to analytical results for validation.
 
     In this approach, unlike the simulations in this study, the mutual recombination term in Eq.
-\ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for a spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\
+\ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for a spherical grain of radius \textit{a} are found as below.
+\citep{heald1977}\\
 
@@
     \end{equation}\\
+
     \begin{equation}
@@
 As seen in Fig.
-\ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.
+\ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.\\
+
     \begin{figure}[h!]
@@
     \end{figure}
-  \newpage
-  \subsubsection{Concentrations} \hspace{10pt}
+
+ \subsubsection{Concentrations}
     The defect concentrations can follow different patterns depending on their properties.
-Interstitials diffuse to sinks faster than vacancies, so their steady state concentrations becomes lower (see Fig.
+Interstitials diffuse to sinks faster than vacancies, so their steady-state concentrations become lower (see Fig.
 \ref{figure:average_concentrations_neutron_5}).
@@
 This is due to the fact that both factors affect the diffusion kinetics of defects.
-However, as will be discussed shortly, its effect on the spatial steady-state profiles is even more complex.
-The dose rate acts like an amplifier and change intensity of the defect behavior, thus the seperation between defect concentrations becomes more explicit.
+However, as will be discussed shortly, its effect on the steady-state spatial profiles is even more complicated.
+The dose rate acts as an amplifier and changes the intensity of the defect behavior.
+Thus the separation between defect concentrations becomes more explicit.
+
+\textcolor{red}{
+instability (flipping) affects the steady state concentrations levels//
+abnormal concentration behaviors for both transient(proposed in papers) steady state(observed in this study)//
+with grain size increase, defect concentrations diverges. this might initiate problems for physical properties, mechanical properties//
+less recombination, more vacancy more void more swelling
+}
 
@@
         \centering
-      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
+        a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}
         \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
-      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a)low dose rate neutron, b) high dose rate neutron}
+        b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}
+        \caption{Time-dependent behavior of average defect concentration for different grain sizes with 5\% production bias for a) neutrons and b) protons}
         \label{figure:average_concentrations_neutron_5}
@@
 
-    For unbiased case, as a result of uniform defect production and equilibrium condition at boundaries, the concentration profiles are symmetrical around domain center.
-The steady state concentration at center doesn't change significantly with increasing size as shown in Fig.
+    Uniform defect production and equilibrium condition at boundaries result in a symmetrical concentration profile around the domain center for neutron case.
+The steady-state concentrations at the center doesn't change significantly with increasing size, as shown in Fig.
 \ref{figure:concentrations_neutron_0_1e-6}.
-In case of high dose rate neutron, concentration levels increase at the center of domain with higher gradients close to the boundaries.
-(see Fig.
-\ref{figure:concentrations_neutron_0_1e-3}).\\
 
-    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
-      \caption{Concentration profiles for low dose rate neutron with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
-      \label{figure:concentrations_neutron_0_1e-6}
-    \end{figure}
-    \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
-      \caption{Concentration profiles for high dose rate neutron with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
-      \label{figure:concentrations_neutron_0_1e-3}
-    \end{figure}
-    \newpage
-     If production bias (\%5) is applied, the steady state concentration profiles change considerably.
+    Protons tend to create more defect on material, and consequently concentration levels are higher compared to neutrons.(see Fig. \ref{figure:concentrations_neutron_0_1e-3}).
+
+    % \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
+    %     \centering
+    %     a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}
+    %     b)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}
+    %     c)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}
+    %     d)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}
+    %     \caption{Concentration profiles with 0\% production bias, interstitial concentration for a) neutrons and b) protons, vacancy concentration for c) neutrons and b) protons}
+    %     \label{figure:concentrations_neutron_0_1e-6}
+    % \end{figure}
+
+    Whenever a production bias exists, the steady-state profiles of defects show different trends.
+Depending on production rate and bias, a critical grain size exists above which the spatial dependence of the interstitial, the defect type with lower production rate, is reversed.
+This result can be attributed to the fact that production bias breaks the symmetry of the point defect balance leading to the manifestation of distinct steady-state profiles for the different defects.
+It is worth noting that such instability will make irradiation damage more pronounced.
+    Since it will enhance the clustering of different point defects into distinct extended defects, vacancies at the center of the domain will cluster into voids.
+Simultaneously, interstitials close to the boundaries will form dislocation loops.
+    In (\%5) production bias case, we have observed that the steady-state concentration profile has changed significantly.
 The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig.
 \ref{figure:concentrations_neutron_5_1e-6}a).
-Moreover, the depth of profile gets larger with increasing grain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary.
-The vacancy concentration, on the other hand, increases proportional to grain size, and its profile starts having peak at higher concentrations as seen in Fig.
-\ref{figure:concentrations_neutron_5_1e-6}b.\\
+Moreover, the depth of profile gets larger with increasing grain size, which could be explained as accumulation of more interstitial atoms trying to reach equilibrium at boundary.
+On the other hand, the vacancy concentration increases equivalent to grain size, as seen in Fig.
+\ref{figure:concentrations_neutron_5_1e-6}b.
+
+    Similar to the unbiased case, protons increases average concentration levels.
+The most significant effect of protons is causing decrease in critical grain size.
+Therefore, the interstitial concentration profile starts being reversed in smaller grain sizes than 500 nm.
+(see Fig.
+\ref{figure:concentrations_proton_5_1e-3}).\\
     \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
         \centering
-      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
-      \caption{Concentration profiles for low dose rate neutron with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
+        a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}
+        b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}
+        c)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}
+        d)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}
+        e)\includegraphics[scale=0.55]{average_concentration_250nm}
+        f)\includegraphics[scale=0.55]{interstitial_concentration_time_evolution_250nm}
+        \caption{Concentration profiles with 5\% production bias for neutrons (a,b) and protons (c,d).
+e) Average defect concentration change with time for ${250nm}$.
+f) The evolution of interstitial concentration profile for ${250nm}$}
         \label{figure:concentrations_neutron_5_1e-6}
@@
 
-    Similar to unbiased case, average concentration levels increases with dose rate.
-But, the most important effect of high dose rate neutron is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig.
-\ref{figure:concentrations_neutron_5_1e-3}).\\
-    \begin{figure}[htb!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
-      \caption{Concentration profiles for high dose rate neutron with 0\% production bias, a) interstitial concentration b) vacancy concentration}
-      \label{figure:concentrations_neutron_5_1e-3}
-    \end{figure}
+\textcolor{red}{
+change font size //
+comment on trends//
+1 paragraph//
+being radiation tolerant of nanocrystals//
+larger grain size increases clustering//
+}
+\\
+\subsubsection{Vacancy Supersaturation}
+    Voids are the result of vacancy agglomeration.
+Therefore,  supersaturated vacancies in microstructure can lead to void formation.
+Moreover, void formation affects the properties of the material as it will change the material volume.
+The volume expansion of materials under irradiation is known as void swelling.
+In order to understand the details of void swelling behavior as a function of irradiation dose rate, the effective vacancy supersaturation is calculated.
 
-    \newpage
-    \subsubsection{Supersaturation} \hspace{10pt}
     Supersaturation is a condition that the actual concentration of point defect is larger than its equilibrium concentration.
@@
 In both cases, the system is not at the minimum free energy.
-Both vacancies and interstitials could be supersaturated, then aggiomerate into voids or discs of interstitial atoms.
-These can produce stacking faults in crystal microstructure.
 
-    The effective vacancy supersaturation, ${S_v}$ is calculated by using following equation, \cite{was2016}\\
+    The effective vacancy supersaturation, ${S_v}$ is calculated by using following equation, \citep{was2017}
 
@@
         \end{aligned}
-    \end{equation}\\
+    \end{equation}
 
-    The vacancy supersaturation curves for biased neutron irradation is given in Fig.
-\ref{figure:vacancy_supersaturation_neutron_5}.
-Since the defect concentrations have symmetrical profiles for neutron irradation, supersaturation curves are also symmetrical around grain center.
+    The vacancy supersaturation curves for biased neutron irradiation is given in Fig.
+\ref{figure:vacancy_supersaturation_neutron}.
+Since the defect concentrations have symmetrical profiles for neutron irradiation, supersaturation curves are also symmetrical around grain center.
 The plot shows a non-linear increase in supersaturation values as grain gets larger.
-      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
-        \caption{Vacancy supersaturation profiles for 5\% production bias, a)low dose rate neutron, b) high dose rate neutron}
-        \label{figure:vacancy_supersaturation_neutron_5}
-      \end{figure}
+
+\textcolor{red}{
+linear dependence with production rate, non linear dependency with grain size and production bias//
+}
 
     \newpage
-    \subsubsection{Sink Strengths} \hspace{10pt}
+    \subsubsection{Grain Boundary Sink Strength}
     The sink reaction term in Eq.
@@
     \end{equation}\\
-    The total grain boundary sink strength, ${k^2_{gb}}$ is calculated by multiplying ${Z_{gb}}$ by the grain density, ${\rho_{gb}}$.\cite{heald1977}
+    The total grain boundary sink strength, ${k^2_{gb}}$ is calculated by multiplying ${Z_{gb}}$ by the grain density, ${\rho_{gb}}$. \citep{heald1977}
     \begin{equation}
@@
 \ref{equation:spherical_grain_analytical_solution} into expressions above.
-Thus, grain boundary sink strengths are associated with the domain sink strength, ${k^2}$.\cite{heald1977}
+Thus, grain boundary sink strengths are associated with the domain sink strength, ${k^2}$.
+\citep{heald1977}
 
@@
 
-    Using appropriate diffusion coefficient (${D}$), domain sink strength (${k^2}$) and concentration (${C_0}$) will give  relevant sink strengths.
-The analytical expressions for each defect type given by following equations
+    Grain Boundary sink strength for different defect type can be calculated by using appropriate diffusion coefficient (${D}$), domain sink strength (${k^2}$) and concentration (${C_0}$).
+The analytical expression for each is given by following equations,
 
@@
 
-  The results of bencmark problem, previously discussed in Fig.
-\ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations.
-Table \ref{table:sink_strengths_calculations} show the comparison of calculations.
-    \begin{table}[h!]
-      \centering
-      \caption{Comparison of sink strength calculations}
-      \label{table:sink_strengths_calculations}
-      \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}||  }
-         \hline
-          & MOOSE & Analytical\\
-         \hline\hline\hline
-         ${Z_{gb,i}}$  & 1.257206e-05 m & 1.257332e-05 m\\
-         ${Z_{gb,v}}$  & 1.256941e-05 m & 1.257332e-05 m\\
-         ${k_{gb,i}}$  & 2.401086e+13 m^{-2} & 2.401327e+13 m^{-2}\\
-         ${k_{gb,v}}$  & 2.400580e+13 m^{-2} & 2.401327e+13 m^{-2}\\
-         \hline
-      \end{tabular}
-    \end{table}
-    \newpage
-    Sink strength plots are presented in Fig.
-\ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}.
-The effect of flipping behavior is not visible in the plot of grain boundary sink strength, ${Z^{gb}}$, but there is a significant change on total grain boundary sink strength, ${k^2_i}$ after critical grain size of ${\sim}$1000 nm.
-In case of high dose rate, the critical grain size drops to ${\sim}$250 nm (Fig.
-\ref{figure:sink_strengths_neutron_5_1e-6}b).
+    The results of benchmark problem, previously discussed in Fig. \ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations.
+
+    Calculated sink strengths for different grain sizes are shown in Fig \ref{figure:sink_strengths_neutron_5_1e-6}.
+The grain boundary sink strengths, ${Z^{gb}}$ and ${k^2_i}$, separate from each other after critical grain size value for both neutrons (Fig \ref{figure:sink_strengths_neutron_5_1e-6} a,c) and protons (Fig \ref{figure:sink_strengths_neutron_5_1e-6} b,d).
+The separation is more significant for protons because of higher dose rate.
+
+    The change of sink strengths with different production bias or grain sizes are presented in 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
+
+\textcolor{red}{
+more comment on trends related to grain size, production bias, production rate//
+critical grain size $>$ critical size//
+}
     \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
         \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
-        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low dose rate neutron, b) high dose rate neutron}
+        a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}
+        b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}
+        \caption{Change of grain boundary sink strengths with grain size for 5\% production bias, a) neutron, b) proton}
         \label{figure:sink_strengths_neutron_5_1e-6}
-      \end{figure}
-
-      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
-        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low dose rate neutron, b) high dose rate neutron}
-        \label{figure:sink_strengths_neutron_5_1e-3}
-      \end{figure}
-
-      \newpage
-      The calculated sink strengths for different production bias and for different grain sizes are presented by a 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
-      \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}}
-        \subfloat{b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}}
-        \qquad
-        \subfloat{c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}}
-        \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
-        \caption{Change of sink strengths with grain size and production bias for low dose rate neutron in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
-        \label{figure:sink_strength_moose_neutron_3D}
     \end{figure}
@@
         \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_Zi_scaled_nolegend}}
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_Zv_scaled_nolegend}}
-        \subfloat{\includegraphics[scale=0.35]{legend}}
-        \qquad
-        % \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron_500-5000nm}}
-        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
-        \caption{Change of sink strengths with production bias for low dose rate neutron, a) interstitial GB sink strength, b) vacancy GB sink strength}
+        a)\includegraphics[scale=0.55]{sink_strength_neutron_Zi_scaled_nolegend}
+        b)\includegraphics[scale=0.55]{sink_strength_neutron_Zv_scaled_nolegend}
+        \includegraphics[scale=0.35]{legend}
+        c)\includegraphics[scale=0.55]{sink_strength_high_neutron_Zi_scaled_nolegend}
+        d)\includegraphics[scale=0.55]{sink_strength_high_neutron_Zv_scaled_nolegend}
+        \includegraphics[scale=0.35]{legend}
+        \caption{Change of grain boundary sink strengths with production bias and grain size for neutrons (a,b) and protons (c,d)}
         \label{figure:sink_strengths_neutron_bias_Z}
@@
 
-      \begin{figure}[h!]  %Total GB Sink Strength - Neutron 1e-6 dpa/s
+    %   \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
+    %     \centering
+    %     a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}
+    %     b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}
+    %     c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}
+    %     d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}
+    %     \caption{Change of sink strengths with grain size and production bias for neutrons in log scale, a)interstitial grain boundary sink strength, b) vacancy grain boundary sink strength, c) total interstitial grain boundary sink strength, d) total vacancy grain boundary sink strength}
+    %     \label{figure:sink_strength_moose_neutron_3D}
+    %   \end{figure}
+
+\clearpage
+\subsection{Non-Uniform Irradiation}
+    Contrary to neutrons, ions have a relatively narrow energy channel width, which is almost monoenergetic.
+Furthermore, they cannot penetrate through material excessively because of their high energy loss in collisions.
+This characteristic behavior causes a non-uniform defect production profile.
+Figure \ref{figure:defect_production} shows the profile used for ion irradiation simulations.
+The dose rate, K\textsubscript{0} and grain size (1000 nm) would be scaled for the case of interest, but it does not create a change in the profile.
+    \begin{figure}[h!]  %Ion irradiation
         \centering
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_ki_scaled_nolegend}}
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_kv_scaled_nolegend}}                \subfloat{\includegraphics[scale=0.35]{legend}}
+        a)\includegraphics[scale=0.27]{defect_production}
         \qquad
-        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron_500-5000nm}}
-        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
-        \caption{Change of sink strengths with production bias for low dose rate neutron, a) total interstitial GB sink strength, b) total vacancy GB sink strength}
-        \label{figure:sink_strengths_neutron_bias_k}
-      \end{figure}
-
-  \newpage
-  \subsection{Ion Irradiation} \hspace{10pt}
-  Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic.
-Furthermore, they cannot penetrate through material too much because of their high energy loss in collisions.
-These characteristic causes a non-uniform defect production profile.
-Figure \ref{figure:defect_production} shows the profile used for ion irradation simulations.
-The dose rate, K\textsubscript{0} and grain size (1000 nm) would be scaled for the case of interest, but the profile doesn't change.
-    \begin{figure}[h!]  %Ion irradation
-      \centering
-      \subfloat{\includegraphics[scale=0.27]{defect_production}}
-      \qquad
-      \caption{Defect production profile for ion irradation.}
+        b)\includegraphics[scale=0.55]{average_concentration_ion_5_size}
+        \caption{a)Defect production profile for ion irradiation, b)Time-dependent behavior of average defect concentration  with 5\% production bias for ions}
         \label{figure:defect_production}
     \end{figure}
-    \newpage
-    \subsubsection{Concentrations} \hspace{10pt}
-    Even though ion irradation has non-uniform defect production, average defect concentrations show a time-dependent trend that is identical to the one in neutron irradation case.
+\subsubsection{Concentrations}
+    Even though ion irradiation has non-uniform defect production, average defect concentrations show a time-dependent trend that is identical to the one in neutron irradiation case.
 The only difference is the change in concentration levels as a result of less defect production (see Fig.
 \ref{figure:average_concentrations_ion_5}).
-
-    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
-      \centering
-      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_low_ion_5_size}}
-      \qquad
-      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
-      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a) low ion dose rate, b) high ion dose rate}
-      \label{figure:average_concentrations_ion_5}
-    \end{figure}
 
@@
 
-    If production bias is zero, maximum concentration of each type of point defect becomes independent of grain sizes shown in Fig.
-\ref{figure:concentrations_ion_0_1e-6}.
-High ion dose rate only scales up the concentration levels without making any significant change in profiles (see Fig.
-\ref{figure:concentrations_ion_0_1e-3}).
-      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
-        \caption{Concentration profiles for low ion dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
-        \label{figure:concentrations_ion_0_1e-6}
-      \end{figure}
-      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
-        \caption{Concentration profiles for high ion dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
-        \label{figure:concentrations_ion_0_1e-3}
-      \end{figure}
-      \newpage
-      In case of applying production bias, profiles become completely different.
-The flipping behavior observed in neutron irradation case repeats on ion irradation case.
-In addition, the non-uniform defect production causes asymmetrical interstitial concentration profile given in Fig.
-\ref{figure:concentrations_ion_5_1e-6}a.
+    If production bias is zero, maximum concentration of each type of point defect becomes independent of grain sizes shown in Fig. \ref{figure:concentrations_ion_0_1e-3}).
+
+    %   \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
+    %     \centering
+    %     a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}
+    %     b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}
+    %     \caption{Concentration profiles for ions with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
+    %     \label{figure:concentrations_ion_0_1e-3}
+    %   \end{figure}
+
+    In the case of applying production bias, profiles become completely different.
+In addition to the reversal behavior observed in neutron irradiation case, the non-uniform defect production profile causes asymmetrical interstitial concentration profile as given in Fig.
+\ref{figure:concentrations_ion_5_1e-3}a.
+The critical grain size for ion case occurs around ${\sim}$1000 nm.
 The vacancy concentration profiles also loose their symmetry and shift up with increasing grain size (see Fig.
-\ref{figure:concentrations_ion_5_1e-6}b).
-Increase on ion dose rate, from 1e-6 dpa/s to 1e-3 dpa/s, combines with the effect of defect production profile and reduces the critical grain size to ${\sim}$250 nm.
-The flipping start to be visible through end of the grains.
-(see Fig.
-\ref{figure:concentrations_ion_5_1e-3}a).
+\ref{figure:concentrations_ion_5_1e-3}b).
+
       \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
         \centering
-        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
-        \caption{Concentration profiles for low ion dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
-        \label{figure:concentrations_ion_5_1e-6}
-      \end{figure}
-      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
-        \caption{Concentration profiles for high ion dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
+        a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}
+        b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}
+        \caption{Concentration profiles for ions with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
         \label{figure:concentrations_ion_5_1e-3}
@@
 \newpage
-    \subsubsection{Supersaturation} \hspace{10pt}
+\subsubsection{Vacancy Supersaturation}
+    The vacancy supersaturation curves for ion irradiation case are quite similar to ones for neutron irradiation case.
+The only difference is the asymmetrical shape of curves originates from concentration profiles.
+The non-linear increase in supersaturation values as domain gets larger is observed for ion irradiation too.
+    %\textcolor{blue}
+    The vacancy supersaturation behavior, shown in Fig.
+\ref{figure:vacancy_supersaturation_ion}, is identical to one in given for neutron irradiation case (see Fig.
+\ref{figure:vacancy_supersaturation_neutron}).
+The only difference is the asymmetrical shape of curves originating from defect production distribution.
+This similarity makes it possible to use ions instead of neutrons to predict the swelling behavior of reactor materials.
+The non-linear increase in supersaturation peak values might result in more void creation and undesired swelling behavior.\\
 
-    The vacancy supersaturation curves for ion irradation case are quite similar to ones for neutron irradation case.
-The only difference is the asymmetrical shape of curves originates from concentration profiles.
-The non-linear increase in supersaturation values as domain gets larger is observed for ion irradation too.
-      \begin{figure}[h!]  %Ion - %5 Bias rate
-        \centering
-        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
-        \caption{Vacancy supersaturation profiles for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
-        \label{figure:vacancy_supersaturation_ion_5}
-      \end{figure}
-      \newpage
-    \subsubsection{Sink Strengths} \hspace{10pt}
+\subsubsection{Grain Boundary Sink Strength}
     The sink strengths are directly related to concentration at center and flow at boundary.
-The change in centerline defect concentrations are not as considerable as neutron case.
+The change of defect concentrations are not as considerable as neutron case.
 So, the flow or flux at boundary becomes more dominant on sink strength profiles (see Fig.
-\ref{figure:sink_strengths_ion_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}).
-      % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
-      %   \centering
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
-      %   \qquad
-      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
-      %   \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
-      %   \label{figure:sink_strengths_ion_0_1e-6}
-      % \end{figure}
-      \begin{figure}[h!]  %Sink Strength - ion 1e-6 dpa/s - 5% Bias rate
-        \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_Z_scaled}}
-        \qquad
-        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
-        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
-        \label{figure:sink_strengths_ion_5_1e-6}
-      \end{figure}
+\ref{figure:sink_strengths_ion_5_1e-3}c).
+
+    As discussed previously, since ions can not penetrate until the end of the domain, they cause a non-uniform defect production.
+If the grain is small enough compared to penetration depth, concentration profiles become symmetrical (similar to neutron case), and the effect of distribution profile is not visible (up to 1000 $nm$ in Fig.
+\ref{figure:concentrations_ion_5_1e-3_5-5000nm}).
+Yet, for larger grains, the defect concentrations are highly affected by non-uniformity.
+The flux at the far boundary oscillates and approaches zero as grain size increases.
+Since sink strengths are related to the ratio of flux to concentration, they are affected by those oscillations.
+
     \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 5% Bias rate
         \centering
-        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
-        \qquad
-        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
-        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low dose rate neutron, b) high dose rate neutron}
+        a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}
+        b)\includegraphics[scale=0.55]{interstitial_concentration_5-5000nm-ion-5}
+        \caption{a) Change of grain boundary sink strengths with grain size for 5\% production bias for ions, b) Change of interstitial concentration for different grain sizes}
         \label{figure:sink_strengths_ion_5_1e-3}
@@
 
-% In nano-scale case, since the grain size is not big enough, the boundaries become
-% closer to each other. This causes point defects to reach sinks before they react with each other
-% and recombination plateau to disappear as it can be seen in Fig. 2. The nanoscale case acts like
-% a high-sink and high-temp condition case despite its low-sink and low-temperature. Therefore,
-% change in production bias does not have a significant effect on average concentration behavior
-% in nanoscale
-%
-% On the other hand, in micro-scale case, the domain has reasonable size, and thus
-% boundaries are far from each other. This provides defects more time to accumulate inside the
-% domain and recombine with each other after they reach a specific concentration. Figure 3
-% clearly shows the effect of production bias on average concentration.
-%
-% Effect of production bias on spatial profile of defect concentrations for nanoscale is
-% shown in Figure 4. The results seem not affected too much because of the same reasons
-% mentioned previously for average concentration.
-%
-% The micro-scale results (Fig. 5) are quite interesting and worth to think over. The
-% concentration profiles of interstitials for 0.1%, 5% and 10% cases are flipped over. A closer look
-% at evolution of 5% case over time in Fig. 6, after the end of quasi-steady-state region (t=10 -4 s in
-% Fig 3.), the average interstitial concentration starts to decrease as they segregate through sinks.
-% At steady state, the average interstitial concentration becomes minimum at the center and
-% maximum near boundaries because of segregation.
-%
-% The defect production rate (K 0 ) is the source term in point defect equations and has a
-% significant effect on concentrations.
-% In nano-scale case, the average concentration behavior is like high-sink density behavior
-% because of narrow domain. But, when the defect production rate increases, the average
-% concentration is shifted upward, and interstitial and vacancy average concentrations get closer
-% to each other because the production compensates more absorption at sinks than previous.
-% Based on this, if the production rate increased sufficiently, the recombination zone would
-% appear again in nano-scale domain.
+    \begin{figure}[h!]  %GB Sink Strength - Ion 1e-3 dpa/s
+        \centering
+        a)\includegraphics[scale=0.55]{sink_strength_ion_Zi_scaled_nolegend}
+        b)\includegraphics[scale=0.55]{sink_strength_ion_Zv_scaled_nolegend}
+        \includegraphics[scale=0.35]{legend}
+        \caption{Change of grain boundary sink strengths with production bias and grain size for ions}
+        \label{figure:sink_strengths_ion_bias_Z}
+    \end{figure}
+\newpage
+\subsection{Radiation-induced Segregation}
+
+    Ni-Cr based alloys is one of the most important structural materials for current and future advanced fission reactor designs.
+Currently, Ni-Cr based alloys are used widely in light water reactors (LWR), particularly for reactor coolant systems.
+These alloys show high strength and resistance to swelling at high temperatures and superior corrosion performance.
+Despite their many advantages, however, irradiation may cause dramatic changes to composition of alloy following that radiation induced segregation (RIS) can take place near microstructural defects where materials are sensitive to corrosive attack.
+Point defects can migrate, recombine, and cancel each other out on numerous sinks i.e., dislocations, free surfaces, or grain boundaries.
+The migration of these point defects causes significant changes in microstructure with similar changes in behavior.
+Ni-Cr based alloys contains a high Cr content to prevent corrosion.
+The decrease in the local composition of Cr may result in severe structural changes.
+Predictions of the effects of RIS in Ni-Cr based alloys are crucial for determining safe limits in the work environment.
+
+    In this section, in order to understand the effect of production bias on the various spatial profile of atom and defect concentrations, we used 5\%, 10\%, and 20\% production bias factors to produce a difference between interstitial and vacancy generation.
+    \\
+    \subsubsection{Rate Theory model for RIS}
+
+    This model considers the coupling of defects and atom fluxes through migration of interstitials and vacancies in a binary Ni-Cr alloy.
+
+    \begin{equation}
+        \begin{aligned}
+        &\frac{dC_i}{dt} = - \nabla\cdot J_i + K_0 - K_{iv}C_iC_v - S \\
+        &\frac{dC_v}{dt} = - \nabla\cdot J_v + K_0 - K_{iv}C_iC_v - S\\
+        &\frac{dC_{Cr}}{dt} = - \nabla\cdot J_{Cr} \\
+        \end{aligned}
+        \label{equation:RIS_equations}
+     \end{equation}\\
+    In the above, $\nabla\cdot J_i$ and $\nabla\cdot J_v$ are the divergences of the vacancy and interstitial fluxes at defect sinks, and $K_0$, $K_{iv}C_IC_V$, S terms are the local total rates of production, recombination of point defects per unit volume and sink absorption rate respectively.
+    Vacancy and interstitial concentrations were determined as the concentrations at thermal equilibrium for the initial conditions of system.
+Cr concentration is taken as the nominal value in the alloy composition.
+We assume that the alloy atoms are randomly distributed throughout the grain at the initial time.
+The equations were solved numerically with the initial and boundary conditions, and one-dimension calculations were performed.
+
+    \begin{table}[h!]
+  \centering
+  \caption{Input Parameters for RIS }
+  \label{table:Input_parameters_for_RIS}
+  \begin{tabular}{ ||p{7cm}|p{1cm}|p{2cm}||p{1cm}|p{1.5cm}||  }
+     % \hline
+     % \multicolumn{5}{|c|}{Material Properties} \\
+     \hline
+     Input Parameter & Symbol & Value & Units &  Reference\\
+     \hline\hline
+
+     Vacancy jump frequency for Ni & \omega_{Ni,v}  & 0 & s^{-1} &\\
+     Vacancy jump frequency for Cr & \omega_{Cr,v}  & 0 & s^{-1} &\\
+     Interstitial jump frequency for Ni & \omega_{Ni,,i}  & 0 & s^{-1} &\\
+     Interstitial jump frequency for Cr & \omega_{Cr,i}  & 0 & s^{-1} &\\
+     Vacancy migration energy for Ni & E_{Ni,v}^m  & 0 & eV & \\
+     Vacancy migration energy for Cr & E_{Cr,v}^m  & 0 & eV & \\
+     Interstitial migration energy for Ni & E_{Ni,i}^m  & 0 & eV & \\
+     Interstitial migration energy for Cr  & E_{Cr,i}^m  & 0 & eV & \\
+     Vacancy jump correlation factor for Ni  & f_vNi  & 0 & unitless & \\
+     Vacancy jump correlation factor for Cr  & f_vCr  & 0 & unitless & \\
+     Interstitial jump correlation factor for Ni   & f_iNi  & 0 & unitless & \\
+     Interstitial jump correlation factor for Cr  & f_iCr  & 0 & unitless & \\
+     \hline
+  \end{tabular}
+\end{table}
+
+    \begin{equation}
+        \begin{aligned}
+        d_{z}^{v,i}\ =\frac{1}{6}\lambda^2 \omega f exp(\frac{-E_{z-v,i}^m}{k_B T})
+        \end{aligned}
+        \label{equation:RIS_equations}
+    \end{equation}\\
+    $d_{a}^{v,i}$ represents diffusivity coefficient for the atom-defect pairs.
+For the chosen z atom, in this work z is Ni and Cr atoms, $\lambda$ is jump distance, $\omega$ is jump frequency and f is correlation factor.
+For vacancy and interstitial, $E_{z-v,i}^m$ is migration energy and $k_B$ is Boltzmann constant.
+
+    RIS behavior in the alloy with Ni-18Cr composition shows a vacancy-driven inverse Kirkendall mechanism.
+While chromium diffuses rapidly with vacancy flux, the concentration of chromium decreases at the grain boundaries, and the concentration of Nickel moving slower than Chromium increases at the grain boundary.
+
+    The concentration profiles of defects and Cr atoms at various production biases and grain sizes are presented in Figure \ref{figure:RIS}.
+Results show that at 50 nm grain size, effect of 5\%, 10\%, and 20\% production bias on interstitials does not show reversal behavior.
+Yet, at the grain size of 500 nm, the production bias effect shows reversal behavior on interstitials concentration.
+This conclusion also influences the Cr concentration profile.\\
+    The most critical consequence of the reversal behavior and sink density is that fast interstitials find sinks before vacancies.
+As a result of the interstitials finding sinks faster than vacancies, vacancy concentration continues to increase.
+This competition between interstitial and vacancy results in interstitials disappearing at the sink and recombining with vacancies.
+
+      \begin{figure}[h!]  %
+        \centering
+        a)\includegraphics[scale=0.55]{RIS_50nm_vacancy_concentraiton_bias.png}
+        b)\includegraphics[scale=0.55]{RIS_500nm_vacancy_concentration_bias.png}
+        \\
+        c)\includegraphics[scale=0.55]{RIS_50nm_interstitial_concentration_bias.png}
+        d)\includegraphics[scale=0.55]{RIS_500nm_interstitial_concentration_bias.png}
+        \\
+        e)\includegraphics[scale=0.55]{RIS_50nm_chromium_concentration_bias.png}
+        f)\includegraphics[scale=0.55]{RIS_500nm_chromium_concentration_bias.png}
+        \caption{Concentration profiles for high dose rate neutron with 0\%, 5\%, 10\%, and 20\% production bias a) 50 nm, vacancy concentration b) 500 nm, vacancy concentration c) 50 nm, interstitial concentration d) 500 nm, interstitial concentration e) 50 nm, chromium concentration f) 500 nm, chromium concentration }
+        \label{figure:RIS}
+      \end{figure}
+
+\clearpage
+
+    Fig.\ref{figure:RIS_Cr_concentration} shows the Cr concentration varying according to grain sizes and production bias.
+In Fig.\ref{figure:RIS_Cr_concentration}a, the vacancies and interstitials have the same generation rate.
+The change in Cr concentration profile between 50 and 1000 grain sizes is insignificant.
+We can say that as the grain size increases, the Cr segregation profile change is observed, but it is not marked clearly.
+With the purpose of effect of production bias, the production generation was re-analyzed with 20\% bias in the calculations.
+Fig.\ref{figure:RIS_Cr_concentration}b displays the Cr segregation profiles calculated with 20\% production bias in various grain sizes.
+It has been recognized that the area of Cr segregation increases with the increase of production bias and grain size.
+
+    \begin{figure}[h!]  %
+        \centering
+        a)\includegraphics[scale=0.55]{RIS_domainsize_all.png}
+        b)\includegraphics[scale=0.55]{RIS_domainsize_all_20.png}
+        \caption{Chromium concentration profiles with a) 0\% and b) 20\% production bias }
+        \label{figure:RIS_Cr_concentration}
+    \end{figure}
+
+        Trends in radiation-induced segregation in Ni-18Cr alloy occur with Cr depletion. The significance of the Cr segregation, related to the combination of production bias and domain size.\\
+
+        To examine the segregation effect at low temperature and high temperature, low-temperature 200\degree C, high-temperature 800\degree C, and 500\degree C temperature were selected as parameters.
+For Ni-18Cr alloy, Cr depletion was seen in the range from 200\degree C to 800\degree C.
+However, the highest Cr depletion effect was 20\% bias at 500\degree C.
+In general, it was observed that Cr depletion at 200\degree C increased at 500\degree C and decreased again at 800\degree C.
+It was found that this effect continues to increase in direct proportion to the increase in the production bias effect.\\
+
+        20\% production bias at 500\degree C shows the most remarkable Cr depletion effect, followed by 10\%  production bias at the same temperature.
+At high temperatures, the amount of Cr depletion is effectively reduced in the grain boundary.
+This may be due to the fact that at high temperatures, the interstitial concentration began to dominate the vacancy concentration.
+
+    \begin{figure}[h!]  %
+        \centering
+        a)\includegraphics[scale=0.55]{RIS_1vs10vs20_473_773_1073_Cr_conc.png}
+        b)\includegraphics[scale=0.55]{RIS_1vs10vs20_473_773_1073_interstitial_conc.png}
+        c)\includegraphics[scale=0.55]{RIS_1vs10vs20_473_773_1073_vacancy_conc.png}
+        \caption{Concentration profiles at different temperatures and with 1\%, 10\% and 20\% bias a) chromium b) vacancy and c) interstitial concentration}
+        \label{figure:RIS_temperature}
+    \end{figure}
+
+\clearpage
+
   \subsection{Discussion} \hspace{10pt}
-  What happens when switched from neutron irradation to ion irradiation
+
+    \begin{figure}[htb!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
+        \centering
+        a)\includegraphics[scale=0.33]{data_neutron_50nm}
+        b)\includegraphics[scale=0.33]{data_neutron_500nm}
+        c)\includegraphics[scale=0.33]{data_high_neutron_50nm}
+        d)\includegraphics[scale=0.33]{data_high_neutron_500nm}
+        e)\includegraphics[scale=0.33]{data_ion_50nm}
+        f)\includegraphics[scale=0.33]{data_ion_500nm}
+        f)\includegraphics[scale=0.3]{data_ion_1000nm_grey}
+        f)\includegraphics[scale=0.33]{data_ion_1000nm}
+        \caption{Change of interstitial concentration profiles with production bias in a grain of 50 $nm$ and 500 $nm$ for neutrons (a,b), protons (c,d) and ions (e,f)}
+        \label{figure:3D_concentrations_neutron_1e-6}
+    \end{figure}
+
+        \begin{figure}[h!]  %Neutron - Vacancy Supersaturation - 5% Bias
+        \centering
+        a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}
+        b)\includegraphics[scale=0.38]{data_neutron_Sv_center}
+        c)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}
+        d)\includegraphics[scale=0.38]{data_high_neutron_Sv_center}
+        e)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}
+        f)\includegraphics[scale=0.38]{data_ion_Sv_center}
+        \caption{Vacancy supersaturation profiles with different production biases for neutrons and b) protons c) ions, different production biases for neutrons (a,b), protons (c,d) and ions (e,f).
+2D plots (a,c,e) shows change of profiles for 5\% production bias.}
+        \label{figure:vacancy_supersaturation_neutron}
+    \end{figure}
+
+  What happens when switched from neutron irradiation to ion irradiation
   \begin{enumerate}
@@
 
-\newpage
+\clearpage
 \section{Conclusion} \hspace{10pt}
@@
 The behavior of concentration distributions are controlled by parameters given in equation, representing their reactions and diffusion in domain.
-According to the results obtained in this study, the combination of production bias, production dose rate, production profile and grain size determine whether the steady state point defect concentration profile is symmetrical, flipped or both.
+According to the results obtained in this study, the combination of production bias, production dose rate, production profile and grain size determine whether the steady state point defect concentration profile is symmetrical, reversed or both.
 There is always a critical value for parameters that could change the defect concentration profile entirely.
+The dependence of radiation induced segregation (RIS) on production biases and grain sizes was reproduced.
+Results shows that a combination of production bias and grain size results in the change of Cr segregation area.
 
-% An online tool could be created to play with different parameters.
-% \begin{thebibliography}{00}
-% \bibitem{b2} Garry S. Was.
-% \end{thebibliography}
-\addcontentsline{toc}{section}{References}
-\bibliographystyle{unsrt}
-\bibliography{ref}
+\clearpage
+\bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
+%\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
+\bibliography{references}
+
+%%% Make sure to upload the bib file along with the tex file and PDF
+%%% Please see the test.bib file for some examples of references
 
 \end{document}
+
+% \section{Manuscript Formatting}
+
+% \subsection{Heading Levels}
+
+% %There are 5 heading levels
+
+% \subsection{Level 2}
+% \subsubsection{Level 3}
+% \paragraph{Level 4}
+% \subparagraph{Level 5}
+
+% \subsection{Equations}
+% Equations should be inserted in editable format from the equation editor.
+
+% \begin{equation}
+% \sum x+ y =Z\label{eq:01}
+% \end{equation}
+
+% \subsection{Figures}
+% Frontiers requires figures to be submitted individually, in the same order as they are referred to in the manuscript.
+Figures will then be automatically embedded at the bottom of the submitted manuscript.
+Kindly ensure that each table and figure is mentioned in the text and in numerical order.
+Figures must be of sufficient resolution for publication \href{http://home.frontiersin.org/about/author-guidelines#ResolutionRequirements}{see here for examples and minimum requirements}.
+Figures which are not according to the guidelines will cause substantial delay during the production process.
+Please see \href{http://home.frontiersin.org/about/author-guidelines#GeneralStyleGuidelinesforFigures}{here} for full figure guidelines.
+Cite figures with subfigures as figure \ref{fig:2}B.
+
+% \subsubsection{Permission to Reuse and Copyright}
+% Figures, tables, and images will be published under a Creative Commons CC-BY licence and permission must be obtained for use of copyrighted material from other sources (including re-published/adapted/modified/partial figures and images from the internet).
+It is the responsibility of the authors to acquire the licenses, to follow any citation instructions requested by third-party rights holders, and cover any supplementary charges.
+% %%Figures, tables, and images will be published under a Creative Commons CC-BY licence and permission must be obtained for use of copyrighted material from other sources (including re-published/adapted/modified/partial figures and images from the internet).
+It is the responsibility of the authors to acquire the licenses, to follow any citation instructions requested by third-party rights holders, and cover any supplementary charges.
+
+% \subsection{Tables}
+% Tables should be inserted at the end of the manuscript.
+Please build your table directly in LaTeX.Tables provided as jpeg/tiff files will not be accepted.
+Please note that very large tables (covering several pages) cannot be included in the final PDF for reasons of space.
+These tables will be published as \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} on the online article page at the time of acceptance.
+The author will be notified during the typesetting of the final article if this is the case.
+
+% \section{Nomenclature}
+
+% \subsection{Resource Identification Initiative}
+% To take part in the Resource Identification Initiative, please use the corresponding catalog number and RRID in your current manuscript.
+For more information about the project and for steps on how to search for an RRID, please click \href{http://www.frontiersin.org/files/pdf/letter_to_author.pdf}{here}.
+
+% \subsection{Life Science Identifiers}
+% Life Science Identifiers (LSIDs) for ZOOBANK registered names or nomenclatural acts should be listed in the manuscript before the keywords.
+For more information on LSIDs please see \href{http://www.frontiersin.org/about/AuthorGuidelines#InclusionofZoologicalNomenclature}{Inclusion of Zoological Nomenclature} section of the guidelines.
+
+% \section{Additional Requirements}
+
+% For additional requirements for specific article types and further information please refer to \href{http://www.frontiersin.org/about/AuthorGuidelines#AdditionalRequirements}{Author Guidelines}.
+
+% \section*{Conflict of Interest Statement}
+% %All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed.
+If no such relationship exists, authors will be asked to confirm the following statement:
+
+% The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
+
+% \section*{Author Contributions}
+
+% The Author Contributions section is mandatory for all articles, including articles by sole authors.
+If an appropriate statement is not provided on submission, a standard one will be inserted during the production process.
+The Author Contributions statement must describe the contributions of individual authors referred to by their initials and, in doing so, all authors agree to be accountable for the content of the work.
+Please see  \href{http://home.frontiersin.org/about/author-guidelines#AuthorandContributors}{here} for full authorship criteria.
+
+% \section*{Funding}
+% Details of all funding sources should be provided, including grant numbers if applicable. Please ensure to add all necessary funding information, as after publication this is no longer possible.
+
+% \section*{Acknowledgments}
+% This is a short text to acknowledge the contributions of specific colleagues, institutions, or agencies that aided the efforts of the authors.
+
+% \section*{Supplemental Data}
+%  \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure.
+LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.
+
+% \section*{Data Availability Statement}
+% The datasets [GENERATED/ANALYZED] for this study can be found in the [NAME OF REPOSITORY] [LINK].
+% % Please see the availability of data guidelines for more information, at https://www.frontiersin.org/about/author-guidelines#AvailabilityofData
+
+% \section*{Figure captions}
+
+% %%% Please be aware that for original research articles we only permit a combined number of 15 figures and tables, one figure with multiple subfigures will count as only one figure.
+% %%% Use this if adding the figures directly in the mansucript, if so, please remember to also upload the files when submitting your article
+% %%% There is no need for adding the file termination, as long as you indicate where the file is saved. In the examples below the files (logo1.eps and logos.eps) are in the Frontiers LaTeX folder
+% %%% If using *.tif files convert them to .jpg or .png
+% %%%  NB logo1.eps is required in the path in order to correctly compile front page header %%%
+
+% \begin{figure}[h!]
+% \begin{center}
+% \includegraphics[width=10cm]{logo1}% This is a *.eps file
+% \end{center}
+% \caption{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures}\label{fig:1}
+% \end{figure}
+
+% \begin{figure}[h!]
+% \begin{center}
+% \includegraphics[width=15cm]{logos}
+% \end{center}
+% \caption{This is a figure with sub figures, \textbf{(A)} is one logo, \textbf{(B)} is a different logo.}\label{fig:2}
+% \end{figure}
+
+%%% If you are submitting a figure with subfigures please combine these into one image file with part labels integrated.
+%%% If you don't add the figures in the LaTeX files, please upload them when submitting the article.
+%%% Frontiers will add the figures at the end of the provisional pdf automatically
+%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should be avoided. They should be external callouts including graphics.
